### 2017-11-17 doc/paper.tex
Move from ECE gitlab to github

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

% \usepackage{nips_2016}

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[final]{nips_2016}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{amsmath}	% for \begin{align}
\usepackage{graphicx}	% for \includegraphics{filename}

\newcommand{\bb}[1]{\boldsymbol{#1}}

\title{Adversarial Zero-Shot Learning}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
	Shihui Li, Yu-Hsiang Lin, Kangyan Zhou
		%\thanks{Use footnote for providing further information about author (webpage, alternative address)---\emph{not} for acknowledging funding agencies.}
		\\
	Language Technologies Institute\\
	Carnegie Mellon University\\
	Pittsburgh, PA 15213 \\
	\texttt{\{shihuil,yuhsianl,kangyanz\}@andrew.cmu.edu} \\
	%% examples of more authors
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}

	This is a 4-page draft.

\end{abstract}

% ----------------------------------------------------
% ----------------------------------------------------

\section{Introduction}

Zero-shot learning has been a hot research topic in the field of image classification. One of the main challenges for object recognition is the lack of sufficient annotations for all possible concepts. This problem becomes even more severe when we target at the task of fine-grained classification because the annotation is more expensive and the number of fine-grained classes is huge. Ideally, a large-scale image classification system should be able to recognize novel categories based on its previous training experience. It simulates how people learn things: when people see an unfamiliar object, we would like to use our existing knowledge and try to evaluate the new object.

Realizing this limitation, researchers resort to additional information, for example attributes or text, to solve this problem. \par

Recently autoencoder has shown its great express power to present complicate distributions such human faces, natural sceneries and natural language. Lots of recent works focus

The fundamental problem of zero-shot learning is to extract semantically meaningful feature embeddings that could bridge the gap between

Autoencoder is able to convert complicated real world data distributions, e.g. to very well-formed low dimension. Many studies have shown that after applying autoencoder techniques, the learned latent feature space often has clear semantic meanings. For example, in \cite{makhzani2015adversarial}, all the digits can be well embedded into a low-dimensional manifold such that similar digits will have smaller distance within that manifold.

Autoencoder becomes an ideal option for this task because it can automatically learn import features. In \cite{kodirov2017semantic}, they present a novel solution to zero-shot learning based on learning a Semantic AutoEncoder(SAE). Taking the encoder-decoder paradigm, an encoder aims to project a visual feature vector into the semantic space as in the existing zero-learning shot models and the decoder should be able to reconstruct the original visual feature. Their results show that under this framework, the learned projection function from the seen classes is able to generalize better to the new unseen classes. One shortcoming of this model is that the encoder tends to learn similar features across multiple classes, which is disappointing for the task of fine-grained classification.

Inspired by these models, we propose an Adversarial Semantic AutoEncoder(ASAE). In our model, we have an encoder that projects a visual feature vector into the semantic space and a decoder that decodes and reconstructs the original visual features. Besides, we incorporates a discriminator as in \cite{makhzani2015adversarial} to ensure that generating from any part of prior space results in meaningful samples. Two types of discriminators will be discussed in this project, one is independent from semantic space and the other is dependent from semantic space.

% In this project we plan to explore how to develop an effective transfer learning algorithm, with focus on zero-shot learning and its combination with several popular deep learning methods, such as convolutional neural network, attention models, and Adversarial training, to detect unseen objects only with text description. \\
% Zero-shot learning consists in learning how to recognize new concepts by just having a description of them. State-of-the-art methods for zero-shot recognition formulate learning as a embedding problem of images and side information like text \cite{Elhoseiny2013}. We propose a model that can classify unseen categories from their textual description. Inspired by the fact that there is little supervision on text data, certain noise-cancelling techniques could be applied to improve the performance of our model.\\

% ----------------------------------------------------
% --------------------------------------------------

\section{Related Works}    
Considering that fine-grained categories might share some common knowledge, a common approach is to seek for an intermediate semantic representation that could connect seen and unseen classes.   \par

Human specified attributes are first explored to represent the discriminative properties shared among both seen and unseen categories in zero-shot learning\cite{torresani2010efficient, lampert2009learning}. One limitation of this method is that the creation of attributes still relies on human labors, making it difficult to scale up to meet large scale needs. \par

Other forms of semantic representations have been explored since then. \cite{mensink2014costa} attempts to capture the semantic relevance of two concepts by the co-occurrence of words. \cite{frome2013devise} learns joint image-word embeddings as well as embedding
images and sentences into a common space.

\cite{mensink2014costa,romera2015embarrassingly} assumes that the classifier for an unseen class can be presented as a linear combination of seen class classifiers. \cite{torresani2010efficient} employs the idea of using object detectors as the basic representations of images and the semantic concept is trained by using the entire image.

Apart from attributes, another type of additional information source for creating the semantic representation is the online textual document. \cite{Ba_2015_ICCV} proposed a model that allows  to automatically generate a list of pseudo attributes for each visual category consisting of words from Wikipedia articles. Instead of learning an embedding space for both modalities, they take advantage of the architecture of CNNs and learn features at different layers. More specifically, the image features are extracted from the activation layer of a convolutional neural network(CNN), and then go through a linear projection layer to reduce dimensions. The input text, e.g. Wikipedia articles, is first converted to one-hot encodings of the words with their tf-idf scores, and then fed into a multi-layer perceptron (MLP) to generate a deep representation, with the same dimension as the final image feature, and unique for each class. The final prediction is obtained by the dot product of the two generated features. \\

	More recent works jointly project the class into an embedding space, and try to compute a compatability function $F(x, y)$ that tries to predict whether the image feature x and the embedded class feature y. Here each class is represented as a vector that contains the relevance scores of the class and a set of predefined attributes. \cite{hariharan2012efficient} firstly proposed a SVM based classifier which takes the linearly projection of both source and target domain data as an input. \\

    In \cite{akata2013label}, $F(x, y)$ takes a linear form as $F(x, y) = xWy$. \cite{xian2016latent} takes this idea one step further, where a set of $W_i$ is available for the the compatibility function $F(x, y)$, and the final prediction will choose the $W$ that can produce the highest score. This $W_i$ can be shared across different labels.  The method is called as latent embedding, since it learns a latent embedding space explicitly based on clustering. \cite{zhang2015zero, zhang2016zero} proposes a framework that generalizes deep learning embedding, label embedding, and latent embedding. \\

    Recently deep encoder-decoder has become popular for a variety of multi-modal problems. In \cite{kiros2014unifying}, they introduce an encoder-decoder pipeline that learns a multimodal joint embedding space with images and text and a novel language model for decoding distributed representations the space. Their pipeline effectively unifies joint image-text embedding models with multimodal neural language models. \cite{kodirov2017semantic} takes a step further in multimodal model under the autoencoder paradigm. They proposed a novel zero-shot learning model based on a semantic autoencoder that uses a fast linear projection function and introduce an additional reconstruction objective function for learning a more generalisable projection function. \\

% 	In \cite{Elhoseiny2013}, during training, they learn the domain transfer function, $W$, from text domain to vision domain (in addition to feature extraction from text and image data). They use the approach from \cite{Kulis2011}. There is a measure of how much two feature vectors ($\bb{t}$ from text domain and $\bb{x}$ from vision domain) are similar to each other, based on $\bb{t}^{\top} W \bb{x}$. The training objective is basically that: (1) if $\bb{t}$ and $\bb{x}$ belong to the same class, their similarity should be more than a positive threshold (a margin), and (2) if $\bb{t}$ and $\bb{x}$ belong to the different classes, their similarity should be less than a negative threshold (a margin). It is trained with some regularization. (If the objective function is a direct/simple function of $\bb{t}^{\top} W \bb{x}$, it is non-convex for $\bb{t}$ and $\bb{x}$. That might be the reason that in \cite{Kulis2011} they use a more sophisticated formulation.)

% 	In fact, in \cite{Elhoseiny2013} during training they also need to learn the weight vectors $\bb{w}_i$, $i = 1, \dots, N_{sc}$ for ``seen classes'', but it seems that they do not describe how they learn these classifiers.

% 	They said that they ``learn'' the weight predictor (or the ``classifier regressor'') during training, but from their formulation it seems that as long as you have $\bb{w}_i$, then what the predictor does is that, given a new text vector $\bb{t}$, use $\bb{w}_i$ and Gaussian kernels (presumably with some fixed hyperparameters?) to compute (through an optimization problem) the predicted weight vector. So there doesn't seem to be any model parameters to learn here, but only works to do during inference time.

% 	During test time (inference), they give a clear constrained optimization problem to solve. What they try to optimize (in order to obtain the predicted weight vector $\bb{w}$ for an unseen-class text data $\bb{t}$) is basically:
% 		\begin{enumerate}
% 			\item Maximizing the similarity between $\bb{w}$ and $\bb{t}$ with respect to the domain transfer function $W$ (note that $W$ was trained using image feature $\bb{x}$ but here it is applied to weight vector $\bb{w}$ in image domain).
% 			\item Maximizing the log probability of having this $\bb{w}$ given $\bb{t}$ with respect to the weight predictor (and a given Gaussian prior).
% 			\item Minimizing the margin (well, it seems to be unbounded if you try to maximize the margin) of correctly labeling the seen classes all into negative side (they do not belong to the new class).
% 			\item Minimize the L2 regularizor.
% 		\end{enumerate}
% 		Their constraints are that all the seen images are classified as negative with some margin (done the slack variables, the margin, which are minimized).

% ----------------------------------------------------
% ----------------------------------------------------

% ----------------------------------------------------

% \subsection{Adversarial autoencoder}

% 	The adversarial autoencoder is a mixture of an autoencoder and a generative adversarial network. The input image $\bb{x}$ is encoded into $\bb{h}$ through encoder function $\bb{h} = f_{enc}(\bb{x})$. The reconstruction is performed by the conjugate decoder function $\tilde{\bb{x}} = f_{dec}(\bb{h})$. The autoencoder is trained to reconstruct the input image by minimizing the cross entropy loss,
% 		\begin{align}
% 			\textrm{loss} = -\bb{x}^{\top} \log \tilde{\bb{x}}.
% 		\end{align}

% 	The encoder also serves as the generator of the adversarial network, which generates negative samples with aggregated posterior distribution $q(\bb{h})$ that comes from the encoding distribution $q(\bb{h} | \bb{x})$ and the data distribution $p_d(\bb{x})$,
% 		\begin{align}
% 			q(\bb{h}) = \int q(\bb{h} | \bb{x}) p_d(\bb{x}) d \bb{x}.
% 		\end{align}

% 	A discriminator $D(\bb{z})$ gives the probability that $\bb{z}$ is a positive sample generated from a given and fixed prior distribution $r(\bb{z})$. The generator (the encoder) and discriminator are then jointly trained according to
% 		\begin{align}
% 			\min_{f_{enc}} \max_D \left\{ E_{\bb{z} \sim r(\bb{z})}[ \log D(\bb{z}) ] + E_{\bb{x} \sim p_d(\bb{x})}[ \log( 1 - D(f_{enc}(\bb{x})) ) ] \right\}.
% 		\end{align}
% 		That is, the generator (the encoder) is trained to generate samples mimicing the samples produced by the prior (such that the discriminator tends to classify it as positive samples from prior), and the discriminator is trained to classify the samples from prior as positive and those from generator as negative. The optimal solution is that the generator generates samples exactly according to the prior distribution (i.e.~$q(\bb{h}) \propto r(\bb{z})$), and the discriminator classifies samples from either the prior or the generator as positive samples with equal probabilities (e.g.~$D(\bb{z}) = D(f_{enc}(\bb{x})) = 1/2$).

% ----------------------------------------------------
% ----------------------------------------------------

\section{Zero-shot learning task}

	The problem we are going to solve is\dots

% ----------------------------------------------------
% ----------------------------------------------------

\section{Adversarial autoencoder for zero-shot learning}

	We propose two architectures that make use of adversarial autoencoders for the zero-shot learning tasks. In one of them we draw positive samples from the prior that is a Gaussian noise, and explicitly require the code to match the text representation. In this case, the prior serves as a regularizer. In the other of them, we directly use the text representation as positive samples drawn from some distribution that describes a class of data, and the code is trained by the adversarial net to match the text representation. In this case, the prior guides the generator (the encoder) to learn the code that is close to the semantic representation of text.

% ----------------------------------------------------

\subsection{Prior as regularizer}

	The architecture in Figure \ref{fig:NoisePrior} has an autoencoder that learns the encoding $\bb{h}^c$ of the input images $\bb{x}^c$ belonging to a class $c$. The code $\bb{h}^c$ is explicitly required to match the text representation $\bb{t}^c$ of that class, as well as regularized by the prior in the adversarial net. The learning task can be expressed as the optimization problem,
	\begin{align}
		\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) + || G(\bb{x}) - \bb{t} ||_2^2 \;\right].
	\end{align}

	Similar architecture has been proposed in \cite{kodirov2017semantic}, in which the explicit matching to the text representation was used to learn the semantic autoencoder for the image input. The difference in our architecture is that we use a adversarial net to regularize the matching to the text representation.

% ---------------------------------------------------------

\begin{figure}[h]
\centering
\includegraphics[width = 10 cm]{figNoisePrior}
\caption{Adversarial autoencoder with noise prior and explicit matching to the text representation.}
\label{fig:NoisePrior}
\end{figure}

% ---------------------------------------------------------

% ----------------------------------------------------

\subsection{Prior as guide}

	In Figure \ref{fig:TextPrior} we show the adversarial autoencoder that takes the text representation $\bb{t}^c$ as the positive sample drawn from some underlying prior dictating the distribution of the text representation of a class. In this architecture, the code is driven to match the text representation through the adversarial net itself. The optimization problem for this learning scheme is of the same form of the standard adversarial autoencoder,
	\begin{align}
		\min_{G} \max_D E_{\bb{t} \sim r(\bb{t})}\left[\; \log D(\bb{t}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) \;\right],
	\end{align}
	except that the prior serves as a guide to match the text distribution rather than as a regularizer that drives the code to a Gaussian noise.

% ---------------------------------------------------------

\begin{figure}[h]
\centering
\includegraphics[width = 10 cm]{figTextPrior}
\caption{Adversarial autoencoder with text representations as positive samples drawn from some underlying prior.}
\label{fig:TextPrior}
\end{figure}

% ---------------------------------------------------------

%	We propose to generalize this basic structure to fulfill the zero-shot learning task. In addition to the basic structure of the adversarial autoencoder, we include a domain transfer function $T$. Given the code $\bb{h}^c$ of an image $\bb{x}^c$ coming from a class $c$, the transfer function transforms $\bb{h}^c$ into its corresponding text-domain feature $\bb{\tau}^c = T(\bb{h}^c) = T(f_{enc}(\bb{x}^c))$. We denote the distribution of $\bb{\tau}^c$ as $\bb{\tau}^c \sim s(\bb{\tau}^c | \bb{h}^c, T)$, and the distribution of the actual text in this class as $\bb{t}^c \sim u^c(\bb{t}^c)$. Then, during training, we learn the domain transfer function $T$ such that $s(\bb{\tau}^c | \bb{h}^c, T) \rightarrow u^c(\bb{t}^c)$; that is, the encoded-then-transformed $\bb{\tau}^c$ is similar to $\bb{t}^c$.

% 	We propose a novel architecture that jointly learn the the encoding function $f_{enc}$ and the domain transfer function $T$ simultaneously. We adopt the paradigm of the adversarial autoencoder, but instead of using the encoder as the generator, the generator here is the hierarchical structure consisting of the encoder and the domain transfer function, which generates (negative) samples from the distribution $s(\bb{\tau}^c | \bb{h}^c, T)$. The discriminator is trained to classify the actual text $\bb{t}^c$ generated from $u^c(\bb{t}^c)$ (the prior) as positive sample, and the text feature $\bb{\tau}^c$ transferred from the image according to the distribution $s(\bb{\tau}^c | \bb{h}^c, T)$ (that is, $\bb{\tau}^c$ generated by the generator) as negative sample. Note that each class $c$ has its own distinct prior $u^c$. The encoder is in the mean time trained with the decoder to minimize the reconstruction error.

% 	During the test time of the zero-shot learning, an unseen test image $\bb{x}$ is given. We feed it into the encoder and the domain transfer function to obtain the text feature $\bb{\tau}$. Then, by computing its similarities to each of the unseen-class actual texts $\bb{t}^1, \bb{t}^2, \dots$, we take the most similar class as the class prediction for this image.

% % \noindent\rule{\textwidth}{0.4pt}

% % ----------------------------------------------------

% \subsection{Another possible learning scheme}

% 	We consider train the network in two stages: a pre-training to obtain the prior, and then a training of adversarial autoencoder using the pre-trained prior.

% 	In the first stage, we learn the domain transfer function, the matrix $W$. (Do we need to use the decoder part of the autoencoder here?) Method: For images $\bb{x}^c_i$ belonging to class $c$, and a text $\bb{t}^c$ in this class, we jointly learn an encoder $W_{enc}$, such that
% 		\begin{align}
% 			\min_{W_{enc}, W} || \bb{h}^c - W \bb{t}^c ||_2^2,
% 		\end{align}
% 		where
% 		\begin{align}
% 			\bb{h}^c = \sigma( W_{enc} \bb{x}^c ).
% 		\end{align}
% 		If we also use decoder part, it will be
% 		\begin{align}
% 			\min_{W_{enc}, W} \alpha || \bb{h}^c - W \bb{t}^c ||_2^2 + \beta [ -(\bb{x}^c)^{\top} \log ( W_{enc}^{\top} \bb{h}^c ) ].
% 		\end{align}

% 	In the second stage, we train the adversarial autoencoder with
% 		\begin{enumerate}
% 			\item $W_{enc}$ initialized by the pre-trained $W_{enc}$ in first stage. It serves as the generator of the adversarial network.
% 			%
% 			\item A class-wise prior
% 				\begin{align}
% 					p^c(\bb{h}^c) = \mathcal{N}( W \bb{t}^c, ( \sigma^{(c)} )^2 I ).
% 				\end{align}
% 		\end{enumerate}
% 		The goal in this stage is to learn (fine tune) the autoencoder $W_{enc}$,
% 		\begin{align}
% 			\min_{W_{enc}} [ -(\bb{x}^c)^{\top} \log ( W_{enc}^{\top} \bb{h}^c ) ],
% 		\end{align}
% 		with the class-wise prior.

% 	In predict time, for a test image $\bb{x}$, compute its code $\bb{h} = \sigma(W_{enc} \bb{x})$. Then predict its belonging text $\bb{t}^*$ among the candidate (unseen-class text) $\{ \bb{t}^1, \bb{t}^2, \dots \}$ by computing $\{ || \bb{h} - W \bb{t}^1 ||_2^2, || \bb{h} - W \bb{t}^2 ||_2^2, \dots \}$ and select the $\bb{t}^c$ of the minimum one as the $\bb{t}^*$.

% ----------------------------------------------------
% ----------------------------------------------------

\section{Datasets}

	Datasets we use.

% ----------------------------------------------------
% ----------------------------------------------------

\section{Experiments}

	Preliminary results.

% ----------------------------------------------------
% ----------------------------------------------------

\section{Discussion}

% 	The architecture proposed in this work can also be applied to image generation from text. By applying the inverse domain transfer function to a given text, $T^{-1}(\bb{t})$ can be taken as the code $\bb{h}$, which can then be fed into the decoder to obtain the image $\bb{x}$.

% ----------------------------------------------------
% ----------------------------------------------------

%\subsubsection*{Acknowledgments}

%Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.

% ----------------------------------------------------
% ----------------------------------------------------

\bibliographystyle{plain}
\bibliography{MachineLearning}

\end{document}

### 2017-11-17 proposal/proposal.tex
Move from ECE gitlab to github

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

% \usepackage{nips_2016}

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[final]{nips_2016}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{\vspace{-4mm} 10707 Project Proposal \vspace{-4mm}}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
	Shihui Li, Yu-Hsiang Lin, Kangyan Zhou
		%\thanks{Use footnote for providing further information about author (webpage, alternative address)---\emph{not} for acknowledging funding agencies.}
		\\
	Language Technologies Institute\\
	Carnegie Mellon University\\
	Pittsburgh, PA 15213 \\
	\texttt{\{shihuil,yuhsianl,kangyanz\}@andrew.cmu.edu} \\
	%% examples of more authors
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
	%% \And
	%% Coauthor \\
	%% Affiliation \\
	%% Address \\
	%% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

%\begin{abstract}
%Abstract.
%\end{abstract}

% ----------------------------------------------------
% ----------------------------------------------------
\vspace{-10mm}
\section{Problem Statement}
\vspace{-3mm}
Transfer learning has been a hot research topic in the field. It simulates how people learn things: when people see an unfamiliar object, we would like to use our existing knowledge and try to evaluate the new object. In this project we plan to explore how to develop an effective transfer learning algorithm, with focus on zero-shot learning and its combination with several popular deep learning methods, such as convolutional neural network, attention models, and Adversarial training, to detect unseen objects only with text description.

% ----------------------------------------------------
% ----------------------------------------------------
\vspace{-3mm}
\section{Motivation}
\vspace{-3mm}
Zero-shot learning consists in learning how to recognize new concepts by just having a description of them. State-of-the-art methods for zero-shot recognition formulate learning as a embedding problem of images and side information like text \cite{Elhoseiny2013}. We propose a model that can classify unseen categories from their textual description. Inspired by the fact that there is little supervision on text data, certain noise-cancelling techniques could be applied to improve the performance of our model.

% ----------------------------------------------------
% ----------------------------------------------------
\vspace{-3mm}
\section{Proposed Approach}
\vspace{-3mm}
\subsection{Convolutional Neural Network}
\vspace{-3mm}
	Convolutional neural network has shown its powerful ability in the image feature extraction task. We plan to use VggNet \cite{Simonyan2014} as our pre-trained model, and fine tune it with images in the training set, and then use the output of last convolution layer as the vector representation of the image.
\vspace{-3mm}
\subsection{Text Embedding}
\vspace{-3mm}
	There are several existing different techniques for text embedding. We plan to try fasttext \cite{Bojanowski2016} for our task. As an improvement based on word2vec \cite{Mikolov2013}, fasttext is a relatively new method that can reliably model different forms of the same word (e.g.~single/plural form) by referring the final representation as sum of character n-gram.
\vspace{-3mm}
\subsection{Soft Attention}
\vspace{-3mm}
	Attention is powerful technique to align different input modalities. It is commonly used in image captioning and visual question answering, for the purpose of allowing the algorithm to attend the correct part of image given text. In our scenario we want to try soft attention to use text to focus on specific part of the image. We would like to use the similar structure for the attention part as in \cite{You2016}.
\vspace{-3mm}
\subsection{Adversarial}
\vspace{-3mm}
	Adversarial training increases robustness to attacks by injecting adversarial examples into training data. However, it seems inappropriate to add adversarial noise to sparse high-dimensional inputs such as one-hot word representations. Therefore, we want to apply perturbations to the word embeddings instead to improve the ability of generalization of this model.

% ----------------------------------------------------
% ----------------------------------------------------
\vspace{-3mm}
\section{Datasets}
\vspace{-3mm}
\subsection{Caltech-UCSD Birds 200 (2010)}
\vspace{-3mm}
	Class number: 200. Feature dimension: 500 $\times$ [300--500] $\times$ 3. Size of dataset: 6033.

	Bird images belonging to 200 species \cite{Welinder2010}. Each class consists of between 20 and 40 images, with total of 6033 color images in jpeg format.

\vspace{-3mm}
\subsection{Oxford VGG 102 category flower dataset}
\vspace{-3mm}
	Class number: 102. Feature dimension: [500--600] $\times$ 500 $\times$ 3. Size of dataset: 8189.

	Flower images belonging to 102 categories \cite{Nilsback2008}. Each class consists of between 40 and 258 images, with total of 8189 color images in jpeg format.

% ----------------------------------------------------
% ----------------------------------------------------

%\subsubsection*{Acknowledgments}

%Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.

% ----------------------------------------------------
% ----------------------------------------------------

\bibliographystyle{plain}
\bibliography{MachineLearning}

%\section*{References}

%References follow the acknowledgments. Use unnumbered first-level heading for the references. Any choice of citation style is acceptable as long as you are consistent. It is permissible to reduce the font size to \verb+small+ (9 point) when listing the references. {\bf Remember that you can use a ninth page as long as it contains \emph{only} cited references.}
%\medskip

%\small

%[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen (eds.), {\it Advances in Neural Information Processing Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.

%[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring Realistic Neural Models with the GEneral NEural SImulation System.}  New York: TELOS/Springer--Verlag.

%[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and recall at excitatory recurrent synapses and cholinergic modulation in rat hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.

\end{document}

### 2017-11-17 doc/paper.tex
Added dataset

@@
 
-\section{Datasets}
+\section{Data}
 
-	Datasets we use.
+	We use two datasets: The Caltech-UCSD Birds 200 (2010) dataset \cite{Welinder2010}, and the Oxford VGG 102 category flower dataset \cite{Nilsback2008}.
+The Birds dataset has class number 200, feature dimension 500 $\times$ [300--500] $\times$ 3, and the size of the dataset is 6033.
+The bird images belonging to 200 species.
+Each class consists of between 20 and 40 images, with total of 6033 color images in jpeg format.
+
+	The Oxford VGG 102 category flower dataset has class number 102, feature dimension [500--600] $\times$ 500 $\times$ 3, and the size of the dataset is 8189.
+The flower images belonging to 102 categories.
+Each class consists of between 40 and 258 images, with total of 8189 color images in jpeg format.
 

### 2017-11-17 doc/paper.tex
Revised Intro and Related Work

@@
 
-\begin{abstract}
+%\begin{abstract}
 
-	This is a 4-page draft.
+%	This is a 4-page draft.
 
-\end{abstract}
+%\end{abstract}
 
@@
 Zero-shot learning has been a hot research topic in the field of image classification.
+It simulates how people learn things: when people see an unfamiliar object, we would like to use our existing knowledge and try to evaluate the new object.
+Ideally, a large-scale image classification system should be able to recognize novel categories based on its previous training experience.
 One of the main challenges for object recognition is the lack of sufficient annotations for all possible concepts.
 This problem becomes even more severe when we target at the task of fine-grained classification because the annotation is more expensive and the number of fine-grained classes is huge.
-Ideally, a large-scale image classification system should be able to recognize novel categories based on its previous training experience.
-It simulates how people learn things: when people see an unfamiliar object, we would like to use our existing knowledge and try to evaluate the new object.
+Realizing this limitation, researchers resort to additional information, for example attributes or text, to solve this problem.
 
-Realizing this limitation, researchers resort to additional information, for example attributes or text, to solve this problem. \par
-
-Recently autoencoder has shown its great express power to present complicate distributions such human faces, natural sceneries and natural language. Lots of recent works focus
-
-The fundamental problem of zero-shot learning is to extract semantically meaningful feature embeddings that could bridge the gap between
-
+On the other hand, autoencoder has shown its great express power to present complicate distributions such human faces, natural sceneries and natural language.
 Autoencoder is able to convert complicated real world data distributions, e.g.
-to very well-formed low dimension.
+text features, to very well-formed low dimension.
 Many studies have shown that after applying autoencoder techniques, the learned latent feature space often has clear semantic meanings.
@@
 
-Autoencoder becomes an ideal option for this task because it can automatically learn import features.
+ \par
+
+The fundamental problem of zero-shot learning is to extract semantically meaningful feature embeddings that could bridge the gap between similar image/text features and fine-grained classes.
+Autoencoder becomes an ideal option for this task because it can automatically learn important features.
 In \cite{kodirov2017semantic}, they present a novel solution to zero-shot learning based on learning a Semantic AutoEncoder(SAE).
@@
 \section{Related Works}    
-Considering that fine-grained categories might share some common knowledge, a common approach is to seek for an intermediate semantic representation that could connect seen and unseen classes.   \par
-
+Considering that fine-grained categories might share some common knowledge, a common approach is to seek for an intermediate semantic representation that could connect seen and unseen classes.
 Human specified attributes are first explored to represent the discriminative properties shared among both seen and unseen categories in zero-shot learning\cite{torresani2010efficient, lampert2009learning}.
@@
 
-Other forms of semantic representations have been explored since then.
+%Other forms of semantic representations have been explored since then.
+\cite{torresani2010efficient} employs the idea of using object detectors as the basic representations of images and the semantic concept is trained by using the entire image.
 \cite{mensink2014costa} attempts to capture the semantic relevance of two concepts by the co-occurrence of words.
-\cite{frome2013devise} learns joint image-word embeddings as well as embedding
-images and sentences into a common space.
+In \cite{mensink2014costa, romera2015embarrassingly}, the authors assume that the classifier for an unseen class can be presented as a linear combination of seen class classifiers.
 
-\cite{mensink2014costa,romera2015embarrassingly} assumes that the classifier for an unseen class can be presented as a linear combination of seen class classifiers.
-\cite{torresani2010efficient} employs the idea of using object detectors as the basic representations of images and the semantic concept is trained by using the entire image.
-
-Apart from attributes, another type of additional information source for creating the semantic representation is the online textual document.
-\cite{Ba_2015_ICCV} proposed a model that allows  to automatically generate a list of pseudo attributes for each visual category consisting of words from Wikipedia articles.
-Instead of learning an embedding space for both modalities, they take advantage of the architecture of CNNs and learn features at different layers.
+Apart from handcrafting attributes, another scheme is to directly use the online textual document as the additional information source.
+\cite{Elhoseiny2013} is one of the first works to use Wiki documents as text attributes.
+\cite{Ba_2015_ICCV} proposed a model that changes both the ways of extracting features from images and text domains.
 More specifically, the image features are extracted from the activation layer of a convolutional neural network(CNN), and then go through a linear projection layer to reduce dimensions.
 The input text, e.g.
-Wikipedia articles, is first converted to one-hot encodings of the words with their tf-idf scores, and then fed into a multi-layer perceptron (MLP) to generate a deep representation, with the same dimension as the final image feature, and unique for each class.
+Wikipedia articles, is first converted to one-hot encodings of the words with their tf-idf scores, which can be viewed as attributes, and then fed into a multi-layer perceptron (MLP) to generate a deep representation, with the same dimension as the final image feature, and unique for each class.
 The final prediction is obtained by the dot product of the two generated features.
-\\
+Instead of learning an embedding space for each modalities, \cite{frome2013devise} learns joint image-word embeddings so as to embedding images and sentences into a common space.\\
 
-	More recent works jointly project the class into an embedding space, and try to compute a compatability function $F(x, y)$ that tries to predict whether the image feature x and the embedded class feature y.
+	Another line of research is to improve the quality of the classification procedure.
+\cite{hariharan2012efficient} firstly proposed a SVM based classifier which takes the linear projection of both source and target domain data as the combined input.
+More recent works jointly project the class into an embedding space, and try to compute a compatability function $F(x, y)$ that tries to predict whether the image feature x is compatible with the embedded class feature y.
 Here each class is represented as a vector that contains the relevance scores of the class and a set of predefined attributes.
-\cite{hariharan2012efficient} firstly proposed a SVM based classifier which takes the linearly projection of both source and target domain data as an input.
-\\
-
 In \cite{akata2013label}, $F(x, y)$ takes a linear form as $F(x, y) = xWy$.
@@
 The method is called as latent embedding, since it learns a latent embedding space explicitly based on clustering.
-\cite{zhang2015zero, zhang2016zero} proposes a framework that generalizes deep learning embedding, label embedding, and latent embedding.
+\cite{zhang2016zero} proposes a framework that generalizes deep learning embedding, label embedding, and latent embedding.
 \\
@@
     Recently deep encoder-decoder has become popular for a variety of multi-modal problems.
-In \cite{kiros2014unifying}, they introduce an encoder-decoder pipeline that learns a multimodal joint embedding space with images and text and a novel language model for decoding distributed representations the space.
+In \cite{kiros2014unifying}, they introduce an encoder-decoder pipeline that learns a multimodal joint embedding space with images and text and a novel language model for decoding distributed representations of the text semantic space.
 Their pipeline effectively unifies joint image-text embedding models with multimodal neural language models.

### 2017-11-17 doc/paper.tex
Added task description

@@
 
-	The problem we are going to solve is\dots
+	We aim to solve the zero-shot learning problem of classifying images of unseen classes.
+Given the training images $\bb{x}^c$ and their corresponding text description documents $\bb{t}^c$ for $N_s$ seen classes $c$, we learn the semantic encodings $\bb{h}^c$ of the images.
+The learning goal is to learn the encodings $\bb{h}^c$ for a class that are close to their corresponding text document representation for this class.
+The encodings $\bb{h}^{c_1}$ and $\bb{h}^{c_2}$ from two different classes should bear some separable differences.
+
+	During the test time, we are given images $\bb{x}^c$ of $N_{us}$ unseen classes $c$ and also their text description documents $\bb{t}^c$, but without the prior knowledge of the correspondence between the images and the text documents.
+Our task is to predict the corresponding text document given an image.
 

### 2017-11-17 doc/paper.tex
Minor revision.

@@
 	We propose two architectures that make use of adversarial autoencoders for the zero-shot learning tasks.
-In one of them we draw positive samples from the prior that is a Gaussian noise, and explicitly require the code to match the text representation.
-In this case, the prior serves as a regularizer.
+In one of them we draw positive samples from the prior that is a Gaussian noise, and explicitly require the encoding $\bb{h}^c$ to match the text representation $\bb{t}^c$.
+In this case, the prior serves as a regularizer, which is presented in Sec.~\ref{subsec:NoisePrior}.
 In the other of them, we directly use the text representation as positive samples drawn from some distribution that describes a class of data, and the code is trained by the adversarial net to match the text representation.
-In this case, the prior guides the generator (the encoder) to learn the code that is close to the semantic representation of text.
+In this case, the prior guides the generator (the encoder) to learn the code that is close to the semantic representation of text, which is presented in Sec.~\ref{subsec:TextPrior}.
 
@@
 \subsection{Prior as regularizer}
+\label{subsec:NoisePrior}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[!htb]
 \centering
@@
 % ---------------------------------------------------------
+% ---------------------------------------------------------
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width = 10 cm]{figTextPrior}
+\caption{Adversarial autoencoder with text representations as positive samples drawn from some underlying prior.}
+\label{fig:TextPrior}
+\end{figure}
+
+% ---------------------------------------------------------
 
@@
 \subsection{Prior as guide}
+\label{subsec:TextPrior}
 
@@
 	except that the prior serves as a guide to match the text distribution rather than as a regularizer that drives the code to a Gaussian noise.
-
-% ---------------------------------------------------------
-
-\begin{figure}[h]
-\centering
-\includegraphics[width = 10 cm]{figTextPrior}
-\caption{Adversarial autoencoder with text representations as positive samples drawn from some underlying prior.}
-\label{fig:TextPrior}
-\end{figure}
-
-% ---------------------------------------------------------
 
@@
 
+\section{Dataset Description and Baseline Models}
+
+The dataset we want to use for this project is the Caltech-UCSD Birds 200-2011 data\cite{wah2011caltech}.
+There are 200 categories of birds.
+The number of images is 11,788, and the image dimension is 500 $\times$ [300--500] $\times$ 3.
+Each class consists of between 40 and 80 images.
+
+Here we also list the baseline models we want to compare out result with.
+They are Semantic Autoencoder(SAE)\cite{kodirov2017semantic}, Joint Latent Semantic Embedding(JLSE)\cite{zhang2016zero}, and Synthesized classifiers(Sync)\cite{changpinyo2016synthesized}.
+According to \cite{kodirov2017semantic}, the performance of the baseline models are reported as follows:
+\begin{table}[!htb]
+ \centering
+ \begin{tabular}{|l|l|}
+  \hline
+  Model & Results \\
+  \hline
+  SAE\cite{kodirov2017semantic} & 61.4 \\
+  \hline
+  JLSE\cite{zhang2016zero} & 41.8 \\
+  \hline
+  Sync\cite{changpinyo2016synthesized} & 54.4 \\
+  \bottomrule
+ \end{tabular}
+ \caption{Performance of baseline models.}
+\end{table}
+
 % ----------------------------------------------------
@@
 
-\section{Data}
+%\section{Data}
 
-	We use two datasets: The Caltech-UCSD Birds 200 (2010) dataset \cite{Welinder2010}, and the Oxford VGG 102 category flower dataset \cite{Nilsback2008}.
+%	We use two datasets: The Caltech-UCSD Birds 200 (2010) dataset \cite{Welinder2010}, and the Oxford VGG 102 category flower dataset \cite{Nilsback2008}.
 The Birds dataset has class number 200, feature dimension 500 $\times$ [300--500] $\times$ 3, and the size of the dataset is 6033.
@@
 
-	The Oxford VGG 102 category flower dataset has class number 102, feature dimension [500--600] $\times$ 500 $\times$ 3, and the size of the dataset is 8189.
+%	The Oxford VGG 102 category flower dataset has class number 102, feature dimension [500--600] $\times$ 500 $\times$ 3, and the size of the dataset is 8189.
 The flower images belonging to 102 categories.
@@
 
-\section{Experiments}
-
-	Preliminary results.
-
-% ----------------------------------------------------
-% ----------------------------------------------------
-
-\section{Discussion}
+%\section{Discussion}
 

### 2017-11-17 doc/paper.tex
The version submitted.

@@
 \usepackage{graphicx}	% for \includegraphics{filename}
+\usepackage{subcaption}	% for \begin{subfigure}[t]{0.5\textwidth}
 
@@
 
-	The architecture in Figure \ref{fig:NoisePrior} has an autoencoder that learns the encoding $\bb{h}^c$ of the input images $\bb{x}^c$ belonging to a class $c$.
+	The architecture in Figure \ref{fig:Architecture} (a) has an autoencoder that learns the encoding $\bb{h}^c$ of the input images $\bb{x}^c$ belonging to a class $c$.
 The code $\bb{h}^c$ is explicitly required to match the text representation $\bb{t}^c$ of that class, as well as regularized by the prior in the adversarial net.
@@
 
-\begin{figure}[!htb]
+\begin{figure*}[t!]
     \centering
-\includegraphics[width = 10 cm]{figNoisePrior}
-\caption{Adversarial autoencoder with noise prior and explicit matching to the text representation.}
-\label{fig:NoisePrior}
-\end{figure}
-
-% ---------------------------------------------------------
-% ---------------------------------------------------------
-
-\begin{figure}[!htb]
+    \begin{subfigure}[t]{0.5\textwidth}
         \centering
-\includegraphics[width = 10 cm]{figTextPrior}
-\caption{Adversarial autoencoder with text representations as positive samples drawn from some underlying prior.}
-\label{fig:TextPrior}
-\end{figure}
-
-% ---------------------------------------------------------
+        \includegraphics[height=1.65in]{figNoisePrior}
+        \caption{}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[height=1.65in]{figTextPrior}
+        \caption{}
+    \end{subfigure}
+    \caption{Adversarial autoencoders with (a) Gaussian prior and explicit matching to the text representation, and (b) text representations as positive samples drawn from some underlying prior of text distribution.}
+    \label{fig:Architecture}
+\end{figure*}
 
@@
 
-	In Figure \ref{fig:TextPrior} we show the adversarial autoencoder that takes the text representation $\bb{t}^c$ as the positive sample drawn from some underlying prior dictating the distribution of the text representation of a class.
+	In Figure \ref{fig:Architecture} (b) we show the adversarial autoencoder that takes the text representation $\bb{t}^c$ as the positive sample drawn from some underlying prior dictating the distribution of the text representation of a class.
 In this architecture, the code is driven to match the text representation through the adversarial net itself.

### 2017-11-19 doc/supplementary.tex
Added Supplementary

--- 2017-11-17 doc/paper.tex
@@
 
-\title{Adversarial Zero-Shot Learning}
+\title{Supplementary of Adversarial Zero-Shot Learning}
 
@@
 
-\section{Introduction}
+\section{Adversarial autoencoder with the prior as the regularizer}
 
-Zero-shot learning has been a hot research topic in the field of image classification.
-It simulates how people learn things: when people see an unfamiliar object, we would like to use our existing knowledge and try to evaluate the new object.
-Ideally, a large-scale image classification system should be able to recognize novel categories based on its previous training experience.
-One of the main challenges for object recognition is the lack of sufficient annotations for all possible concepts.
-This problem becomes even more severe when we target at the task of fine-grained classification because the annotation is more expensive and the number of fine-grained classes is huge.
-Realizing this limitation, researchers resort to additional information, for example attributes or text, to solve this problem.
+	Given an input image representation $\bb{x}^c \in R^{d_x}$, the encoder encodes it into $\bb{h}^c \in R^{d_h}$ by
+	\begin{align}
+		\bb{h}^c = \sigma(W^e \bb{x}^c + \bb{b}^e),
+	\end{align}
+	where $W^e \in R^{d_h \times d_x}$, $\bb{b}^e \in R^{d_h}$, and $\sigma(\cdot)$ is the sigmoid function,
+	\begin{align}
+		\sigma(s) = \frac{1}{1 + e^{-s}},
+	\end{align}
+	applied element-wisely. Note that the hidden representation space $R^{d_h}$ is also the space of the text representation; that is, $\bb{t}^c \in R^{d_h}$. The decoder computes
+	\begin{align}
+		\tilde{\bb{x}}^c = \sigma(W^d \bb{h}^c + \bb{b}^d),
+	\end{align}
+	where $W^d \in R^{d_x \times d_h}$ and $\bb{b}^d \in R^{d_x}$, such that the reconstruction cross entropy,
+	\begin{align}
+		S = -\bb{x}^c \odot \log \tilde{\bb{x}}^c,
+	\end{align}
+	where the log being applied element-wisely, is to be minimized.
 
-On the other hand, autoencoder has shown its great express power to present complicate distributions such human faces, natural sceneries and natural language.
-Autoencoder is able to convert complicated real world data distributions, e.g.
-text features, to very well-formed low dimension.
-Many studies have shown that after applying autoencoder techniques, the learned latent feature space often has clear semantic meanings.
-For example, in \cite{makhzani2015adversarial}, all the digits can be well embedded into a low-dimensional manifold such that similar digits will have smaller distance within that manifold.
-
- \par
-
-The fundamental problem of zero-shot learning is to extract semantically meaningful feature embeddings that could bridge the gap between similar image/text features and fine-grained classes.
-Autoencoder becomes an ideal option for this task because it can automatically learn important features.
-In \cite{kodirov2017semantic}, they present a novel solution to zero-shot learning based on learning a Semantic AutoEncoder(SAE).
-Taking the encoder-decoder paradigm, an encoder aims to project a visual feature vector into the semantic space as in the existing zero-learning shot models and the decoder should be able to reconstruct the original visual feature.
-Their results show that under this framework, the learned projection function from the seen classes is able to generalize better to the new unseen classes.
-One shortcoming of this model is that the encoder tends to learn similar features across multiple classes, which is disappointing for the task of fine-grained classification.
-
-Inspired by these models, we propose an Adversarial Semantic AutoEncoder(ASAE).
-In our model, we have an encoder that projects a visual feature vector into the semantic space and a decoder that decodes and reconstructs the original visual features.
-Besides, we incorporates a discriminator as in \cite{makhzani2015adversarial} to ensure that generating from any part of prior space results in meaningful samples.
-Two types of discriminators will be discussed in this project, one is independent from semantic space and the other is dependent from semantic space.
-
-% In this project we plan to explore how to develop an effective transfer learning algorithm, with focus on zero-shot learning and its combination with several popular deep learning methods, such as convolutional neural network, attention models, and Adversarial training, to detect unseen objects only with text description.
-\\
-% Zero-shot learning consists in learning how to recognize new concepts by just having a description of them.
-State-of-the-art methods for zero-shot recognition formulate learning as a embedding problem of images and side information like text \cite{Elhoseiny2013}.
-We propose a model that can classify unseen categories from their textual description.
-Inspired by the fact that there is little supervision on text data, certain noise-cancelling techniques could be applied to improve the performance of our model.\\
-
-% ----------------------------------------------------
-% --------------------------------------------------
-
-\section{Related Works}    
-Considering that fine-grained categories might share some common knowledge, a common approach is to seek for an intermediate semantic representation that could connect seen and unseen classes.
-Human specified attributes are first explored to represent the discriminative properties shared among both seen and unseen categories in zero-shot learning\cite{torresani2010efficient, lampert2009learning}.
-One limitation of this method is that the creation of attributes still relies on human labors, making it difficult to scale up to meet large scale needs.
-\par
-
-%Other forms of semantic representations have been explored since then.
-\cite{torresani2010efficient} employs the idea of using object detectors as the basic representations of images and the semantic concept is trained by using the entire image.
-\cite{mensink2014costa} attempts to capture the semantic relevance of two concepts by the co-occurrence of words.
-In \cite{mensink2014costa, romera2015embarrassingly}, the authors assume that the classifier for an unseen class can be presented as a linear combination of seen class classifiers.
-
-Apart from handcrafting attributes, another scheme is to directly use the online textual document as the additional information source.
-\cite{Elhoseiny2013} is one of the first works to use Wiki documents as text attributes.
-\cite{Ba_2015_ICCV} proposed a model that changes both the ways of extracting features from images and text domains.
-More specifically, the image features are extracted from the activation layer of a convolutional neural network(CNN), and then go through a linear projection layer to reduce dimensions.
-The input text, e.g.
-Wikipedia articles, is first converted to one-hot encodings of the words with their tf-idf scores, which can be viewed as attributes, and then fed into a multi-layer perceptron (MLP) to generate a deep representation, with the same dimension as the final image feature, and unique for each class.
-The final prediction is obtained by the dot product of the two generated features.
-Instead of learning an embedding space for each modalities, \cite{frome2013devise} learns joint image-word embeddings so as to embedding images and sentences into a common space.\\
-
-	Another line of research is to improve the quality of the classification procedure.
-\cite{hariharan2012efficient} firstly proposed a SVM based classifier which takes the linear projection of both source and target domain data as the combined input.
-More recent works jointly project the class into an embedding space, and try to compute a compatability function $F(x, y)$ that tries to predict whether the image feature x is compatible with the embedded class feature y.
-Here each class is represented as a vector that contains the relevance scores of the class and a set of predefined attributes.
-In \cite{akata2013label}, $F(x, y)$ takes a linear form as $F(x, y) = xWy$.
-\cite{xian2016latent} takes this idea one step further, where a set of $W_i$ is available for the the compatibility function $F(x, y)$, and the final prediction will choose the $W$ that can produce the highest score.
-This $W_i$ can be shared across different labels.
-The method is called as latent embedding, since it learns a latent embedding space explicitly based on clustering.
-\cite{zhang2016zero} proposes a framework that generalizes deep learning embedding, label embedding, and latent embedding.
-\\
-
-    Recently deep encoder-decoder has become popular for a variety of multi-modal problems.
-In \cite{kiros2014unifying}, they introduce an encoder-decoder pipeline that learns a multimodal joint embedding space with images and text and a novel language model for decoding distributed representations of the text semantic space.
-Their pipeline effectively unifies joint image-text embedding models with multimodal neural language models.
-\cite{kodirov2017semantic} takes a step further in multimodal model under the autoencoder paradigm.
-They proposed a novel zero-shot learning model based on a semantic autoencoder that uses a fast linear projection function and introduce an additional reconstruction objective function for learning a more generalisable projection function.
-\\
-
-% 	In \cite{Elhoseiny2013}, during training, they learn the domain transfer function, $W$, from text domain to vision domain (in addition to feature extraction from text and image data).
-They use the approach from \cite{Kulis2011}.
-There is a measure of how much two feature vectors ($\bb{t}$ from text domain and $\bb{x}$ from vision domain) are similar to each other, based on $\bb{t}^{\top} W \bb{x}$.
-The training objective is basically that: (1) if $\bb{t}$ and $\bb{x}$ belong to the same class, their similarity should be more than a positive threshold (a margin), and (2) if $\bb{t}$ and $\bb{x}$ belong to the different classes, their similarity should be less than a negative threshold (a margin).
-It is trained with some regularization.
-(If the objective function is a direct/simple function of $\bb{t}^{\top} W \bb{x}$, it is non-convex for $\bb{t}$ and $\bb{x}$.
-That might be the reason that in \cite{Kulis2011} they use a more sophisticated formulation.)
-
-% 	In fact, in \cite{Elhoseiny2013} during training they also need to learn the weight vectors $\bb{w}_i$, $i = 1, \dots, N_{sc}$ for ``seen classes'', but it seems that they do not describe how they learn these classifiers.
-
-% 	They said that they ``learn'' the weight predictor (or the ``classifier regressor'') during training, but from their formulation it seems that as long as you have $\bb{w}_i$, then what the predictor does is that, given a new text vector $\bb{t}$, use $\bb{w}_i$ and Gaussian kernels (presumably with some fixed hyperparameters?) to compute (through an optimization problem) the predicted weight vector.
-So there doesn't seem to be any model parameters to learn here, but only works to do during inference time.
-
-% 	During test time (inference), they give a clear constrained optimization problem to solve.
-What they try to optimize (in order to obtain the predicted weight vector $\bb{w}$ for an unseen-class text data $\bb{t}$) is basically:
-% 		\begin{enumerate}
-% 			\item Maximizing the similarity between $\bb{w}$ and $\bb{t}$ with respect to the domain transfer function $W$ (note that $W$ was trained using image feature $\bb{x}$ but here it is applied to weight vector $\bb{w}$ in image domain).
-% 			\item Maximizing the log probability of having this $\bb{w}$ given $\bb{t}$ with respect to the weight predictor (and a given Gaussian prior).
-% 			\item Minimizing the margin (well, it seems to be unbounded if you try to maximize the margin) of correctly labeling the seen classes all into negative side (they do not belong to the new class).
-% 			\item Minimize the L2 regularizor.
-% 		\end{enumerate}
-% 		Their constraints are that all the seen images are classified as negative with some margin (done the slack variables, the margin, which are minimized).
-
-% ----------------------------------------------------
-% ----------------------------------------------------
-
-% ----------------------------------------------------
-
-% \subsection{Adversarial autoencoder}
-
-% 	The adversarial autoencoder is a mixture of an autoencoder and a generative adversarial network.
-The input image $\bb{x}$ is encoded into $\bb{h}$ through encoder function $\bb{h} = f_{enc}(\bb{x})$.
-The reconstruction is performed by the conjugate decoder function $\tilde{\bb{x}} = f_{dec}(\bb{h})$.
-The autoencoder is trained to reconstruct the input image by minimizing the cross entropy loss,
-% 		\begin{align}
-% 			\textrm{loss} = -\bb{x}^{\top} \log \tilde{\bb{x}}.
-% 		\end{align}
-
-% 	The encoder also serves as the generator of the adversarial network, which generates negative samples with aggregated posterior distribution $q(\bb{h})$ that comes from the encoding distribution $q(\bb{h} | \bb{x})$ and the data distribution $p_d(\bb{x})$,
-% 		\begin{align}
-% 			q(\bb{h}) = \int q(\bb{h} | \bb{x}) p_d(\bb{x}) d \bb{x}.
-% 		\end{align}
-
-% 	A discriminator $D(\bb{z})$ gives the probability that $\bb{z}$ is a positive sample generated from a given and fixed prior distribution $r(\bb{z})$.
-The generator (the encoder) and discriminator are then jointly trained according to
-% 		\begin{align}
-% 			\min_{f_{enc}} \max_D \left\{ E_{\bb{z} \sim r(\bb{z})}[ \log D(\bb{z}) ] + E_{\bb{x} \sim p_d(\bb{x})}[ \log( 1 - D(f_{enc}(\bb{x})) ) ] \right\}.
-% 		\end{align}
-% 		That is, the generator (the encoder) is trained to generate samples mimicing the samples produced by the prior (such that the discriminator tends to classify it as positive samples from prior), and the discriminator is trained to classify the samples from prior as positive and those from generator as negative.
-The optimal solution is that the generator generates samples exactly according to the prior distribution (i.e.~$q(\bb{h}) \propto r(\bb{z})$), and the discriminator classifies samples from either the prior or the generator as positive samples with equal probabilities (e.g.~$D(\bb{z}) = D(f_{enc}(\bb{x})) = 1/2$).
-
-% ----------------------------------------------------
-% ----------------------------------------------------
-
-\section{Zero-shot learning task}
-
-	We aim to solve the zero-shot learning problem of classifying images of unseen classes.
-Given the training images $\bb{x}^c$ and their corresponding text description documents $\bb{t}^c$ for $N_s$ seen classes $c$, we learn the semantic encodings $\bb{h}^c$ of the images.
-The learning goal is to learn the encodings $\bb{h}^c$ for a class that are close to their corresponding text document representation for this class.
-The encodings $\bb{h}^{c_1}$ and $\bb{h}^{c_2}$ from two different classes should bear some separable differences.
-
-	During the test time, we are given images $\bb{x}^c$ of $N_{us}$ unseen classes $c$ and also their text description documents $\bb{t}^c$, but without the prior knowledge of the correspondence between the images and the text documents.
-Our task is to predict the corresponding text document given an image.
-
-% ----------------------------------------------------
-% ----------------------------------------------------
-
-\section{Adversarial autoencoder for zero-shot learning}
-
-	We propose two architectures that make use of adversarial autoencoders for the zero-shot learning tasks.
-In one of them we draw positive samples from the prior that is a Gaussian noise, and explicitly require the code to match the text representation.
-In this case, the prior serves as a regularizer.
-In the other of them, we directly use the text representation as positive samples drawn from some distribution that describes a class of data, and the code is trained by the adversarial net to match the text representation.
-In this case, the prior guides the generator (the encoder) to learn the code that is close to the semantic representation of text.
-
-% ----------------------------------------------------
-
-\subsection{Prior as regularizer}
-
-	The architecture in Figure \ref{fig:NoisePrior} has an autoencoder that learns the encoding $\bb{h}^c$ of the input images $\bb{x}^c$ belonging to a class $c$.
-The code $\bb{h}^c$ is explicitly required to match the text representation $\bb{t}^c$ of that class, as well as regularized by the prior in the adversarial net.
-The learning task can be expressed as the optimization problem,
+	The generator of the adversarial net is the encoder of the autoencoder; that is,
 	\begin{align}
-		\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) + || G(\bb{x}) - \bb{t} ||_2^2 \;\right].
+		G(\bb{x}^c) = \sigma(W^e \bb{x}^c + \bb{b}^e) = \bb{h}^c.
 	\end{align}
-
-	Similar architecture has been proposed in \cite{kodirov2017semantic}, in which the explicit matching to the text representation was used to learn the semantic autoencoder for the image input.
-The difference in our architecture is that we use a adversarial net to regularize the matching to the text representation.
-
-% ---------------------------------------------------------
-
-\begin{figure}[h]
-\centering
-\includegraphics[width = 10 cm]{figNoisePrior}
-\caption{Adversarial autoencoder with noise prior and explicit matching to the text representation.}
-\label{fig:NoisePrior}
-\end{figure}
-
-% ---------------------------------------------------------
-
-% ----------------------------------------------------
-
-\subsection{Prior as guide}
-
-	In Figure \ref{fig:TextPrior} we show the adversarial autoencoder that takes the text representation $\bb{t}^c$ as the positive sample drawn from some underlying prior dictating the distribution of the text representation of a class.
-In this architecture, the code is driven to match the text representation through the adversarial net itself.
-The optimization problem for this learning scheme is of the same form of the standard adversarial autoencoder,
+	The positive samples are drawn from the Gaussian prior,
 	\begin{align}
-		\min_{G} \max_D E_{\bb{t} \sim r(\bb{t})}\left[\; \log D(\bb{t}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) \;\right],
+		\bb{z} \sim \mathcal{N}(0, \lambda^2).
 	\end{align}
-	except that the prior serves as a guide to match the text distribution rather than as a regularizer that drives the code to a Gaussian noise.
-
-% ---------------------------------------------------------
-
-\begin{figure}[h]
-\centering
-\includegraphics[width = 10 cm]{figTextPrior}
-\caption{Adversarial autoencoder with text representations as positive samples drawn from some underlying prior.}
-\label{fig:TextPrior}
-\end{figure}
-
-% ---------------------------------------------------------
-
-%	We propose to generalize this basic structure to fulfill the zero-shot learning task.
-In addition to the basic structure of the adversarial autoencoder, we include a domain transfer function $T$.
-Given the code $\bb{h}^c$ of an image $\bb{x}^c$ coming from a class $c$, the transfer function transforms $\bb{h}^c$ into its corresponding text-domain feature $\bb{\tau}^c = T(\bb{h}^c) = T(f_{enc}(\bb{x}^c))$.
-We denote the distribution of $\bb{\tau}^c$ as $\bb{\tau}^c \sim s(\bb{\tau}^c | \bb{h}^c, T)$, and the distribution of the actual text in this class as $\bb{t}^c \sim u^c(\bb{t}^c)$.
-Then, during training, we learn the domain transfer function $T$ such that $s(\bb{\tau}^c | \bb{h}^c, T) \rightarrow u^c(\bb{t}^c)$; that is, the encoded-then-transformed $\bb{\tau}^c$ is similar to $\bb{t}^c$.
-
-% 	We propose a novel architecture that jointly learn the the encoding function $f_{enc}$ and the domain transfer function $T$ simultaneously.
-We adopt the paradigm of the adversarial autoencoder, but instead of using the encoder as the generator, the generator here is the hierarchical structure consisting of the encoder and the domain transfer function, which generates (negative) samples from the distribution $s(\bb{\tau}^c | \bb{h}^c, T)$.
-The discriminator is trained to classify the actual text $\bb{t}^c$ generated from $u^c(\bb{t}^c)$ (the prior) as positive sample, and the text feature $\bb{\tau}^c$ transferred from the image according to the distribution $s(\bb{\tau}^c | \bb{h}^c, T)$ (that is, $\bb{\tau}^c$ generated by the generator) as negative sample.
-Note that each class $c$ has its own distinct prior $u^c$.
-The encoder is in the mean time trained with the decoder to minimize the reconstruction error.
-
-% 	During the test time of the zero-shot learning, an unseen test image $\bb{x}$ is given.
-We feed it into the encoder and the domain transfer function to obtain the text feature $\bb{\tau}$.
-Then, by computing its similarities to each of the unseen-class actual texts $\bb{t}^1, \bb{t}^2, \dots$, we take the most similar class as the class prediction for this image.
-
-% % \noindent\rule{\textwidth}{0.4pt}
-
-% % ----------------------------------------------------
-
-% \subsection{Another possible learning scheme}
-
-% 	We consider train the network in two stages: a pre-training to obtain the prior, and then a training of adversarial autoencoder using the pre-trained prior.
-
-% 	In the first stage, we learn the domain transfer function, the matrix $W$.
-(Do we need to use the decoder part of the autoencoder here?) Method: For images $\bb{x}^c_i$ belonging to class $c$, and a text $\bb{t}^c$ in this class, we jointly learn an encoder $W_{enc}$, such that
-% 		\begin{align}
-% 			\min_{W_{enc}, W} || \bb{h}^c - W \bb{t}^c ||_2^2,
-% 		\end{align}
-% 		where
-% 		\begin{align}
-% 			\bb{h}^c = \sigma( W_{enc} \bb{x}^c ).
-% 		\end{align}
-% 		If we also use decoder part, it will be
-% 		\begin{align}
-% 			\min_{W_{enc}, W} \alpha || \bb{h}^c - W \bb{t}^c ||_2^2 + \beta [ -(\bb{x}^c)^{\top} \log ( W_{enc}^{\top} \bb{h}^c ) ].
-% 		\end{align}
-
-% 	In the second stage, we train the adversarial autoencoder with
-% 		\begin{enumerate}
-% 			\item $W_{enc}$ initialized by the pre-trained $W_{enc}$ in first stage. It serves as the generator of the adversarial network.
-% 			%
-% 			\item A class-wise prior
-% 				\begin{align}
-% 					p^c(\bb{h}^c) = \mathcal{N}( W \bb{t}^c, ( \sigma^{(c)} )^2 I ).
-% 				\end{align}
-% 		\end{enumerate}
-% 		The goal in this stage is to learn (fine tune) the autoencoder $W_{enc}$,
-% 		\begin{align}
-% 			\min_{W_{enc}} [ -(\bb{x}^c)^{\top} \log ( W_{enc}^{\top} \bb{h}^c ) ],
-% 		\end{align}
-% 		with the class-wise prior.
-
-% 	In predict time, for a test image $\bb{x}$, compute its code $\bb{h} = \sigma(W_{enc} \bb{x})$.
-Then predict its belonging text $\bb{t}^*$ among the candidate (unseen-class text) $\{ \bb{t}^1, \bb{t}^2, \dots \}$ by computing $\{ || \bb{h} - W \bb{t}^1 ||_2^2, || \bb{h} - W \bb{t}^2 ||_2^2, \dots \}$ and select the $\bb{t}^c$ of the minimum one as the $\bb{t}^*$.
-
-% ----------------------------------------------------
-% ----------------------------------------------------
-
-\section{Data}
-
-	We use two datasets: The Caltech-UCSD Birds 200 (2010) dataset \cite{Welinder2010}, and the Oxford VGG 102 category flower dataset \cite{Nilsback2008}.
-The Birds dataset has class number 200, feature dimension 500 $\times$ [300--500] $\times$ 3, and the size of the dataset is 6033.
-The bird images belonging to 200 species.
-Each class consists of between 20 and 40 images, with total of 6033 color images in jpeg format.
-
-	The Oxford VGG 102 category flower dataset has class number 102, feature dimension [500--600] $\times$ 500 $\times$ 3, and the size of the dataset is 8189.
-The flower images belonging to 102 categories.
-Each class consists of between 40 and 258 images, with total of 8189 color images in jpeg format.
-
-% ----------------------------------------------------
-% ----------------------------------------------------
-
-\section{Experiments}
-
-	Preliminary results.
-
-% ----------------------------------------------------
-% ----------------------------------------------------
-
-\section{Discussion}
-
-% 	The architecture proposed in this work can also be applied to image generation from text.
-By applying the inverse domain transfer function to a given text, $T^{-1}(\bb{t})$ can be taken as the code $\bb{h}$, which can then be fed into the decoder to obtain the image $\bb{x}$.
+	where $\bb{z} \in R^{d_h}$.	We use a fully connected neural network with a single hidden layer as the discriminator. Given an input $\bb{z} \in R^{d_h}$, it computes
+	\begin{align}
+		\bb{z} \sim \mathcal{N}(0, \lambda^2).
+	\end{align}
 
@@
 
-\bibliographystyle{plain}
-\bibliography{MachineLearning}
+%\bibliographystyle{plain}
+%\bibliography{MachineLearning}
 

### 2017-11-19 doc/supplementary.tex
Editing implementing details...

@@
 	\begin{align}
-		\bb{z} \sim \mathcal{N}(0, \lambda^2).
+		\bb{z}^1 &= \sigma( W^1 \bb{z} + \bb{b}^1 ), \\
+		%
+		z^2 &= \sigma( (\bb{w}^2)^{\top} \bb{z}^1 + b^2 ),
+	\end{align}
+	where $\bb{z}^1 \in R^{d_1}$, $W^1 \in R^{d_1 \times d_h}$, $\bb{b}^1 \in R^{d_1}$, $\bb{w}^2 \in R^{d_1}$, and $b^2$ and $z^2$ are scalars. The discriminator returns
+	\begin{align}
+		D(\bb{z}) = z^2,
+	\end{align}
+	which is the estimation of the probability that $\bb{z}$ is drawn from the prior.
+
+	For the autoencoder and the generator of the adversarial net, the loss function is the empirical risk,
+	\begin{align}
+		f_e = \frac{1}{\ell} \sum_{c = 1}^{N_s} \sum_{i = 1}^{\ell_c} \left\{ -\bb{x}^{c, (i)} \odot \log \tilde{\bb{x}}^{c, (i)} + \log\left[ 1 - D( \bb{h}^{c, (i)} ) \right] + || \bb{h}^{c, (i)} - \bb{t}^c ||_2^2 \right\},
+	\end{align}
+	where
+	\begin{align}
+		\ell = \sum_{c = 1}^{N_s} \ell_c
+	\end{align}
+	is the total number of training images. Here we assume there is only one text $\bb{t}^c$ for each class.
+
+	where the parameters of the discriminator is held constant.
+
+	\begin{align}
+		f = \frac{1}{\ell} \sum_{i = 1}^{\ell} \log z^{2, (i)}
 	\end{align}

### 2017-11-19 doc/supplementary.tex
Wrote down the optimization problems for autoencoder+generator and discriminator.

@@
 	\end{align}
-	where the log being applied element-wisely, is to be minimized.
+	is minimized. Here $\odot$ denotes the element-wise product, and the log function is applied element-wisely.
 
@@
 	\begin{align}
-		f_e = \frac{1}{\ell} \sum_{c = 1}^{N_s} \sum_{i = 1}^{\ell_c} \left\{ -\bb{x}^{c, (i)} \odot \log \tilde{\bb{x}}^{c, (i)} + \log\left[ 1 - D( \bb{h}^{c, (i)} ) \right] + || \bb{h}^{c, (i)} - \bb{t}^c ||_2^2 \right\},
+		f_g = \frac{1}{m} \sum_{c = 1}^{N_s} \sum_{i = 1}^{m_c} \left\{ -\bb{x}^{c, (i)} \odot \log \tilde{\bb{x}}^{c, (i)} + \log\left[ 1 - D( \bb{h}^{c, (i)} ) \right] + || \bb{h}^{c, (i)} - \bb{t}^c ||_2^2 \right\},
 	\end{align}
@@
 	\begin{align}
-		\ell = \sum_{c = 1}^{N_s} \ell_c
+		m = \sum_{c = 1}^{N_s} m_c
 	\end{align}
@@
 
-	where the parameters of the discriminator is held constant.
+	For the discriminator of the adversarial net, the loss function is the empirical risk,
+	\begin{align}
+		f_d = -\frac{1}{m} \sum_{j = 1}^{m} \log D( \bb{z}^{(j)} ) - \frac{1}{m} \sum_{c = 1}^{N_s} \sum_{i = 1}^{m_c} \log\left[ 1 - D( \bb{h}^{c, (i)} ) \right],
+	\end{align}
+	where $\bb{z}^{(j)}$ are $m$ samples drawn from the prior distribution $\mathcal{N}(0, \lambda^2)$.
 
+	The optimization problem for the autoencoder and the generator is
 	\begin{align}
-		f = \frac{1}{\ell} \sum_{i = 1}^{\ell} \log z^{2, (i)}
+		\min_{W^e, \bb{b}^e, W^d, \bb{b}^d} \; f_g,
 	\end{align}
+	while the parameters of the discriminator ($W^1, \bb{b}^1, \bb{w}^2, b^2$) are held constant. The optimization problem for the discriminator is
+	\begin{align}
+		\min_{W^1, \bb{b}^1, \bb{w}^2, b^2} \; f_d,
+	\end{align}
+	while the parameters of the generator ($W^e, \bb{b}^e, W^d, \bb{b}^d$) are held constant.
 

### 2017-11-19 doc/supplementary.tex
Slightly modified the notation used in Supplementary, so that the mini-batch can be easily incorporated.

--- 2017-11-19 doc/supplementary.tex
@@
 
-	Given an input image representation $\bb{x}^c \in R^{d_x}$, the encoder encodes it into $\bb{h}^c \in R^{d_h}$ by
+	Given an input image representation $\bb{x} \in R^{d_x}$, the encoder encodes it into $\bb{h} \in R^{d_h}$ by
 	\begin{align}
-		\bb{h}^c = \sigma(W^e \bb{x}^c + \bb{b}^e),
+		\bb{h} = \sigma(W^e \bb{x} + \bb{b}^e),
 	\end{align}
@@
 	\end{align}
-	applied element-wisely. Note that the hidden representation space $R^{d_h}$ is also the space of the text representation; that is, $\bb{t}^c \in R^{d_h}$. The decoder computes
+	applied element-wisely. Note that the hidden representation space $R^{d_h}$ is also the space of the text representation; that is, $\bb{t} \in R^{d_h}$. The decoder computes
 	\begin{align}
-		\tilde{\bb{x}}^c = \sigma(W^d \bb{h}^c + \bb{b}^d),
+		\tilde{\bb{x}} = \sigma(W^d \bb{h} + \bb{b}^d),
 	\end{align}
-	where $W^d \in R^{d_x \times d_h}$ and $\bb{b}^d \in R^{d_x}$, such that the reconstruction cross entropy,
-	\begin{align}
-		S = -\bb{x}^c \odot \log \tilde{\bb{x}}^c,
-	\end{align}
-	where the log being applied element-wisely, is to be minimized.
+	where $W^d \in R^{d_x \times d_h}$ and $\bb{b}^d \in R^{d_x}$.
 
@@
 	\begin{align}
-		G(\bb{x}^c) = \sigma(W^e \bb{x}^c + \bb{b}^e) = \bb{h}^c.
+		G(\bb{x}) = \sigma(W^e \bb{x} + \bb{b}^e) = \bb{h}.
 	\end{align}
@@
 	\begin{align}
-		\bb{z} \sim \mathcal{N}(0, \lambda^2).
+		\bb{z}^1 &= \sigma( W^1 \bb{z} + \bb{b}^1 ), \\
+		%
+		z^2 &= \sigma( (\bb{w}^2)^{\top} \bb{z}^1 + b^2 ),
 	\end{align}
+	where $\bb{z}^1 \in R^{d_1}$, $W^1 \in R^{d_1 \times d_h}$, $\bb{b}^1 \in R^{d_1}$, $\bb{w}^2 \in R^{d_1}$, and $b^2$ and $z^2$ are scalars. The discriminator returns
+	\begin{align}
+		D(\bb{z}) = z^2,
+	\end{align}
+	which is the estimation of the probability that $\bb{z}$ is drawn from the prior.
 
-% ----------------------------------------------------
-% ----------------------------------------------------
+	For the autoencoder and the generator of the adversarial net, the loss function for a mini-batch of instances, $S$, is the empirical risk,
+	\begin{align}
+		f_g = \frac{1}{|S|} \sum_{i \in S} \left\{ -\bb{x}^{(i)} \odot \log \tilde{\bb{x}}^{(i)} + \log\left[ 1 - D( \bb{h}^{(i)} ) \right] + || \bb{h}^{(i)} - \bb{t}^{c_i} ||_2^2 \right\},
+	\end{align}
+	where $\odot$ denotes the element-wise product, the log function is applied element-wisely, and $c_i$ is the class of the instance $x^{(i)}$.
+Here we assume that there is only one text $\bb{t}^c$ for each class $c$.
 
-%\subsubsection*{Acknowledgments}
+	For the discriminator of the adversarial net, the loss function is
+	\begin{align}
+		f_d = -\frac{1}{|S|} \sum_{j = 1}^{|S|} \log D( \bb{z}^{(j)} ) - \frac{1}{|S|} \sum_{i \in S} \log\left[ 1 - D( \bb{h}^{(i)} ) \right],
+	\end{align}
+	where $\bb{z}^{(j)}$ are $|S|$ samples drawn from the prior distribution $\mathcal{N}(0, \lambda^2)$.
 
-%Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.
+	The optimization problem for the autoencoder and the generator is
+	\begin{align}
+		\min_{W^e, \bb{b}^e, W^d, \bb{b}^d} \; f_g,
+	\end{align}
+	while the parameters of the discriminator ($W^1, \bb{b}^1, \bb{w}^2, b^2$) are held constant. The optimization problem for the discriminator is
+	\begin{align}
+		\min_{W^1, \bb{b}^1, \bb{w}^2, b^2} \; f_d,
+	\end{align}
+	while the parameters of the generator ($W^e, \bb{b}^e, W^d, \bb{b}^d$) are held constant.
 

### 2017-12-01 doc/supplementary.tex
Added classification accuracy; still checking...

@@
 	\end{align}
-	where $\odot$ denotes the element-wise product, the log function is applied element-wisely, and $c_i$ is the class of the instance $x^{(i)}$.
+	where $\odot$ denotes the element-wise product, the log function is applied element-wisely, and $c_i$ is the class of the instance $\bb{x}^{(i)}$.
 Here we assume that there is only one text $\bb{t}^c$ for each class $c$.
@@
 
+	At test time, given a test image $\bb{x}$, the encoder generates its representation $\bb{h}$.
+We are also given the text representations $\bb{t}^c$ of the unseen classes, $c \in \{ 1, 2, \dots, N_{\textrm{us}} \}$.
+We then compute the L2 distance between each pair of $\bb{h}$ and $\bb{t}^c$, and return the $\bb{t}^{c*}$ that is closest to $\bb{h}$ as our prediction of the class of this image $\bb{x}$.
+
+% ----------------------------------------------------
+% ----------------------------------------------------
+
+\section{Adversarial autoencoder with the prior as the guide}
+
+	The encoder, decoder, and generator are the same as described in the previous section.
+The difference is that we use the text representation instead of Gaussian noise as the prior in the adversarial net.
+For an input image $\bb{x}^{(i)}$ of class $c_i$ and the text representation $\bb{t}^{c_i}$ of this class,
+
 % ----------------------------------------------------

### 2017-12-01 code/aaeexp.py

@@ -66,10 +66,10 @@ class aaeexp(object):
 			self.gaus_sample.initialize_batch('train_init')
 			self.attrdata.initialize_batch('train_init')
 			#X_full, Y_full, current_batch_size, batch_counter, index_vector = self.data.next_batch()
-			X_full, _, _, _, index_vector = self.data.next_batch()
+			X_full, Y_full, _, _, _ = self.data.next_batch()
 			Z_batch, _, _, _, _ = self.gaus_sample.next_batch()
 			#T_batch = self.attrdata.next_batch(index_vector)
-			T_batch = self.attrdata.next_batch( self.data.train_Y[ index_vector ] )
+			T_batch = self.attrdata.next_batch(Y_full)
 			feed_dict = { X: X_full, Z: Z_batch, T: T_batch }
 			#feed_dict = { X: X_full, Z: Z_batch }
 			train_gen_loss_got, train_disc_loss_got = sess.run([gen_loss, disc_loss], feed_dict = feed_dict)
@@ -79,10 +79,10 @@ class aaeexp(object):
 		self.data.initialize_batch('val')
 		self.gaus_sample.initialize_batch('val')
 		self.attrdata.initialize_batch('val')
-		X_val_full, _, _, _, index_vector = self.data.next_batch()
+		X_val_full, Y_val_full, _, _, _ = self.data.next_batch()
 		Z_val_full, _, _, _, _ = self.gaus_sample.next_batch()
 		#T_batch = self.attrdata.next_batch(index_vector)
-		T_batch = self.attrdata.next_batch( self.data.val_Y[ index_vector ] )
+		T_batch = self.attrdata.next_batch(Y_val_full)
 		feed_dict = { X: X_val_full, Z: Z_val_full, T: T_batch }
 		#feed_dict = { X: X_val_full, Z: Z_val_full }
 		val_gen_loss_got, val_disc_loss_got = sess.run([gen_loss, disc_loss], feed_dict = feed_dict)
@@ -172,10 +172,10 @@ class aaeexp(object):
 			self.gaus_sample.initialize_batch('train')
 			self.attrdata.initialize_batch('train')
 			while self.data.has_next_batch():
-				X_batch, _, _, _, index_vector = self.data.next_batch()
+				X_batch, Y_batch, _, _, _ = self.data.next_batch()
 				Z_batch, _, _, _, _ = self.gaus_sample.next_batch()
[…]

### 2017-12-01 code/run.py

@@ -22,7 +22,9 @@ def main(_):
 	epoch_max = 100
 
 	train_size = 5994
-	test_size = 5794
+	#val_size = ...
+	#test_size = 5794
+	test_size = 5994
 	#reg_lambda = 1.0 / train_size
 	reg_lambda = 0
 
@@ -33,9 +35,10 @@ def main(_):
 
 	train_file_name = '../../project/data/preprocessed/training.txt'
 	val_file_name = '../../project/data/preprocessed/testing.txt'
-	test_file_name = '../../project/data/preprocessed/testing.txt'
+	#test_file_name = '../../project/data/preprocessed/testing.txt'
+	test_file_name = "../../project/data/preprocessed/training.txt"
 
-	log_file_name_head = './log/log_02'
+	log_file_name_head = './log/log_03'
 
 	gaus_train_file_name = '../../project/data/gaussian/gaus_sample_train.txt'
 	gaus_val_file_name = '../../project/data/gaussian/gaus_sample_valid.txt'

### 2017-12-01 code/aaeexp.py
.

@@ -229,5 +229,5 @@ class aaeexp(object):
 
 
 		#print_string = 'Total epoch = %d, test gen loss = %f, test disc loss = %f, total time = %f' % (epoch + 1, test_gen_loss_got, test_disc_loss_got, total_time)
-		print_string = "Total epoch = %d, test accuracy = %f" % (epoch + 1, test_accuracy)
+		print_string = "Total epoch = %d, test accuracy = %f, total time = %f" % (epoch + 1, test_accuracy, total_time)
 		print(print_string)

### 2017-12-01 code/run.py

@@ -19,7 +19,7 @@ def main(_):
 	lrn_rate = 0.02
 	momentum = 0.9
 	batch_size_train = 16
-	epoch_max = 100
+	epoch_max = 500
 
 	train_size = 5994
 	#val_size = ...

### 2017-12-01 doc/supplementary.tex
Added supplementary section for prior as guide.

@@
 
-	The encoder, decoder, and generator are the same as described in the previous section.
-The difference is that we use the text representation instead of Gaussian noise as the prior in the adversarial net.
-For an input image $\bb{x}^{(i)}$ of class $c_i$ and the text representation $\bb{t}^{c_i}$ of this class,
+	The encoder, decoder, generator, and discriminator are the same as described in the previous section.
+The difference is that we use the text representation, instead of Gaussian noise, as the prior in the adversarial net.
+For an input image $\bb{x}^{(i)}$ of class $c_i$ and the text representation $\bb{t}^{c_i}$ of this class, we use $\bb{t}^{c_i}$ as the sample drawn from some underlying prior for the representation distribution of this class,
+	\begin{align}
+		\bb{z}^{c_i} = \bb{t}^{c_i}.
+	\end{align}
+	In addition, we remove the term measuring the L2 distance between the text representation and the hidden representation of the image from the loss function.
+
+	The loss function for the autoencoder and the generator is now the standard one,
+	\begin{align}
+		f_g = \frac{1}{|S|} \sum_{i \in S} \left\{ -\bb{x}^{(i)} \odot \log \tilde{\bb{x}}^{(i)} + \log\left[ 1 - D( \bb{h}^{(i)} ) \right] \right\}.
+	\end{align}
+	For the discriminator of the adversarial net, the loss function is
+	\begin{align}
+		f_d = -\frac{1}{|S|} \sum_{i \in S} \log D( \bb{z}^{(i)} ) - \frac{1}{|S|} \sum_{i \in S} \log\left[ 1 - D( \bb{h}^{(i)} ) \right],
+	\end{align}
+	where $\bb{z}^{(i)}$ is the corresponding text representation $\bb{t}^{c_i}$ for the image $\bb{x}^{(i)}$ belonging to class $c_i$.
+
+	The optimization and test procedures are the same as those described in the previous section.
 

### 2017-12-02 code/aaeexp.py
Added and tested top-k classification accuracy.

@@ -165,7 +165,8 @@ class aaeexp(object):
 		#self.write_log(log_file, -1, 0.0, X, Z, None, sess, gen_loss, disc_loss)
 
 		total_time_begin = time.time()
-		for epoch in range(self.epoch_max):
+		epoch = 0
+		while epoch < self.epoch_max:
 			time_begin = time.time()
 
 			self.data.initialize_batch('train')
@@ -193,6 +194,8 @@ class aaeexp(object):
 			# Confirmed: Does not make difference
 			self.write_log(log_file, epoch, time_epoch, X, Z, T, sess, gen_loss, disc_loss, train_gen_loss_given = train_gen_loss_got, train_disc_loss_given = train_disc_loss_got)
 			#self.write_log(log_file, epoch, time_epoch, X, Z, None, sess, gen_loss, disc_loss, train_gen_loss_given = train_gen_loss_got, train_disc_loss_given = train_disc_loss_got)
+
+			epoch += 1
 		# End of all epochs
 		total_time_end = time.time()
 		total_time = total_time_end - total_time_begin
@@ -211,23 +214,35 @@ class aaeexp(object):
 		#test_gen_loss_got, test_disc_loss_got = sess.run([gen_loss, disc_loss], feed_dict = feed_dict)
 
 		t = tf.placeholder(tf.float32, [self.hid_dim])
-		dist_from_t = tf.reduce_sum( tf.pow(H - t, 2), axis = 1 )
+		# Compute negative distance, in order to pick top k as shortest distances
+		neg_dist_from_t = -tf.reduce_sum( tf.pow(H - t, 2), axis = 1 )
 
 		# Attribute row vectors of unsceen classes
 		T_test_full = self.attrdata.test_X
 
-		dist_matrix = []
+		neg_neg_dist_matrix = []
 
 		for t_vec in T_test_full:
 			feed_dict = { X: X_test_full, t: t_vec }
-			dist_matrix.append( sess.run(dist_from_t, feed_dict = feed_dict) )
+			neg_dist_matrix.append( sess.run(neg_dist_from_t, feed_dict = feed_dict) )
 
-		y_pred = np.array(dist_matrix).argmax(axis = 0)
-		del dist_matrix
+		y_pred = sess.run( tf.nn.top_k( tf.transpose( tf.convert_to_tensor(np.array(neg_dist_matrix)) ), k = T_test_full.shape[0] ).indices )
[…]

### 2017-12-02 code/plot_y_pred_pos.py

@@ -1,0 +1,16 @@
+from __future__ import division
+
+import matplotlib.pyplot as plt
+import numpy as np
+
+
+y_pred_pos = np.load("./log/log_05_y_pred_pos.npy")
+idx = np.array(range(y_pred_pos.shape[0]))
+
+plt.figure(1)
+plt.plot(idx, y_pred_pos, 'ko')
+#plt.xlim([0, 11])
+#plt.ylim([0, 0.5])
+plt.xlabel('Instance index')
+plt.ylabel('Rank of the true label in prediction results')
+plt.savefig('./log/fig_05_y_pred_pos_itr_1000.pdf')

### 2017-12-02 code/run.py

@@ -19,12 +19,11 @@ def main(_):
 	lrn_rate = 0.02
 	momentum = 0.9
 	batch_size_train = 16
-	epoch_max = 500
+	epoch_max = 1000
 
 	train_size = 5994
 	#val_size = ...
-	#test_size = 5794
-	test_size = 5994
+	test_size = 5794
 	#reg_lambda = 1.0 / train_size
 	reg_lambda = 0
 
@@ -35,10 +34,10 @@ def main(_):
 
 	train_file_name = '../../project/data/preprocessed/training.txt'
 	val_file_name = '../../project/data/preprocessed/testing.txt'
-	#test_file_name = '../../project/data/preprocessed/testing.txt'
-	test_file_name = "../../project/data/preprocessed/training.txt"
+	test_file_name = '../../project/data/preprocessed/testing.txt'
+	#test_file_name = "../../project/data/preprocessed/training.txt"
 
-	log_file_name_head = './log/log_03'
+	log_file_name_head = './log/log_05'
 
 	gaus_train_file_name = '../../project/data/gaussian/gaus_sample_train.txt'
 	gaus_val_file_name = '../../project/data/gaussian/gaus_sample_valid.txt'

### 2017-12-02 code/aeexp.py
Major revision. Working version of: (1) AAE with explicit matching (aaeexp.py), (2) AE (no adversarial) with explicit matching (aeexp.py). Updated attrdataset.py. Re-organized. Changed Guassian prior parameters to encourage sparse encoding. CUB_200_2011 dataset has been re-cut into training (130 classes), validation (20 classes), test (50 classes) sets.

@@ -10,7 +10,7 @@ import dataset
 import attrdataset
 
 
-class aaeexp(object):
+class aeexp(object):
 	def __init__(self, input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_file_name, write_model_log_period):
 		self.input_dim = input_dim
 		self.hid_dim = hid_dim
@@ -41,7 +41,7 @@ class aaeexp(object):
 	def eval_gen_loss(self, ave_entropy, disc_res_neg, H, T):
 		# Note that tf.nn.l2_loss() has already included the 1/2 factor
 		# loss = ave_entropy + self.reg_lambda * ( tf.nn.l2_loss(W_e) )
-		gen_loss = ave_entropy + tf.reduce_mean( tf.log( 1.0 - disc_res_neg ) ) + tf.losses.mean_squared_error( T, H )
+		gen_loss = ave_entropy + tf.losses.mean_squared_error( T, H )
 		return gen_loss
 	
 
@@ -55,7 +55,7 @@ class aaeexp(object):
 
 	def eval_disc_loss(self, disc_res_pos, disc_res_neg):
 		# loss = ave_entropy + self.reg_lambda * ( tf.nn.l2_loss(W_e) )
-		disc_loss = -tf.reduce_mean( tf.log( disc_res_pos ) ) - tf.reduce_mean( tf.log( 1.0 - disc_res_neg ) )
+		disc_loss = tf.constant(0.0, dtype = tf.float32)
 		return disc_loss
 
 
@@ -155,7 +155,6 @@ class aaeexp(object):
 		disc_loss = self.eval_disc_loss(disc_res_pos, disc_res_neg)
 
 		train_gen_step = tf.train.MomentumOptimizer(self.lrn_rate, self.momentum).minimize(gen_loss)
-		train_disc_step = tf.train.MomentumOptimizer(self.lrn_rate, self.momentum).minimize(disc_loss)
 
 		sess = tf.Session()
 		sess.run( tf.global_variables_initializer() )
@@ -180,7 +179,7 @@ class aaeexp(object):
 				feed_dict = { X: X_batch, Z: Z_batch, T: T_batch }
 				#feed_dict = { X: X_batch, Z: Z_batch }
[…]

### 2017-12-02 code/attrdataset.py

@@ -8,29 +8,23 @@ import numpy as np
 # In this class, the files are .npy files stored with numpy ndarray
 # Note that there is no class_num
 class attrdataset(object):
-	def __init__(self, train_file_name, val_file_name, test_file_name):
-		self.train_X = self.get_X(train_file_name)
-		self.val_X = self.get_X(val_file_name)
-		self.test_X = self.get_X(test_file_name)
-
-		self.dataset_name = ''
+	def __init__(self, file_name):
+		self.X = self.get_X(file_name)
 
 
 	def get_X(self, file_name):
 		X = np.load(file_name)
 		return X.astype(np.float32)
 
-	def initialize_batch(self, dataset_name):
-		self.dataset_name = dataset_name
+
+	"""
+	def initialize_batch(self):
+		pass
+	"""
 
 
 	# Assert: there is next batch
 	def next_batch(self, index_vector):
-		if self.dataset_name == 'train' or self.dataset_name == 'train_init':
-			output_X = self.train_X[index_vector, :]
-		elif self.dataset_name == 'val':
-			output_X = self.val_X[index_vector, :]
-		elif self.dataset_name == 'test':
-			output_X = self.test_X[index_vector, :]
+		output_X = self.X[index_vector, :]
 
 		return output_X

### 2017-12-02 code/gen_gaus_sample.py

@@ -6,9 +6,9 @@ import numpy as np
 
 
 def main():
-	gaus_prior_mean = 0.5
-	gaus_prior_stddev = 0.2
-	batch_size = 5994
+	gaus_prior_mean = 0.0
+	gaus_prior_stddev = 0.05
+	batch_size = 7626
 	hid_dim = 312
 	pos_sample = np.random.normal(gaus_prior_mean, gaus_prior_stddev, [batch_size, hid_dim])
 
@@ -27,7 +27,7 @@ def main():
 		pos_sample_train_file.write(str_to_write)
 
 
-	batch_size = 5794
+	batch_size = 1196
 	pos_sample = np.random.normal(gaus_prior_mean, gaus_prior_stddev, [batch_size, hid_dim])
 
 	pos_sample_train_file_name = './gaus_sample_valid.txt'
@@ -45,7 +45,7 @@ def main():
 		pos_sample_train_file.write(str_to_write)
 
 
-	batch_size = 5994
+	batch_size = 2966
 	pos_sample = np.random.normal(gaus_prior_mean, gaus_prior_stddev, [batch_size, hid_dim])
 
 	pos_sample_train_file_name = './gaus_sample_test.txt'

### 2017-12-02 code/obsolete/attrdataset_1202.py

@@ -1,0 +1,36 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import numpy as np
+
+
+# In this class, the files are .npy files stored with numpy ndarray
+# Note that there is no class_num
+class attrdataset(object):
+	def __init__(self, train_file_name, val_file_name, test_file_name):
+		self.train_X = self.get_X(train_file_name)
+		self.val_X = self.get_X(val_file_name)
+		self.test_X = self.get_X(test_file_name)
+
+		self.dataset_name = ''
+
+
+	def get_X(self, file_name):
+		X = np.load(file_name)
+		return X.astype(np.float32)
+
+	def initialize_batch(self, dataset_name):
+		self.dataset_name = dataset_name
+
+
+	# Assert: there is next batch
+	def next_batch(self, index_vector):
+		if self.dataset_name == 'train' or self.dataset_name == 'train_init':
+			output_X = self.train_X[index_vector, :]
+		elif self.dataset_name == 'val':
+			output_X = self.val_X[index_vector, :]
+		elif self.dataset_name == 'test':
+			output_X = self.test_X[index_vector, :]
+
+		return output_X

### 2017-12-02 code/obsolete/run_1202.py

@@ -16,10 +16,10 @@ def main(_):
 
 	d1 = 100
 
-	lrn_rate = 0.02
+	lrn_rate = 0.05		#0.02
 	momentum = 0.9
 	batch_size_train = 16
-	epoch_max = 1000
+	epoch_max = 100
 
 	train_size = 5994
 	#val_size = ...
@@ -37,7 +37,7 @@ def main(_):
 	test_file_name = '../../project/data/preprocessed/testing.txt'
 	#test_file_name = "../../project/data/preprocessed/training.txt"
 
-	log_file_name_head = './log/log_05'
+	log_file_name_head = './log/log_08'
 
 	gaus_train_file_name = '../../project/data/gaussian/gaus_sample_train.txt'
 	gaus_val_file_name = '../../project/data/gaussian/gaus_sample_valid.txt'

### 2017-12-02 code/obsolete/run_lrn_0p02_best.py

@@ -1,0 +1,57 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import tensorflow as tf
+import dataset
+import aaeexp
+#import aae
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.02
+	momentum = 0.9
+	batch_size_train = 16
+	epoch_max = 100
+
+	train_size = 5994
+	#val_size = ...
+	test_size = 5794
+	#reg_lambda = 1.0 / train_size
+	reg_lambda = 0
+
+	# Redundant for autoencoder
+	class_num = 200
+
+	write_model_log_period = 10
+
+	train_file_name = '../../project/data/preprocessed/training.txt'
+	val_file_name = '../../project/data/preprocessed/testing.txt'
+	test_file_name = '../../project/data/preprocessed/testing.txt'
+	#test_file_name = "../../project/data/preprocessed/training.txt"
+
+	log_file_name_head = './log/log_05'
+
+	gaus_train_file_name = '../../project/data/gaussian/gaus_sample_train.txt'
+	gaus_val_file_name = '../../project/data/gaussian/gaus_sample_valid.txt'
+	gaus_test_file_name = '../../project/data/gaussian/gaus_sample_test.txt'
+
+	attr_train_file_name = '../../project/data/preprocessed/attribute_embeddings.npy'
+	attr_val_file_name = '../../project/data/preprocessed/attribute_embeddings.npy'
+	attr_test_file_name = '../../project/data/preprocessed/attribute_embeddings.npy'
+
+	aaeexp_machine = aaeexp.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_train_file_name, attr_val_file_name, attr_test_file_name, write_model_log_period)
+	#aae_machine = aae.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, None, None, None, write_model_log_period)
+
+	aaeexp_machine.train()
[…]

### 2017-12-02 code/obsolete/run_lrn_0p02_data_1202.py

@@ -1,0 +1,57 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import tensorflow as tf
+import dataset
+import aaeexp
+#import aae
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.02
+	momentum = 0.9
+	batch_size_train = 16
+	epoch_max = 100
+
+	train_size = 7626
+	val_size = 1196
+	test_size = 2966
+	#reg_lambda = 1.0 / train_size
+	reg_lambda = 0
+
+	# Redundant for autoencoder
+	class_num = 200
+
+	write_model_log_period = 10
+
+	train_file_name = "../../project/data/CUB_200_2011_1202/training.txt"
+	val_file_name = "../../project/data/CUB_200_2011_1202/validation.txt"
+	test_file_name = "../../project/data/CUB_200_2011_1202/testing.txt"
+	#test_file_name = "../../project/data/preprocessed/training.txt"
+
+	log_file_name_head = "./log/log_08_lrn_0p02_data_1202"
+
+	gaus_train_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_train.txt"
+	gaus_val_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_valid.txt"
+	gaus_test_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_test.txt"
+
+	attr_train_file_name = "../../project/data/CUB_200_2011_preprocessed/attribute_embeddings.npy"
+	attr_val_file_name = "../../project/data/CUB_200_2011_preprocessed/attribute_embeddings.npy"
+	attr_test_file_name = "../../project/data/CUB_200_2011_preprocessed/attribute_embeddings.npy"
+
+	aaeexp_machine = aaeexp.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_train_file_name, attr_val_file_name, attr_test_file_name, write_model_log_period)
[…]

### 2017-12-02 code/obsolete/run_lrn_0p1.py

@@ -1,0 +1,57 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import tensorflow as tf
+import dataset
+import aaeexp
+#import aae
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.1
+	momentum = 0.9
+	batch_size_train = 16
+	epoch_max = 100
+
+	train_size = 5994
+	#val_size = ...
+	test_size = 5794
+	#reg_lambda = 1.0 / train_size
+	reg_lambda = 0
+
+	# Redundant for autoencoder
+	class_num = 200
+
+	write_model_log_period = 10
+
+	train_file_name = '../../project/data/preprocessed/training.txt'
+	val_file_name = '../../project/data/preprocessed/testing.txt'
+	test_file_name = '../../project/data/preprocessed/testing.txt'
+	#test_file_name = "../../project/data/preprocessed/training.txt"
+
+	log_file_name_head = './log/log_07'
+
+	gaus_train_file_name = '../../project/data/gaussian/gaus_sample_train.txt'
+	gaus_val_file_name = '../../project/data/gaussian/gaus_sample_valid.txt'
+	gaus_test_file_name = '../../project/data/gaussian/gaus_sample_test.txt'
+
+	attr_train_file_name = '../../project/data/preprocessed/attribute_embeddings.npy'
+	attr_val_file_name = '../../project/data/preprocessed/attribute_embeddings.npy'
+	attr_test_file_name = '../../project/data/preprocessed/attribute_embeddings.npy'
+
+	aaeexp_machine = aaeexp.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_train_file_name, attr_val_file_name, attr_test_file_name, write_model_log_period)
+	#aae_machine = aae.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, None, None, None, write_model_log_period)
+
+	aaeexp_machine.train()
[…]

### 2017-12-02 code/plot_y_pred_pos.py

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 
 
-y_pred_pos = np.load("./log/log_05_y_pred_pos.npy")
+y_pred_pos = np.load("./log/log_10_lrn_0p02_data_1202_y_pred_pos.npy")
 idx = np.array(range(y_pred_pos.shape[0]))
 
 plt.figure(1)
@@ -13,4 +13,4 @@ plt.plot(idx, y_pred_pos, 'ko')
 #plt.ylim([0, 0.5])
 plt.xlabel('Instance index')
 plt.ylabel('Rank of the true label in prediction results')
-plt.savefig('./log/fig_05_y_pred_pos_itr_1000.pdf')
+plt.savefig('./log/fig_10_lrn_0p02_data_1202_y_pred_pos_itr_1000.pdf')

### 2017-12-02 code/run_09_lrn_0p02_data_1202_only_ae_exp.py

@@ -1,0 +1,57 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import tensorflow as tf
+import dataset
+import aaeexp
+#import aae
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.02
+	momentum = 0.9
+	batch_size_train = 16
+	epoch_max = 100
+
+	train_size = 7626
+	val_size = 1196
+	test_size = 2966
+	#reg_lambda = 1.0 / train_size
+	reg_lambda = 0
+
+	# Redundant for autoencoder
+	class_num = 200
+
+	write_model_log_period = 10
+
+	train_file_name = "../../project/data/CUB_200_2011_1202/training.txt"
+	val_file_name = "../../project/data/CUB_200_2011_1202/validation.txt"
+	test_file_name = "../../project/data/CUB_200_2011_1202/testing.txt"
+	#test_file_name = "../../project/data/preprocessed/training.txt"
+
+	log_file_name_head = "./log/log_09_lrn_0p02_data_1202_only_ae_exp"
+
+	gaus_train_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_train.txt"
+	gaus_val_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_valid.txt"
+	gaus_test_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_test.txt"
+
+	attr_train_file_name = "../../project/data/CUB_200_2011_preprocessed/attribute_embeddings.npy"
+	attr_val_file_name = "../../project/data/CUB_200_2011_preprocessed/attribute_embeddings.npy"
+	attr_test_file_name = "../../project/data/CUB_200_2011_preprocessed/attribute_embeddings.npy"
+
+	aaeexp_machine = aaeexp.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_train_file_name, attr_val_file_name, attr_test_file_name, write_model_log_period)
[…]

### 2017-12-02 code/run_10_lrn_0p02_data_1202.py

@@ -1,0 +1,54 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import tensorflow as tf
+import dataset
+import aaeexp
+#import aae
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.02
+	momentum = 0.9
+	batch_size_train = 16
+	epoch_max = 1000
+
+	train_size = 7626
+	val_size = 1196
+	test_size = 2966
+	#reg_lambda = 1.0 / train_size
+	reg_lambda = 0
+
+	# Redundant for autoencoder
+	class_num = 200
+
+	write_model_log_period = 10
+
+	train_file_name = "../../project/data/CUB_200_2011_1202/training.txt"
+	val_file_name = "../../project/data/CUB_200_2011_1202/validation.txt"
+	test_file_name = "../../project/data/CUB_200_2011_1202/testing.txt"
+
+	log_file_name_head = "./log/log_10_lrn_0p02_data_1202"
+
+	gaus_train_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_train.txt"
+	gaus_val_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_valid.txt"
+	gaus_test_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_test.txt"
+
+	attr_file_name = "../../project/data/CUB_200_2011_preprocessed/attribute_embeddings.npy"
+
+	aaeexp_machine = aaeexp.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_file_name, write_model_log_period)
+	#aae_machine = aae.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, None, None, None, write_model_log_period)
+
+	aaeexp_machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-02 code/run_11_lrn_0p02_data_1202_only_aeexp.py

@@ -1,0 +1,55 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import tensorflow as tf
+import dataset
+#import aaeexp
+#import aae
+import aeexp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.02
+	momentum = 0.9
+	batch_size_train = 16
+	epoch_max = 1000
+
+	train_size = 7626
+	val_size = 1196
+	test_size = 2966
+	#reg_lambda = 1.0 / train_size
+	reg_lambda = 0
+
+	# Redundant for autoencoder
+	class_num = 200
+
+	write_model_log_period = 10
+
+	train_file_name = "../../project/data/CUB_200_2011_1202/training.txt"
+	val_file_name = "../../project/data/CUB_200_2011_1202/validation.txt"
+	test_file_name = "../../project/data/CUB_200_2011_1202/testing.txt"
+
+	log_file_name_head = "./log/log_11_lrn_0p02_data_1202_only_aeexp"
+
+	gaus_train_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_train.txt"
+	gaus_val_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_valid.txt"
+	gaus_test_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_test.txt"
+
+	attr_file_name = "../../project/data/CUB_200_2011_preprocessed/attribute_embeddings.npy"
+
+	aeexp_machine = aeexp.aeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_file_name, write_model_log_period)
+	#aae_machine = aae.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, None, None, None, write_model_log_period)
+
+	aeexp_machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-03 code/plot_loss.py
do exp and plot loss curve.

@@ -1,0 +1,65 @@
+from __future__ import division
+
+import matplotlib.pyplot as plt
+import numpy as np
+import re
+
+
+log_file = open("./log/log_10_lrn_0p02_data_1202.txt")
+
+epoch = []
+train_gen_loss = []
+train_disc_loss = []
+val_gen_loss = []
+val_disc_loss = []
+
+for line in log_file:
+	if line[0] == "T":
+		pass
+	else:
+		_epoch, _train_gen_loss, _train_disc_loss, _val_gen_loss, _val_disc_loss, _ = re.split("\t", line)
+		epoch.append(int(_epoch))
+		train_gen_loss.append(float(_train_gen_loss))
+		train_disc_loss.append(float(_train_disc_loss))
+		val_gen_loss.append(float(_val_gen_loss))
+		val_disc_loss.append(float(_val_disc_loss))
+
+plt.figure(1)
+plt.plot(epoch, train_gen_loss, "k-", label = "train gen loss")
+plt.plot(epoch, train_disc_loss, "r-", label = "train disc loss")
+#plt.plot(epoch, val_gen_loss, "k--", label = "val gen loss")
+#plt.plot(epoch, val_gen_loss, "r--", label = "val disc loss")
+plt.xlim([-1, 50])
+plt.ylim([-0.5, 1.5])
+plt.legend()
+plt.xlabel("Epoch")
+plt.ylabel("Loss")
+plt.savefig('./log/fig_10_lrn_0p02_data_1202_zoomin.pdf')
+
+
+plt.figure(2)
+plt.plot(epoch, train_gen_loss, "k-", label = "train gen loss")
+plt.plot(epoch, train_disc_loss, "r-", label = "train disc loss")
+#plt.plot(epoch, val_gen_loss, "k--", label = "val gen loss")
+#plt.plot(epoch, val_gen_loss, "r--", label = "val disc loss")
+#plt.xlim([-1, 50])
+plt.ylim([-0.5, 1.5])
+plt.legend()
+plt.xlabel("Epoch")
+plt.ylabel("Loss")
+plt.savefig('./log/fig_10_lrn_0p02_data_1202.pdf')
+
+
+plt.figure(3)
+#plt.plot(epoch, train_gen_loss, "k-", label = "train gen loss")
+#plt.plot(epoch, train_disc_loss, "r-", label = "train disc loss")
[…]

### 2017-12-03 code/aeexpsae.py
Writing the SAE implementation...

@@ -1,0 +1,226 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import numpy as np
+import tensorflow as tf
+import dataset
+import attrdataset
+
+
+class aeexpsae(object):
+	def __init__(self, input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_file_name, write_model_log_period, lambda_coef):
+		self.input_dim = input_dim
+		self.hid_dim = hid_dim
+		self.class_num = class_num
+		self.d1 = d1
+		self.lrn_rate = lrn_rate
+		self.momentum = momentum
+		self.batch_size_train = batch_size_train
+		self.epoch_max = epoch_max
+		self.reg_lambda = reg_lambda
+		self.log_file_name_head = log_file_name_head
+		self.write_model_log_period = write_model_log_period
+		self.lambda_coef = lambda_coef
+
+		self.data = dataset.dataset(train_file_name, val_file_name, test_file_name, class_num, batch_size_train)
+		self.gaus_sample = dataset.dataset(gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, class_num, batch_size_train)
+		self.attrdata = attrdataset.attrdataset(attr_file_name)
+
+		#self.graph = tf.Graph()
+
+
+	"""
+	# Loss functions for joint training
+	def eval_entropy(self, X_tilde_logit, X):
+		entropy = tf.nn.sigmoid_cross_entropy_with_logits(labels = X, logits = X_tilde_logit)
+		ave_entropy = tf.reduce_mean(entropy)
+		return ave_entropy
+	"""
+
+	
+	def eval_gen_loss(self, X, WTS, WX, S):
+		# Note that tf.nn.l2_loss() has already included the 1/2 factor
+		# loss = ave_entropy + self.reg_lambda * ( tf.nn.l2_loss(W_e) )
[…]

### 2017-12-03 code/aaeexp.py
Fixed bugs. Added matching coefficient option for aaeexp.py.

@@ -11,7 +11,7 @@ import attrdataset
 
 
 class aaeexp(object):
-	def __init__(self, input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_file_name, write_model_log_period):
+	def __init__(self, input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_file_name, write_model_log_period, match_coef = 1):
 		self.input_dim = input_dim
 		self.hid_dim = hid_dim
 		self.class_num = class_num
@@ -23,6 +23,7 @@ class aaeexp(object):
 		self.reg_lambda = reg_lambda
 		self.log_file_name_head = log_file_name_head
 		self.write_model_log_period = write_model_log_period
+		self.match_coef = match_coef
 
 		self.data = dataset.dataset(train_file_name, val_file_name, test_file_name, class_num, batch_size_train)
 		self.gaus_sample = dataset.dataset(gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, class_num, batch_size_train)
@@ -33,15 +34,16 @@ class aaeexp(object):
 
 	# Loss functions for joint training
 	def eval_entropy(self, X_tilde_logit, X):
-		entropy = tf.nn.sigmoid_cross_entropy_with_logits(labels = X, logits = X_tilde_logit)
-		ave_entropy = tf.reduce_mean(entropy)
+		#ave_entropy = tf.reduce_mean( tf.reduce_sum( tf.nn.sigmoid_cross_entropy_with_logits(labels = X, logits = X_tilde_logit), axis = 1 ) )
+		ave_entropy = tf.reduce_mean( tf.nn.sigmoid_cross_entropy_with_logits(labels = X, logits = X_tilde_logit) )
 		return ave_entropy
 
 	
 	def eval_gen_loss(self, ave_entropy, disc_res_neg, H, T):
[…]

### 2017-12-03 code/run_12_lrn_0p02_data_1202.py

@@ -1,0 +1,54 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import tensorflow as tf
+import dataset
+import aaeexp
+#import aae
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.02
+	momentum = 0.9
+	batch_size_train = 16
+	epoch_max = 100
+
+	train_size = 7626
+	val_size = 1196
+	test_size = 2966
+	#reg_lambda = 1.0 / train_size
+	reg_lambda = 0
+
+	# Redundant for autoencoder
+	class_num = 200
+
+	write_model_log_period = 10
+
+	train_file_name = "../../project/data/CUB_200_2011_1202/training.txt"
+	val_file_name = "../../project/data/CUB_200_2011_1202/validation.txt"
+	test_file_name = "../../project/data/CUB_200_2011_1202/testing.txt"
+
+	log_file_name_head = "./log/log_12_lrn_0p02_data_1202"
+
+	gaus_train_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_train.txt"
+	gaus_val_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_valid.txt"
+	gaus_test_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_test.txt"
+
+	attr_file_name = "../../project/data/CUB_200_2011_preprocessed/attribute_embeddings.npy"
+
+	aaeexp_machine = aaeexp.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_file_name, write_model_log_period)
+	#aae_machine = aae.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, None, None, None, write_model_log_period)
+
+	aaeexp_machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-03 code/run_14_lrn_0p02_data_1202_match_100.py

@@ -1,0 +1,56 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import tensorflow as tf
+import dataset
+import aaeexp
+#import aae
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.02
+	momentum = 0.9
+	batch_size_train = 16
+	epoch_max = 100
+
+	match_coef = 100
+
+	train_size = 7626
+	val_size = 1196
+	test_size = 2966
+	#reg_lambda = 1.0 / train_size
+	reg_lambda = 0
+
+	# Redundant for autoencoder
+	class_num = 200
+
+	write_model_log_period = 10
+
+	train_file_name = "../../project/data/CUB_200_2011_1202/training.txt"
+	val_file_name = "../../project/data/CUB_200_2011_1202/validation.txt"
+	test_file_name = "../../project/data/CUB_200_2011_1202/testing.txt"
+
+	log_file_name_head = "./log/log_14_lrn_0p02_data_1202_match_100"
+
+	gaus_train_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_train.txt"
+	gaus_val_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_valid.txt"
+	gaus_test_file_name = "../../project/data/gaussian/gaus_sample_for_CUB_200_2011_1202/gaus_sample_test.txt"
+
+	attr_file_name = "../../project/data/CUB_200_2011_preprocessed/attribute_embeddings.npy"
+
+	aaeexp_machine = aaeexp.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_file_name, write_model_log_period, match_coef = match_coef)
+	#aae_machine = aae.aaeexp(input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, None, None, None, write_model_log_period)
+
[…]

### 2017-12-11 code/aaeexp.py
AAE exp is ready.

@@ -7,106 +7,154 @@ import time
 import numpy as np
 import tensorflow as tf
 import dataset
-import attrdataset
 
 
 class aaeexp(object):
-	def __init__(self, input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_train_file_name, attr_val_file_name, attr_test_file_name, write_model_log_period, match_coef = 1, train_label_file_name = None, val_label_file_name = None, test_label_file_name = None, load_model_file_directory = None):
+	def __init__(self,
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max, momentum = 0.0,
+		gaus_mean = 0.0, gaus_stddev = 1.0,
+		coef_match = 1.0, coef_recon = 1.0, coef_gan = 1.0,
+		unseen_class_file_name = None,
+		train_file_name = None,
+		val_file_name = None,
+		test_file_name = None,
+		train_label_file_name = None,
+		val_label_file_name = None,
+		test_label_file_name = None,
+		train_attr_file_name = None,
+		val_attr_file_name = None,
+		test_attr_file_name = None,
+		log_file_name_head = None, save_model_period = 1,
+		load_model_directory = None,
+		generalizedZSL = False):
+
 		self.input_dim = input_dim
 		self.hid_dim = hid_dim
-		self.class_num = class_num
 		self.d1 = d1
+
 		self.lrn_rate = lrn_rate
-		self.momentum = momentum
-		self.batch_size_train = batch_size_train
+		self.train_batch_size = train_batch_size
 		self.epoch_max = epoch_max
-		self.reg_lambda = reg_lambda
+		self.momentum = momentum
+
+		self.gaus_mean = gaus_mean
+		self.gaus_stddev = gaus_stddev
+
+		self.coef_match = coef_match
+		self.coef_recon = coef_recon
+		self.coef_gan = coef_gan
+
+		self.unseen_class = np.load(unseen_class_file_name)
+
 		self.log_file_name_head = log_file_name_head
-		self.write_model_log_period = write_model_log_period
-		self.match_coef = match_coef
[…]

### 2017-12-11 code/archive/aaeexp_1211.py

@@ -1,0 +1,289 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import numpy as np
+import tensorflow as tf
+import dataset
+import attrdataset
+
+
+class aaeexp(object):
+	def __init__(self, input_dim, hid_dim, class_num, d1, lrn_rate, momentum, batch_size_train, epoch_max, reg_lambda, train_file_name, val_file_name, test_file_name, log_file_name_head, gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, attr_train_file_name, attr_val_file_name, attr_test_file_name, write_model_log_period, match_coef = 1, train_label_file_name = None, val_label_file_name = None, test_label_file_name = None, load_model_file_directory = None):
+		self.input_dim = input_dim
+		self.hid_dim = hid_dim
+		self.class_num = class_num
+		self.d1 = d1
+		self.lrn_rate = lrn_rate
+		self.momentum = momentum
+		self.batch_size_train = batch_size_train
+		self.epoch_max = epoch_max
+		self.reg_lambda = reg_lambda
+		self.log_file_name_head = log_file_name_head
+		self.write_model_log_period = write_model_log_period
+		self.match_coef = match_coef
+		self.load_model_file_directory = load_model_file_directory
+
+		self.data = dataset.dataset(train_file_name, val_file_name, test_file_name, class_num, batch_size_train = batch_size_train, train_label_file_name = train_label_file_name, val_label_file_name = val_label_file_name, test_label_file_name = test_label_file_name)
+		self.gaus_sample = dataset.dataset(gaus_train_file_name, gaus_val_file_name, gaus_test_file_name, class_num, batch_size_train = batch_size_train)
+		self.attrdata = attrdataset.attrdataset(attr_train_file_name, attr_val_file_name, attr_test_file_name)
+
+		#self.graph = tf.Graph()
+
+
+	def train(self):
+		#with self.graph.as_default():
+		
+		sess = tf.Session()
+
+		if self.load_model_file_directory == None:
[…]

### 2017-12-11 code/run_75_exp_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_75_exp_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp.aaeexp(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
[…]

### 2017-12-11 code/run_76_exp_AwA_sZSL_lrn_0p2_match_10_recon_1_gan_1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 10
+	coef_recon = 1
+	coef_gan = 1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_76_exp_AwA_sZSL_lrn_0p2_match_10_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp.aaeexp(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
[…]

### 2017-12-11 code/run_77_exp_AwA_sZSL_lrn_0p2_match_1_recon_10_gan_1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 1
+	coef_recon = 10
+	coef_gan = 1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_77_exp_AwA_sZSL_lrn_0p2_match_1_recon_10_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp.aaeexp(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
[…]

### 2017-12-11 code/run_78_exp_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_10.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 10
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_78_exp_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_10"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp.aaeexp(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
[…]

### 2017-12-11 code/run_76_exp_AwA_sZSL_lrn_0p2_match_5_recon_1_gan_1.py
Run more experiments...

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 5
+	coef_recon = 1
+	coef_gan = 1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_76_exp_AwA_sZSL_lrn_0p2_match_5_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp.aaeexp(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
[…]

### 2017-12-11 code/run_79_exp_AwA_gZSL_lrn_0p2_match_1_recon_1_gan_1.py

@@ -22,7 +22,7 @@ def main(_):
 	gaus_mean = 0.21
 	gaus_stddev = 0.25
 
-	coef_match = 10
+	coef_match = 1
 	coef_recon = 1
 	coef_gan = 1
 
@@ -32,19 +32,19 @@ def main(_):
 
 	save_model_period = 1
 
-	generalizedZSL = False
+	generalizedZSL = True
 
-	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+	unseen_class_file_name = "../AwA_generalizedZSL/unseen_class.npy"
 
-	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
-	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+	train_file_name = "../AwA_generalizedZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_generalizedZSL/xTest_scaled.npy"
 
-	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
-	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+	train_label_file_name = "../AwA_generalizedZSL/yTrain.npy"
+	test_label_file_name = "../AwA_generalizedZSL/yTest.npy"
 
-	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+	test_attr_file_name = "../AwA_generalizedZSL/sTest_scaled.npy"
 
-	log_directory = "./log/log_76_exp_AwA_sZSL_lrn_0p2_match_10_recon_1_gan_1"
+	log_directory = "./log/log_79_exp_AwA_gZSL_lrn_0p2_match_1_recon_1_gan_1"
 	log_file_name_head = log_directory + "/log"
 	if not os.path.exists(log_directory):
 		os.makedirs(log_directory)

### 2017-12-11 code/run_80_exp_CUB_sZSL_lrn_0p2_match_1_recon_1_gan_1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.11
+	gaus_stddev = 0.20
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../CUB_200_2011_standardZSL/unseen_class.npy"
+
+	train_file_name = "../CUB_200_2011_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../CUB_200_2011_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../CUB_200_2011_standardZSL/yTrain.npy"
+	test_label_file_name = "../CUB_200_2011_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../CUB_200_2011_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_80_exp_CUB_sZSL_lrn_0p2_match_1_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp.aaeexp(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-11 code/run_81_exp_CUB_gZSL_lrn_0p2_match_1_recon_1_gan_1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.11
+	gaus_stddev = 0.20
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = True
+
+	unseen_class_file_name = "../CUB_200_2011_generalizedZSL/unseen_class.npy"
+
+	train_file_name = "../CUB_200_2011_generalizedZSL/xTrain_scaled.npy"
+	test_file_name = "../CUB_200_2011_generalizedZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../CUB_200_2011_generalizedZSL/yTrain.npy"
+	test_label_file_name = "../CUB_200_2011_generalizedZSL/yTest.npy"
+
+	test_attr_file_name = "../CUB_200_2011_generalizedZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_81_exp_CUB_gZSL_lrn_0p2_match_1_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp.aaeexp(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
[…]

### 2017-12-12 code/run_82_sae3_AwA_sZSL_lrn_0p2_match_1.py
.

@@ -1,0 +1,67 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import sae3
+
+
+def main(_):
+	input_dim = 1024
+	attr_dim = 85
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	coef_match = 1
+
+	train_size = 24295
+	test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_82_sae3_AwA_sZSL_lrn_0p2_match_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = sae3.sae3(
+		input_dim, attr_dim,
+		lrn_rate, train_batch_size, epoch_max, #momentum = momentum,
+		coef_match = coef_match,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
+		generalizedZSL = generalizedZSL)
+
+	machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-12 code/run_83_sae3_CUB_sZSL_lrn_0p2_match_1.py

@@ -2,17 +2,14 @@ from __future__ import absolute_import
 from __future__ import division
 from __future__ import print_function
 
-import math
-import time
 import os
 import tensorflow as tf
-import dataset
-import sae2
+import sae3
 
 
 def main(_):
 	input_dim = 1024
-	attr_dim = 85
+	attr_dim = 312
 
 	lrn_rate = 0.2
 	train_batch_size = 64
@@ -20,27 +17,27 @@ def main(_):
 
 	#momentum = 0.9
 
-	coef_match = 100
+	coef_match = 1
 
-	train_size = 24295
-	test_size = 6180
+	train_size = 8822
+	test_size = 2966
 	#reg_lambda = 1.0 / train_size
 
 	save_model_period = 1
 
 	generalizedZSL = False
 
-	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+	unseen_class_file_name = "../CUB_200_2011_standardZSL/unseen_class.npy"
 
-	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
-	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+	train_file_name = "../CUB_200_2011_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../CUB_200_2011_standardZSL/xTest_scaled.npy"
 
-	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
-	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+	train_label_file_name = "../CUB_200_2011_standardZSL/yTrain.npy"
+	test_label_file_name = "../CUB_200_2011_standardZSL/yTest.npy"
 
-	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+	test_attr_file_name = "../CUB_200_2011_standardZSL/sTest_scaled.npy"
 
-	log_directory = "./log/log_60_sae2_AwA_lrn_0p2_match_100"
+	log_directory = "./log/log_83_sae3_CUB_sZSL_lrn_0p2_match_1"
 	log_file_name_head = log_directory + "/log"
 	if not os.path.exists(log_directory):
 		os.makedirs(log_directory)
@@ -48,7 +45,7 @@ def main(_):
 	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
 	load_model_directory = None
 
-	machine = sae2.sae2(
[…]

### 2017-12-12 code/run_84_sae3_AwA_sZSL_lrn_0p2_match_0p01.py

@@ -2,17 +2,14 @@ from __future__ import absolute_import
 from __future__ import division
 from __future__ import print_function
 
-import math
-import time
 import os
 import tensorflow as tf
-import dataset
-import sae2
+import sae3
 
 
 def main(_):
 	input_dim = 1024
-	attr_dim = 312
+	attr_dim = 85
 
 	lrn_rate = 0.2
 	train_batch_size = 64
@@ -20,27 +17,27 @@ def main(_):
 
 	#momentum = 0.9
 
-	coef_match = 100
+	coef_match = 0.01
 
-	train_size = 8822
-	test_size = 2966
+	train_size = 24295
+	test_size = 6180
 	#reg_lambda = 1.0 / train_size
 
 	save_model_period = 1
 
 	generalizedZSL = False
 
-	unseen_class_file_name = "../CUB_200_2011_1202_standardZSL/unseen_class.npy"
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
 
-	train_file_name = "../CUB_200_2011_1202_standardZSL/xTrain_scaled.npy"
-	test_file_name = "../CUB_200_2011_1202_standardZSL/xTest_scaled.npy"
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
 
-	train_label_file_name = "../CUB_200_2011_1202_standardZSL/yTrain.npy"
-	test_label_file_name = "../CUB_200_2011_1202_standardZSL/yTest.npy"
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
 
-	test_attr_file_name = "../CUB_200_2011_1202_standardZSL/sTest_scaled.npy"
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
 
-	log_directory = "./log/log_59_sae2_CUB_sZSL_lrn_0p2_match_100"
+	log_directory = "./log/log_84_sae3_AwA_sZSL_lrn_0p2_match_0p01"
 	log_file_name_head = log_directory + "/log"
 	if not os.path.exists(log_directory):
 		os.makedirs(log_directory)
@@ -48,7 +45,7 @@ def main(_):
 	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
[…]

### 2017-12-12 code/run_85_sae3_CUB_sZSL_lrn_0p2_match_0p01.py

@@ -1,0 +1,67 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import sae3
+
+
+def main(_):
+	input_dim = 1024
+	attr_dim = 312
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	coef_match = 0.01
+
+	train_size = 8822
+	test_size = 2966
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../CUB_200_2011_standardZSL/unseen_class.npy"
+
+	train_file_name = "../CUB_200_2011_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../CUB_200_2011_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../CUB_200_2011_standardZSL/yTrain.npy"
+	test_label_file_name = "../CUB_200_2011_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../CUB_200_2011_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_85_sae3_CUB_sZSL_lrn_0p2_match_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = sae3.sae3(
+		input_dim, attr_dim,
+		lrn_rate, train_batch_size, epoch_max, #momentum = momentum,
+		coef_match = coef_match,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
+		generalizedZSL = generalizedZSL)
+
+	machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-12 code/sae3.py

@@ -196,11 +196,15 @@ class sae3(object):
 				dist_matrix = np.array(dist_matrix)
 
 				# Generalized zero-shot learning, test time both unseen and seen classes
-				_, test_top_1_accuracy, harmonic_top_1 = self.generalized_accuracy(dist_matrix, Y_test_full, k_of_topk = 1)
-				_, test_top_5_accuracy, harmonic_top_5 = self.generalized_accuracy(dist_matrix, Y_test_full, k_of_topk = 5)
+				#_, test_top_1_accuracy, harmonic_top_1 = self.generalized_accuracy(dist_matrix, Y_test_full, k_of_topk = 1)
+				#_, test_top_5_accuracy, harmonic_top_5 = self.generalized_accuracy(dist_matrix, Y_test_full, k_of_topk = 5)
+				_, test_top_1_accuracy, _ = self.generalized_accuracy(dist_matrix, Y_test_full, k_of_topk = 1)
 
-				print_string = "%d\t%f\t%f\n  %f%%\t%f%%\t%f%%\t%f%%\t%f\t%f" % (epoch, train_match_loss_got, train_recon_loss_got, test_top_1_accuracy * 100, test_top_5_accuracy * 100, harmonic_top_1 * 100, harmonic_top_5 * 100, epoch_time, total_time)
-				log_string = '%d\t%f\t%f\t%f\t%f\t%f\t%f\t%f\t%f\n' % (epoch, train_match_loss_got, train_recon_loss_got, test_top_1_accuracy, test_top_5_accuracy, harmonic_top_1, harmonic_top_5, epoch_time, total_time)
+				#print_string = "%d\t%f\t%f\n  %f%%\t%f%%\t%f%%\t%f%%\t%f\t%f" % (epoch, train_match_loss_got, train_recon_loss_got, test_top_1_accuracy * 100, test_top_5_accuracy * 100, harmonic_top_1 * 100, harmonic_top_5 * 100, epoch_time, total_time)
+				#log_string = '%d\t%f\t%f\t%f\t%f\t%f\t%f\t%f\t%f\n' % (epoch, train_match_loss_got, train_recon_loss_got, test_top_1_accuracy, test_top_5_accuracy, harmonic_top_1, harmonic_top_5, epoch_time, total_time)
+
+				print_string = "%d\t%f\t%f\n  %f%%\t%f\t%f" % (epoch, train_match_loss_got, train_recon_loss_got, test_top_1_accuracy * 100, epoch_time, total_time)
[…]

### 2017-12-12 code/aaeexp2.py
trying out aaeexp2, 3, ...

@@ -1,0 +1,384 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import numpy as np
+import tensorflow as tf
+import dataset
+
+
+class aaeexp2(object):
+	def __init__(self,
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max, momentum = 0.0,
+		gaus_mean = 0.0, gaus_stddev = 1.0,
+		coef_match = 1.0, coef_recon = 1.0, coef_gan = 1.0,
+		unseen_class_file_name = None,
+		train_file_name = None,
+		val_file_name = None,
+		test_file_name = None,
+		train_label_file_name = None,
+		val_label_file_name = None,
+		test_label_file_name = None,
+		train_attr_file_name = None,
+		val_attr_file_name = None,
+		test_attr_file_name = None,
+		log_file_name_head = None, save_model_period = 1,
+		load_model_directory = None,
+		generalizedZSL = False):
+
+		self.input_dim = input_dim
+		self.hid_dim = hid_dim
+		self.d1 = d1
+
+		self.lrn_rate = lrn_rate
+		self.train_batch_size = train_batch_size
+		self.epoch_max = epoch_max
+		self.momentum = momentum
+
+		self.gaus_mean = gaus_mean
+		self.gaus_stddev = gaus_stddev
+
+		self.coef_match = coef_match
+		self.coef_recon = coef_recon
+		self.coef_gan = coef_gan
+
+		self.unseen_class = np.load(unseen_class_file_name)
+
+		self.log_file_name_head = log_file_name_head
+		self.save_model_period = save_model_period
+		self.load_model_directory = load_model_directory
+
+		self.generalizedZSL = generalizedZSL
+
+		self.data = dataset.dataset(
+			train_file_name = train_file_name,
+			val_file_name = val_file_name,
+			test_file_name = test_file_name,
+			train_label_file_name = train_label_file_name,
+			val_label_file_name = val_label_file_name,
+			test_label_file_name = test_label_file_name)
+		self.attr_data = dataset.dataset(
+			train_file_name = train_attr_file_name,
+			val_file_name = val_attr_file_name,
+			test_file_name = test_attr_file_name)
+
+
+	def train(self):
[…]

### 2017-12-12 code/aaeexp3.py

@@ -1,0 +1,384 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import numpy as np
+import tensorflow as tf
+import dataset
+
+
+class aaeexp3(object):
+	def __init__(self,
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max, momentum = 0.0,
+		gaus_mean = 0.0, gaus_stddev = 1.0,
+		coef_match = 1.0, coef_recon = 1.0, coef_gan = 1.0,
+		unseen_class_file_name = None,
+		train_file_name = None,
+		val_file_name = None,
+		test_file_name = None,
+		train_label_file_name = None,
+		val_label_file_name = None,
+		test_label_file_name = None,
+		train_attr_file_name = None,
+		val_attr_file_name = None,
+		test_attr_file_name = None,
+		log_file_name_head = None, save_model_period = 1,
+		load_model_directory = None,
+		generalizedZSL = False):
+
+		self.input_dim = input_dim
+		self.hid_dim = hid_dim
+		self.d1 = d1
+
+		self.lrn_rate = lrn_rate
+		self.train_batch_size = train_batch_size
+		self.epoch_max = epoch_max
+		self.momentum = momentum
+
+		self.gaus_mean = gaus_mean
+		self.gaus_stddev = gaus_stddev
+
+		self.coef_match = coef_match
+		self.coef_recon = coef_recon
+		self.coef_gan = coef_gan
+
+		self.unseen_class = np.load(unseen_class_file_name)
+
+		self.log_file_name_head = log_file_name_head
+		self.save_model_period = save_model_period
+		self.load_model_directory = load_model_directory
+
+		self.generalizedZSL = generalizedZSL
+
+		self.data = dataset.dataset(
+			train_file_name = train_file_name,
+			val_file_name = val_file_name,
+			test_file_name = test_file_name,
+			train_label_file_name = train_label_file_name,
+			val_label_file_name = val_label_file_name,
+			test_label_file_name = test_label_file_name)
+		self.attr_data = dataset.dataset(
+			train_file_name = train_attr_file_name,
+			val_file_name = val_attr_file_name,
+			test_file_name = test_attr_file_name)
+
+
+	def train(self):
[…]

### 2017-12-12 code/run_84_sae3_AwA_sZSL_lrn_0p2_match_0p01_2.py

@@ -1,0 +1,67 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import sae3
+
+
+def main(_):
+	input_dim = 1024
+	attr_dim = 85
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 200
+
+	#momentum = 0.9
+
+	coef_match = 0.01
+
+	train_size = 24295
+	test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_84_sae3_AwA_sZSL_lrn_0p2_match_0p01_2"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	load_model_directory = "./log/log_84_sae3_AwA_sZSL_lrn_0p2_match_0p01"
+	#load_model_directory = None
+
+	machine = sae3.sae3(
+		input_dim, attr_dim,
+		lrn_rate, train_batch_size, epoch_max, #momentum = momentum,
+		coef_match = coef_match,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
+		generalizedZSL = generalizedZSL)
+
+	machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-12 code/run_86_sae3_AwA_sZSL_lrn_0p2_match_0p1.py

@@ -1,0 +1,67 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import sae3
+
+
+def main(_):
+	input_dim = 1024
+	attr_dim = 85
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	coef_match = 0.1
+
+	train_size = 24295
+	test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_86_sae3_AwA_sZSL_lrn_0p2_match_0p1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = sae3.sae3(
+		input_dim, attr_dim,
+		lrn_rate, train_batch_size, epoch_max, #momentum = momentum,
+		coef_match = coef_match,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
+		generalizedZSL = generalizedZSL)
+
+	machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-12 code/run_87_sae3_AwA_sZSL_lrn_0p2_match_0p001.py

@@ -1,0 +1,67 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import sae3
+
+
+def main(_):
+	input_dim = 1024
+	attr_dim = 85
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	coef_match = 0.001
+
+	train_size = 24295
+	test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_87_sae3_AwA_sZSL_lrn_0p2_match_0p001"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = sae3.sae3(
+		input_dim, attr_dim,
+		lrn_rate, train_batch_size, epoch_max, #momentum = momentum,
+		coef_match = coef_match,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
+		generalizedZSL = generalizedZSL)
+
+	machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-12 code/run_88_exp_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 1
+	coef_gan = 1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_88_exp_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp.aaeexp(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
[…]

### 2017-12-12 code/run_89_sae2_AwA_sZSL_lrn_0p2_match_0p01.py

@@ -1,0 +1,67 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import sae2
+
+
+def main(_):
+	input_dim = 1024
+	attr_dim = 85
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	coef_match = 0.01
+
+	train_size = 24295
+	test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_89_sae2_AwA_sZSL_lrn_0p2_match_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = sae2.sae2(
+		input_dim, attr_dim,
+		lrn_rate, train_batch_size, epoch_max, #momentum = momentum,
+		coef_match = coef_match,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
+		generalizedZSL = generalizedZSL)
+
+	machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-12 code/run_90_exp2_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp2
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 1
+	coef_gan = 0.000001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_90_exp2_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp2.aaeexp2(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_91_exp2_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp2
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.000001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_91_exp2_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp2.aaeexp2(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_92_exp2_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp2
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 10
+	coef_gan = 0.000001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_92_exp2_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp2.aaeexp2(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_93_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_10_gan_0p.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 10
+	coef_gan = 0.000001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_93_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_10_gan_0p"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/sae2.py

@@ -1,0 +1,328 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import math
+import time
+import numpy as np
+import tensorflow as tf
+import dataset
+
+
+class sae2(object):
+	def __init__(self,
+		input_dim, attr_dim,
+		lrn_rate, train_batch_size, epoch_max, momentum = 0.0,
+		coef_match = 1.0,
+		unseen_class_file_name = None,
+		train_file_name = None,
+		val_file_name = None,
+		test_file_name = None,
+		train_label_file_name = None,
+		val_label_file_name = None,
+		test_label_file_name = None,
+		train_attr_file_name = None,
+		val_attr_file_name = None,
+		test_attr_file_name = None,
+		log_file_name_head = None, save_model_period = 1,
+		load_model_directory = None,
+		generalizedZSL = False):
+
+		self.input_dim = input_dim
+		self.attr_dim = attr_dim
+
+		self.lrn_rate = lrn_rate
+		self.train_batch_size = train_batch_size
+		self.epoch_max = epoch_max
+		self.momentum = momentum
+
+		self.coef_match = coef_match
+
+		self.unseen_class = np.load(unseen_class_file_name)
+
+		self.log_file_name_head = log_file_name_head
+		self.save_model_period = save_model_period
+		self.load_model_directory = load_model_directory
+
+		self.generalizedZSL = generalizedZSL
+
+		self.data = dataset.dataset(
+			train_file_name = train_file_name,
+			val_file_name = val_file_name,
+			test_file_name = test_file_name,
+			train_label_file_name = train_label_file_name,
+			val_label_file_name = val_label_file_name,
+			test_label_file_name = test_label_file_name)
+		self.attr_data = dataset.dataset(
+			train_file_name = train_attr_file_name,
+			val_file_name = val_attr_file_name,
+			test_file_name = test_attr_file_name)
+
+
+	def train(self):
+		sess = tf.Session()
+
+		if self.load_model_directory == None:
+			# --Model parameters--
+			# Encoder
+			rng = 1.0 / math.sqrt( float( self.input_dim + self.attr_dim ) )
[…]

### 2017-12-12 code/aaeexp3.py
Run SAE+GAN experiments

@@ -9,6 +9,8 @@ import tensorflow as tf
 import dataset
 
 
+# Take off biases, use tanh, both match/recon use mean square loss and reduce_mean to each matrix element
+
 class aaeexp3(object):
 	def __init__(self,
 		input_dim, hid_dim, d1,
@@ -74,11 +76,11 @@ class aaeexp3(object):
 			# Encoder
 			rng_ae = 1.0 / math.sqrt( float( self.input_dim + self.hid_dim ) )
 			W_e = tf.Variable( tf.random_uniform( [self.input_dim, self.hid_dim], minval = -rng_ae, maxval = rng_ae ), name = "W_e" )
-			b_e = tf.Variable(tf.zeros([self.hid_dim]), name = "b_e")
+			#b_e = tf.Variable(tf.zeros([self.hid_dim]), name = "b_e")
 			
 			# Decoder
 			# Weight is tied (W_d = W_e^T)
-			b_d = tf.Variable(tf.zeros([self.input_dim]), name = "b_d")
+			#b_d = tf.Variable(tf.zeros([self.input_dim]), name = "b_d")
 			
 			# Discriminator
 			# Layer 1
@@ -103,13 +105,13 @@ class aaeexp3(object):
 			# --Build model--
 			# Autoencoder
 			#H = tf.sigmoid( tf.matmul(X, W_e) + b_e )
-			H = tf.matmul(X, W_e) + b_e
+			H = tf.tanh(tf.matmul(X, W_e))
 			
 			# Compute output as logit, to feed input of tf entropy function
 			# X_tilde_logit = tf.matmul(H, tf.transpose(W_e)) + b_d
 			# Compute output after activation function (e.g. sigmoid) if using mean square loss
 			#X_tilde = tf.sigmoid( tf.matmul(H, tf.transpose(W_e)) + b_d )
-			X_tilde = tf.matmul(H, tf.transpose(W_e)) + b_d
+			X_tilde = tf.tanh(tf.matmul(H, tf.transpose(W_e)))
 
 			# Note that this is an average over the total number of features (batch_size * input_dim)
 			# ave_entropy = tf.reduce_mean( tf.nn.sigmoid_cross_entropy_with_logits(labels = X, logits = X_tilde_logit) )
@@ -117,7 +119,7 @@ class aaeexp3(object):
[…]

### 2017-12-12 code/aaeexp4.py

@@ -9,7 +9,9 @@ import tensorflow as tf
 import dataset
 
 
-class aaeexp2(object):
+# SAE structure + GAN
+
+class aaeexp4(object):
 	def __init__(self,
 		input_dim, hid_dim, d1,
 		lrn_rate, train_batch_size, epoch_max, momentum = 0.0,
@@ -74,11 +76,11 @@ class aaeexp2(object):
 			# Encoder
 			rng_ae = 1.0 / math.sqrt( float( self.input_dim + self.hid_dim ) )
 			W_e = tf.Variable( tf.random_uniform( [self.input_dim, self.hid_dim], minval = -rng_ae, maxval = rng_ae ), name = "W_e" )
-			b_e = tf.Variable(tf.zeros([self.hid_dim]), name = "b_e")
+			#b_e = tf.Variable(tf.zeros([self.hid_dim]), name = "b_e")
 			
 			# Decoder
 			# Weight is tied (W_d = W_e^T)
-			b_d = tf.Variable(tf.zeros([self.input_dim]), name = "b_d")
+			#b_d = tf.Variable(tf.zeros([self.input_dim]), name = "b_d")
 			
 			# Discriminator
 			# Layer 1
@@ -103,13 +105,15 @@ class aaeexp2(object):
 			# --Build model--
 			# Autoencoder
 			#H = tf.sigmoid( tf.matmul(X, W_e) + b_e )
-			H = tf.matmul(X, W_e) + 0.000001 * b_e
+			H = tf.matmul(X, W_e)
 			
 			# Compute output as logit, to feed input of tf entropy function
 			# X_tilde_logit = tf.matmul(H, tf.transpose(W_e)) + b_d
 			# Compute output after activation function (e.g. sigmoid) if using mean square loss
 			#X_tilde = tf.sigmoid( tf.matmul(H, tf.transpose(W_e)) + b_d )
-			X_tilde = tf.matmul(H, tf.transpose(W_e)) + 0.000001 * b_d
+			
+			# This is the magical SAE formula
+			X_tilde = tf.matmul(T, tf.transpose(W_e))
 
 			# Note that this is an average over the total number of features (batch_size * input_dim)
 			# ave_entropy = tf.reduce_mean( tf.nn.sigmoid_cross_entropy_with_logits(labels = X, logits = X_tilde_logit) )
@@ -117,7 +121,7 @@ class aaeexp2(object):
[…]

### 2017-12-12 code/run_100_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p_can reproduce SAE.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp4
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.000001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_100_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp4.aaeexp4(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_101_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p01.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp4
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_101_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp4.aaeexp4(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_102_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p01_template.py

@@ -1,0 +1,85 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp4
+
+
+"""
+Please try:
+
+coef_match = [0.001, 0.01, 0.1, 1, 10, 100, 1000]
+coef_recon = 1
+coef_gan = [0.01, 0.0001]
+
+"""
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_102_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p01_template"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp4.aaeexp4(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
[…]

### 2017-12-12 code/run_90_exp2_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p_2.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp2
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 1
+	coef_gan = 0.000001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_90_exp2_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p_2"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	load_model_directory = "./log/log_90_exp2_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p"
+	#load_model_directory = None
+
+	machine = aaeexp2.aaeexp2(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_94_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p_2.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 1
+	coef_gan = 0.000001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_94_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p_2"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	load_model_directory = "./log/log_94_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p"
+	#load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_94_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p_no gan is good.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 1
+	coef_gan = 0.000001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_94_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_95_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_1_nan.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 1
+	coef_gan = 1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_95_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_96_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p01_okay.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_96_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_97_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p001.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 1
+	coef_gan = 0.001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_97_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p001"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_98_exp3_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_0p.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 0.000001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_98_exp3_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_0p"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_99_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.1
+	coef_recon = 1
+	coef_gan = 0.1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_99_exp3_AwA_sZSL_lrn_0p2_match_0p1_recon_1_gan_0p1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/aaeexp41.py
.

@@ -9,13 +9,14 @@ import tensorflow as tf
 import dataset
 
 
-# Use negative cosine similarity => good
+# SAE structure + GAN
 
-class sae3(object):
+class aaeexp41(object):
 	def __init__(self,
-		input_dim, attr_dim,
+		input_dim, hid_dim, d1,
 		lrn_rate, train_batch_size, epoch_max, momentum = 0.0,
-		coef_match = 1.0,
+		gaus_mean = 0.0, gaus_stddev = 1.0,
+		coef_match = 1.0, coef_recon = 1.0, coef_gan = 1.0,
 		unseen_class_file_name = None,
 		train_file_name = None,
 		val_file_name = None,
@@ -31,14 +32,20 @@ class sae3(object):
 		generalizedZSL = False):
 
 		self.input_dim = input_dim
-		self.attr_dim = attr_dim
+		self.hid_dim = hid_dim
+		self.d1 = d1
 
 		self.lrn_rate = lrn_rate
 		self.train_batch_size = train_batch_size
 		self.epoch_max = epoch_max
 		self.momentum = momentum
 
+		self.gaus_mean = gaus_mean
+		self.gaus_stddev = gaus_stddev
+
 		self.coef_match = coef_match
+		self.coef_recon = coef_recon
+		self.coef_gan = coef_gan
 
 		self.unseen_class = np.load(unseen_class_file_name)
 
@@ -67,39 +74,87 @@ class sae3(object):
 		if self.load_model_directory == None:
 			# --Model parameters--
 			# Encoder
-			rng = 1.0 / math.sqrt( float( self.input_dim + self.attr_dim ) )
-			W = tf.Variable( tf.random_uniform( [self.input_dim, self.attr_dim], minval = -rng, maxval = rng ), name = "W" )
+			rng_ae = 1.0 / math.sqrt( float( self.input_dim + self.hid_dim ) )
+			W_e = tf.Variable( tf.random_uniform( [self.input_dim, self.hid_dim], minval = -rng_ae, maxval = rng_ae ), name = "W_e" )
+			#b_e = tf.Variable(tf.zeros([self.hid_dim]), name = "b_e")
+			
+			# Decoder
+			# Weight is tied (W_d = W_e^T)
+			#b_d = tf.Variable(tf.zeros([self.input_dim]), name = "b_d")
+			
+			# Discriminator
+			# Layer 1
+			rng1 = 1.0 / math.sqrt( float( self.hid_dim + self.d1 ) )
[…]

### 2017-12-12 code/run_103_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p1.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp4
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_103_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp4.aaeexp4(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_104_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p001_use.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp4
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_104_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p001"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp4.aaeexp4(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_105_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p0001.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp4
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.0001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_105_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p0001"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp4.aaeexp4(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_106_exp3_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_0p01_use.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_106_exp3_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_107_exp3_AwA_sZSL_lrn_0p2_match_100_recon_1_gan_0p01.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 100
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_107_exp3_AwA_sZSL_lrn_0p2_match_100_recon_1_gan_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_108_exp3_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p01.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_108_exp3_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_109_exp3_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_1_nan.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 1
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_109_exp3_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
[…]

### 2017-12-12 code/run_110_exp3_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_0p0001.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 0.0001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_110_exp3_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_0p0001"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_111_exp41_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_no.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp41
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_111_exp41_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_no"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp41.aaeexp41(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_112_exp3_AwA_gZSL_lrn_0p2_match_1_recon_1_gan_0p01.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = True
+
+	unseen_class_file_name = "../AwA_generalizedZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_generalizedZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_generalizedZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_generalizedZSL/yTrain.npy"
+	test_label_file_name = "../AwA_generalizedZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_generalizedZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_112_exp3_AwA_gZSL_lrn_0p2_match_1_recon_1_gan_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_113_exp3_CUB_sZSL_lrn_0p2_match_1_recon_1_gan_0p01.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.11
+	gaus_stddev = 0.20
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../CUB_200_2011_standardZSL/unseen_class.npy"
+
+	train_file_name = "../CUB_200_2011_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../CUB_200_2011_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../CUB_200_2011_standardZSL/yTrain.npy"
+	test_label_file_name = "../CUB_200_2011_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../CUB_200_2011_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_113_exp3_CUB_sZSL_lrn_0p2_match_1_recon_1_gan_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
[…]

### 2017-12-12 code/run_114_exp3_CUB_gZSL_lrn_0p2_match_1_recon_1_gan_0p01.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp3
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.11
+	gaus_stddev = 0.20
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = True
+
+	unseen_class_file_name = "../CUB_200_2011_generalizedZSL/unseen_class.npy"
+
+	train_file_name = "../CUB_200_2011_generalizedZSL/xTrain_scaled.npy"
+	test_file_name = "../CUB_200_2011_generalizedZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../CUB_200_2011_generalizedZSL/yTrain.npy"
+	test_label_file_name = "../CUB_200_2011_generalizedZSL/yTest.npy"
+
+	test_attr_file_name = "../CUB_200_2011_generalizedZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_114_exp3_CUB_gZSL_lrn_0p2_match_1_recon_1_gan_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp3.aaeexp3(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
[…]

### 2017-12-12 code/run_115_sae3_AwA_gZSL_lrn_0p2_match_0p01.py

@@ -1,0 +1,67 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import sae3
+
+
+def main(_):
+	input_dim = 1024
+	attr_dim = 85
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	coef_match = 0.01
+
+	train_size = 24295
+	test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = True
+
+	unseen_class_file_name = "../AwA_generalizedZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_generalizedZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_generalizedZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_generalizedZSL/yTrain.npy"
+	test_label_file_name = "../AwA_generalizedZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_generalizedZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_115_sae3_AwA_gZSL_lrn_0p2_match_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = sae3.sae3(
+		input_dim, attr_dim,
+		lrn_rate, train_batch_size, epoch_max, #momentum = momentum,
+		coef_match = coef_match,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
+		generalizedZSL = generalizedZSL)
+
+	machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-12 code/run_116_sae3_CUB_gZSL_lrn_0p2_match_0p01.py

@@ -1,0 +1,67 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import sae3
+
+
+def main(_):
+	input_dim = 1024
+	attr_dim = 312
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	coef_match = 0.01
+
+	train_size = 8822
+	test_size = 2966
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = True
+
+	unseen_class_file_name = "../CUB_200_2011_generalizedZSL/unseen_class.npy"
+
+	train_file_name = "../CUB_200_2011_generalizedZSL/xTrain_scaled.npy"
+	test_file_name = "../CUB_200_2011_generalizedZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../CUB_200_2011_generalizedZSL/yTrain.npy"
+	test_label_file_name = "../CUB_200_2011_generalizedZSL/yTest.npy"
+
+	test_attr_file_name = "../CUB_200_2011_generalizedZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_116_sae3_CUB_gZSL_lrn_0p2_match_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = sae3.sae3(
+		input_dim, attr_dim,
+		lrn_rate, train_batch_size, epoch_max, #momentum = momentum,
+		coef_match = coef_match,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
+		generalizedZSL = generalizedZSL)
+
+	machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-12 code/run_117_exp4_AwA_gZSL_lrn_0p2_match_0p01_recon_1_gan_0p001.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp4
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = True
+
+	unseen_class_file_name = "../AwA_generalizedZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_generalizedZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_generalizedZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_generalizedZSL/yTrain.npy"
+	test_label_file_name = "../AwA_generalizedZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_generalizedZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_117_exp4_AwA_gZSL_lrn_0p2_match_0p01_recon_1_gan_0p001"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp4.aaeexp4(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
[…]

### 2017-12-12 code/run_118_exp4_CUB_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p001.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp4
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.11
+	gaus_stddev = 0.20
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../CUB_200_2011_standardZSL/unseen_class.npy"
+
+	train_file_name = "../CUB_200_2011_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../CUB_200_2011_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../CUB_200_2011_standardZSL/yTrain.npy"
+	test_label_file_name = "../CUB_200_2011_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../CUB_200_2011_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_118_exp4_CUB_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p001"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp4.aaeexp4(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
[…]

### 2017-12-12 code/run_119_exp4_CUB_gZSL_lrn_0p2_match_0p01_recon_1_gan_0p001.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp4
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 312
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.11
+	gaus_stddev = 0.20
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = True
+
+	unseen_class_file_name = "../CUB_200_2011_generalizedZSL/unseen_class.npy"
+
+	train_file_name = "../CUB_200_2011_generalizedZSL/xTrain_scaled.npy"
+	test_file_name = "../CUB_200_2011_generalizedZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../CUB_200_2011_generalizedZSL/yTrain.npy"
+	test_label_file_name = "../CUB_200_2011_generalizedZSL/yTest.npy"
+
+	test_attr_file_name = "../CUB_200_2011_generalizedZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_119_exp4_CUB_gZSL_lrn_0p2_match_0p01_recon_1_gan_0p001"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp4.aaeexp4(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
[…]

### 2017-12-12 code/sae2.py

@@ -9,6 +9,8 @@ import tensorflow as tf
 import dataset
 
 
+# Use Euclidean distance => doesn't work
+
 class sae2(object):
 	def __init__(self,
 		input_dim, attr_dim,

### 2017-12-12 code/run_120_exp4_AwA_sZSL_lrn_0p2_match_100_recon_1_gan_0p01.py
experiments

@@ -1,0 +1,85 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp4
+
+
+"""
+Please try:
+
+coef_match = [0.001, 0.01, 0.1, 1, 10, 100, 1000]
+coef_recon = 1
+coef_gan = [0.01, 0.0001]
+
+"""
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 100
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_120_exp4_AwA_sZSL_lrn_0p2_match_100_recon_1_gan_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp4.aaeexp4(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
[…]

### 2017-12-13 doc/paper.tex
Added Supplementary
Revising the paper.

@@
 
-% \usepackage{nips_2016}
+% \usepackage{nips_2017}
 
 % to compile a camera-ready version, add the [final] option, e.g.:
-\usepackage[final]{nips_2016}
+\usepackage[final]{nips_2017}
 
@@
 \begin{document}
-% \nipsfinalcopy is no longer used
 
@@
 
-%\begin{abstract}
-
-%	This is a 4-page draft.
-
-%\end{abstract}
+\begin{abstract}
+In Zero-shot learning(ZSL), how to learn discriminative features for fine-grained classes is a main challenge.
+In this paper, we propose a novel model: semantic adversarial autoencoder(SAAE) to solve ZSL problem.
+This approach is based on a semantic autoencoder(SAE), which projects image representation onto the space of semantic features.
+We incorporate a discriminator for semantic representations to  strengthen the discriminative power of the model.
+The result of experiments on two standard datasets shows that our model is able to outperform other baseline models, especially in generalized ZSL scenario.
+\end{abstract}
 
@@
 
-Zero-shot learning has been a hot research topic in the field of image classification.
-It simulates how people learn things: when people see an unfamiliar object, we would like to use our existing knowledge and try to evaluate the new object.
+Zero-shot learning has been an active research topic in the field of image classification.
+It simulates how people learn things: when people see an unfamiliar object, they use existing knowledge and try to evaluate the new object.
 Ideally, a large-scale image classification system should be able to recognize novel categories based on its previous training experience.
@@
 This problem becomes even more severe when we target at the task of fine-grained classification because the annotation is more expensive and the number of fine-grained classes is huge.
-Realizing this limitation, researchers resort to additional information, for example attributes or text, to solve this problem.
+Realizing this limitation, researchers resort to additional information, for example, textual description, to solve this problem.
 
 On the other hand, autoencoder has shown its great express power to present complicate distributions such human faces, natural sceneries and natural language.
-Autoencoder is able to convert complicated real world data distributions, e.g.
+It is able to convert complicated real world data distributions, e.g.
 text features, to very well-formed low dimension.
@@
 
-The fundamental problem of zero-shot learning is to extract semantically meaningful feature embeddings that could bridge the gap between similar image/text features and fine-grained classes.
+The fundamental problem of ZSL is to extract semantically meaningful feature embeddings that could bridge the gap between similar image/text features and fine-grained classes.
 Autoencoder becomes an ideal option for this task because it can automatically learn important features.
-In \cite{kodirov2017semantic}, they present a novel solution to zero-shot learning based on learning a Semantic AutoEncoder(SAE).
+In \cite{kodirov2017semantic}, they present a novel solution to zero-shot learning--Semantic AutoEncoder(SAE).
 Taking the encoder-decoder paradigm, an encoder aims to project a visual feature vector into the semantic space as in the existing zero-learning shot models and the decoder should be able to reconstruct the original visual feature.
@@
 
-Inspired by these models, we propose an Adversarial Semantic AutoEncoder(ASAE).
+Inspired by these models, we propose an Semantic Adversarial AutoEncoder(SAAE).
 In our model, we have an encoder that projects a visual feature vector into the semantic space and a decoder that decodes and reconstructs the original visual features.
 Besides, we incorporates a discriminator as in \cite{makhzani2015adversarial} to ensure that generating from any part of prior space results in meaningful samples.
+
 Two types of discriminators will be discussed in this project, one is independent from semantic space and the other is dependent from semantic space.
@@
 
-\section{Zero-shot learning task}
+\section{Semantic Adversarial Autoencoder}
 
-	We aim to solve the zero-shot learning problem of classifying images of unseen classes.
-Given the training images $\bb{x}^c$ and their corresponding text description documents $\bb{t}^c$ for $N_s$ seen classes $c$, we learn the semantic encodings $\bb{h}^c$ of the images.
-The learning goal is to learn the encodings $\bb{h}^c$ for a class that are close to their corresponding text document representation for this class.
-The encodings $\bb{h}^{c_1}$ and $\bb{h}^{c_2}$ from two different classes should bear some separable differences.
-
-	During the test time, we are given images $\bb{x}^c$ of $N_{us}$ unseen classes $c$ and also their text description documents $\bb{t}^c$, but without the prior knowledge of the correspondence between the images and the text documents.
-Our task is to predict the corresponding text document given an image.
+\subsection{Adversarial Autoencoder}
+Adversarial autoencoder\cite{makhzani2015adversarial} is an antoencoder with a generator and a discriminator.
+In addition, a prior is chosen to regularize the hidden representation of the input data.
+During training time, the generator can generate positive samples given the prior, and the discriminator aims to discriminate the positive samples from the generator and the negative samples from the hidden layer of the autoencoder.
+This model structure often contributes to a clear boundary of the learned representations by simultaneously minimizing the reconstruction loss from a plain autoencoder, the loss of misclassifying negative samples from the discriminator, and the loss of failing to generate positive samples from the generator.
 
@@
 
-\section{Adversarial autoencoder for zero-shot learning}
+\subsection{Autoencoder models for ZSL}
+Our SAAE model is an extension of semantic autoencoder(SAE)\cite{kodirov2017semantic}.
+In SAE, the inputs are the image features X and the attribute representations S of the corresponding class.
+The original optimization problem of the SAE is
+    \begin{equation}
+    \min_{W} || \bb{x} - W^{\top} W \bb{x} ||_2^2, \quad \text{s.t.} \;\; W \bb{x} = \bb{s},
+    \end{equation}
+   where W is the parameter in the autoencoder.
+This model enforces the hidden representation of images in the autoencoder to mimic the corresponding semantic representation.
+The loss is further relaxed to
+   \begin{equation}
+   L_{\textrm{SAE}} = || \bb{x} - W^{\top} \bb{s}||_2^2 + \lambda || W \bb{x} - \bb{s} ||_2^2,
+    \end{equation}
+where a matching coefficient $\lambda$ is introduced here to control the importance of matching semantic space representation.
+(2) is a globally convex function, thus W can be solved via Bartels-Stewart algorithm\cite{lu1971solution}.
 
-	We propose two architectures that make use of adversarial autoencoders for the zero-shot learning tasks.
-In one of them we draw positive samples from the prior that is a Gaussian noise, and explicitly require the encoding $\bb{h}^c$ to match the text representation $\bb{t}^c$.
+    Based on SAE, We propose two architectures, explicit SAE and implicit SAE, which incorporate the idea of adversarial autoencoder.
+In one of them we draw positive samples from a Gaussian prior, and explicitly require the encoding $\bb{h}^c$ to approximate the semantic representation $ \bb{t}^c$.
 In this case, the prior serves as a regularizer, which is presented in Sec.~\ref{subsec:NoisePrior}.
-In the other of them, we directly use the text representation as positive samples drawn from some distribution that describes a class of data, and the code is trained by the adversarial net to match the text representation.
+In the other, we directly use the text representation as positive samples drawn from some distribution that describes a class of data, and the code is trained by the adversarial net to match the text representation.
 In this case, the prior guides the generator (the encoder) to learn the code that is close to the semantic representation of text, which is presented in Sec.~\ref{subsec:TextPrior}.
@@
 
-\subsection{Prior as regularizer}
+\subsection{SAAE-exp}
 \label{subsec:NoisePrior}
 
-	The architecture in Figure \ref{fig:Architecture} (a) has an autoencoder that learns the encoding $\bb{h}^c$ of the input images $\bb{x}^c$ belonging to a class $c$.
+	The explicit SAAE\ref{fig:Architecturea} has an autoencoder that learns the encoding $\bb{h}^c$ of the input images $\bb{x}^c$ belonging to a class $c$.
 The code $\bb{h}^c$ is explicitly required to match the text representation $\bb{t}^c$ of that class, as well as regularized by the prior in the adversarial net.
@@
 	\begin{align}
-		\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) + || G(\bb{x}) - \bb{t} ||_2^2 \;\right].
+   L_{semantic} + \min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) + || G(\bb{x}) - \bb{t} ||_2^2 \;\right].
 	\end{align}
-
-	Similar architecture has been proposed in \cite{kodirov2017semantic}, in which the explicit matching to the text representation was used to learn the semantic autoencoder for the image input.
-The difference in our architecture is that we use a adversarial net to regularize the matching to the text representation.
+	The computational details are given in the Supplementary.
 
@@
 
-\begin{figure*}[t!]
+\begin{figure*}[hbt!]
     \centering
@@
         \centering
-        \includegraphics[height=1.65in]{figNoisePrior}
+        \includegraphics[height=2.30in]{fig1}
         \caption{}
+            \label{fig:Architecturea}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[height=1.65in]{figTextPrior}
+        \includegraphics[height=2.30in]{fig2}
         \caption{}
+                    \label{fig:Architectureb}
     \end{subfigure}
@@
 
-\subsection{Prior as guide}
+% ----------------------------------------------------
+
+\subsection{SAAE-imp}
 \label{subsec:TextPrior}
 
-	In Figure \ref{fig:Architecture} (b) we show the adversarial autoencoder that takes the text representation $\bb{t}^c$ as the positive sample drawn from some underlying prior dictating the distribution of the text representation of a class.
+	The implicit SAAE \ref{fig:Architectureb} takes the text representation $\bb{t}^c$ as the positive sample drawn from some underlying prior dictating the distribution of the text representation of a class.
 In this architecture, the code is driven to match the text representation through the adversarial net itself.
-The optimization problem for this learning scheme is of the same form of the standard adversarial autoencoder,
+The optimization problem for this learning scheme is of the same form as the standard adversarial autoencoder,
 	\begin{align}
-		\min_{G} \max_D E_{\bb{t} \sim r(\bb{t})}\left[\; \log D(\bb{t}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) \;\right],
+   L_{semantic} + \min_{G} \max_D E_{\bb{t} \sim r(\bb{t})}\left[\; \log D(\bb{t}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) \;\right],
 	\end{align}
-	except that the prior serves as a guide to match the text distribution rather than as a regularizer that drives the code to a Gaussian noise.
+	except that the prior serves as a guide to match the text distribution rather than as a regularizer that drives the encoding to match a Gaussian noise.
 
-%	We propose to generalize this basic structure to fulfill the zero-shot learning task.
-In addition to the basic structure of the adversarial autoencoder, we include a domain transfer function $T$.
-Given the code $\bb{h}^c$ of an image $\bb{x}^c$ coming from a class $c$, the transfer function transforms $\bb{h}^c$ into its corresponding text-domain feature $\bb{\tau}^c = T(\bb{h}^c) = T(f_{enc}(\bb{x}^c))$.
-We denote the distribution of $\bb{\tau}^c$ as $\bb{\tau}^c \sim s(\bb{\tau}^c | \bb{h}^c, T)$, and the distribution of the actual text in this class as $\bb{t}^c \sim u^c(\bb{t}^c)$.
-Then, during training, we learn the domain transfer function $T$ such that $s(\bb{\tau}^c | \bb{h}^c, T) \rightarrow u^c(\bb{t}^c)$; that is, the encoded-then-transformed $\bb{\tau}^c$ is similar to $\bb{t}^c$.
+% ----------------------------------------------------
 
-% 	We propose a novel architecture that jointly learn the the encoding function $f_{enc}$ and the domain transfer function $T$ simultaneously.
-We adopt the paradigm of the adversarial autoencoder, but instead of using the encoder as the generator, the generator here is the hierarchical structure consisting of the encoder and the domain transfer function, which generates (negative) samples from the distribution $s(\bb{\tau}^c | \bb{h}^c, T)$.
-The discriminator is trained to classify the actual text $\bb{t}^c$ generated from $u^c(\bb{t}^c)$ (the prior) as positive sample, and the text feature $\bb{\tau}^c$ transferred from the image according to the distribution $s(\bb{\tau}^c | \bb{h}^c, T)$ (that is, $\bb{\tau}^c$ generated by the generator) as negative sample.
-Note that each class $c$ has its own distinct prior $u^c$.
-The encoder is in the mean time trained with the decoder to minimize the reconstruction error.
+\subsection{SAE-GAN}
 
-% 	During the test time of the zero-shot learning, an unseen test image $\bb{x}$ is given.
-We feed it into the encoder and the domain transfer function to obtain the text feature $\bb{\tau}$.
-Then, by computing its similarities to each of the unseen-class actual texts $\bb{t}^1, \bb{t}^2, \dots$, we take the most similar class as the class prediction for this image.
+	We also check whether adding GAN to the original architecture of SAE will change the performance of SAE. We solve the following optimization problem,
+	\begin{align}
+		\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G_{\textrm{SAE}}(\bb{x})) ) + L_{\textrm{SAE}} \;\right],
+	\end{align}
+	where
+	\begin{align}
+		G_{\textrm{SAE}}(\bb{x}) = W \bb{x}.
+	\end{align}
 
-% % \noindent\rule{\textwidth}{0.4pt}
+% ----------------------------------------------------
 
-% % ----------------------------------------------------
+\subsection{Classification task}
 
-% \subsection{Another possible learning scheme}
+	There are two scenarios for ZSL in image classification, namely standard ZSL and generalized ZSL.
+During training time, given training images $\bb{x}^c$ and their corresponding semantic representations $\bb{t}^c$ for $N_s$ seen classes $c$, the model learns to bridge the gap between $x^c$ and $t^c$.
 
-% 	We consider train the network in two stages: a pre-training to obtain the prior, and then a training of adversarial autoencoder using the pre-trained prior.
+	During testing time, for standard ZSL, we are given images $\bb{x}^{uc}$ from $N_{us}$ unseen classes and semantic representations $\bb{t}^{uc}$ for those unseen classes without knowing the correspondence between $\bb{x}^{uc}$ and $\bb{t}^{uc}$.
+The task is to determine which unseen class each image belongs to.
+For generalized ZSL, the test images are not constrained to unseen classes: images from both seen and unseen classes can be used as test images and semantic representations for both classes should be provided.
 
-% 	In the first stage, we learn the domain transfer function, the matrix $W$.
-(Do we need to use the decoder part of the autoencoder here?) Method: For images $\bb{x}^c_i$ belonging to class $c$, and a text $\bb{t}^c$ in this class, we jointly learn an encoder $W_{enc}$, such that
-% 		\begin{align}
-% 			\min_{W_{enc}, W} || \bb{h}^c - W \bb{t}^c ||_2^2,
-% 		\end{align}
-% 		where
-% 		\begin{align}
-% 			\bb{h}^c = \sigma( W_{enc} \bb{x}^c ).
-% 		\end{align}
-% 		If we also use decoder part, it will be
-% 		\begin{align}
-% 			\min_{W_{enc}, W} \alpha || \bb{h}^c - W \bb{t}^c ||_2^2 + \beta [ -(\bb{x}^c)^{\top} \log ( W_{enc}^{\top} \bb{h}^c ) ].
-% 		\end{align}
+During testing time, we follow the same classification method as in \cite{kodirov2017semantic}.
+The input test image $X$ is first projected using weight matrix $W$ to get the semantic representation $H$ and then the test class is decided by
+\begin{equation}
+	\min_i D(S_i, H),
+\end{equation}
+where $D$ is the distance function, which can be the negative cosine similarity or the Euclidean distance, We find that cosine similarity in general gives higher classification accuracy than the Euclidean distance does.
+We use the former in our experiments.
 
-% 	In the second stage, we train the adversarial autoencoder with
-% 		\begin{enumerate}
-% 			\item $W_{enc}$ initialized by the pre-trained $W_{enc}$ in first stage. It serves as the generator of the adversarial network.
-% 			%
-% 			\item A class-wise prior
-% 				\begin{align}
-% 					p^c(\bb{h}^c) = \mathcal{N}( W \bb{t}^c, ( \sigma^{(c)} )^2 I ).
-% 				\end{align}
-% 		\end{enumerate}
-% 		The goal in this stage is to learn (fine tune) the autoencoder $W_{enc}$,
-% 		\begin{align}
-% 			\min_{W_{enc}} [ -(\bb{x}^c)^{\top} \log ( W_{enc}^{\top} \bb{h}^c ) ],
-% 		\end{align}
-% 		with the class-wise prior.
+% ---------------------------------------------------------
 
-% 	In predict time, for a test image $\bb{x}$, compute its code $\bb{h} = \sigma(W_{enc} \bb{x})$.
-Then predict its belonging text $\bb{t}^*$ among the candidate (unseen-class text) $\{ \bb{t}^1, \bb{t}^2, \dots \}$ by computing $\{ || \bb{h} - W \bb{t}^1 ||_2^2, || \bb{h} - W \bb{t}^2 ||_2^2, \dots \}$ and select the $\bb{t}^c$ of the minimum one as the $\bb{t}^*$.
+\section{Datasets}
 
-\section{Dataset Description and Baseline Models}
+We conduct our experiments on two datasets.
+The first one is the Caltech-UCSD Birds 200-2011 dataset \cite{wah2011caltech}, with 200 categories of bird images.
+The total number of images is 11,788, and each class consists of about 40 to 80 images.
+The second dataset is AwA \cite{lampert2014attribute}, which consists of 30,475 images of 50 classes of animals.
 
-The dataset we want to use for this project is the Caltech-UCSD Birds 200-2011 data\cite{wah2011caltech}.
-There are 200 categories of birds.
-The number of images is 11,788, and the image dimension is 500 $\times$ [300--500] $\times$ 3.
-Each class consists of between 40 and 80 images.
+Following the preprocessing steps taken in \cite{kodirov2017semantic}, for CUB dataset, we extract the 1024D activation from last pooling layer of Inception-v1 \cite{szegedy2015going} as our image features.
+For AwA dataset, we use the extracted 1024D features provided by \cite{kodirov2017semantic}.
+We use the attribute vector of each class as the semantic representation of the class.
+The dimensions of the attribute vectors are 312 and 85 for the CUB and AwA datasets, respectively.
 
-Here we also list the baseline models we want to compare out result with.
-They are Semantic Autoencoder(SAE)\cite{kodirov2017semantic}, Joint Latent Semantic Embedding(JLSE)\cite{zhang2016zero}, and Synthesized classifiers(Sync)\cite{changpinyo2016synthesized}.
-According to \cite{kodirov2017semantic}, the performance of the baseline models are reported as follows:
+For the standard ZSL tasks, following the description of \cite{kodirov2017semantic}, we withhold 10 and 50 classes as the unseen classes for AwA and CUB datasets, respectively.
+For the generalized ZSL tasks on the CUB dataset, we follow the description of \cite{Xian2017}%
+\footnote{Since we do not have the information about the details of the splitting but only the number of instances in each split, we only follow roughly there number of instances used in each split, but not the exactly same split.}%
+, using 7,125 training images from the 150 seen classes, and 4,663 test images from both 150 seen and 50 unseen classes.
+On the AwA dataset, we use 19,094 training images from the 40 seen classes, and 11,381 test images from both 40 seen and 10 unseen classes.
+
+When we run our experiments, the image features and the attribute vectors are both normalized to $[0, 1]$ over the entire dataset.
+
+% ---------------------------------------------------------
+
+\section{Experiments}
+
+We compare the results of our models with the Semantic Autoencoder (SAE) \cite{kodirov2017semantic}, the Joint Latent Semantic Embedding (JLSE) \cite{zhang2016zero}, and the Synthesized classifiers (Sync) \cite{changpinyo2016synthesized}.
+Due to the lack of an identical dataset, we decide to re-implement SAE to produce a reasonable baseline.
+It is worth noting that our implementation of SAE differs from that of \cite{kodirov2017semantic} in that we solve the optimization problem by gradient descent%
+\footnote{We use the AdaGrad optimizer of TensorFlow.}%
+in its original form, while in \cite{kodirov2017semantic} the problem is solved by first transforming it into a simpler linear equation.
+We find that the classification accuracy of the standard ZSL tasks using our implementation of SAE on both CUB and AwA datasets is lower than that reported in \cite{kodirov2017semantic} (see Table \ref{tab:StandardZSL}).
+Although we cannot reproduce the results in \cite{kodirov2017semantic}, we implement our models in the same framework which we use for implementing SAE, in the following discussion, we will therefore focus on comparing our results with our own implementation of SAE for self consistency.
+Table \ref{tab:StandardZSL} and \ref{tab:GeneralizedZSL} show the experimental results as well as the accuracy reported in \cite{kodirov2017semantic}.
+
 \begin{table}[!htb]
 \centering
- \begin{tabular}{|l|l|}
-  \hline
-  Model & Results \\
-  \hline
-  SAE\cite{kodirov2017semantic} & 61.4 \\
-  \hline
-  JLSE\cite{zhang2016zero} & 41.8 \\
-  \hline
-  Sync\cite{changpinyo2016synthesized} & 54.4 \\
-  \bottomrule
+\begin{tabular}{lrr}
+\toprule
+ & CUB & AwA \\
+\midrule
+SAAE-exp & 10.3 & 64.6 \\
+SAAE-imp & 2.0 & 14.4 \\
+SAE-dir & \bf{60.2} & 77.0 \\
+SAE-GAN & 5.7 & \bf{78.5} \\
+\midrule
+SAE \cite{kodirov2017semantic} & 61.4 & 84.7 \\
+JLSE \cite{zhang2016zero} & 41.8 & 80.5 \\
+Sync \cite{changpinyo2016synthesized} & 54.4 & 72.9 \\
+\bottomrule \\
 \end{tabular}
- \caption{Performance of baseline models.}
+\caption{Top-1 per-class accuracy (\%) of ZSL.
+SAAE-exp and SAAE-imp are the semantic adversarial autoencoder using Gaussian and attribute as priors, respectively.
+SAE-dir is our implementation of SAE which directly solve the optimization problem in its original form.}
+\label{tab:StandardZSL}
+\end{table}
+
+\begin{table}[!htb]
+\centering
+\begin{tabular}{lrr}
+\toprule
+ & CUB & AwA \\
+\midrule
+SAAE-exp & \bf{17.8} & \bf{60.0} \\
+SAAE-imp & 0.5 & 2.4 \\
+SAE-dir & 7.0 & 53.8 \\
+SAE-GAN & 6.9 & 54.0 \\
+\bottomrule \\
+\end{tabular}
+\caption{Top-1 per-class accuracy (\%) of generalized ZSL.
+SAAE-exp and SAAE-imp are the semantic adversarial autoencoder using Gaussian and attribute as priors, respectively.
+SAE-dir is our implementation of SAE which directly solve the optimization problem in its original form.}
+\label{tab:GeneralizedZSL}
+\end{table}
+
+In the experiments of SAAE with explicit matching, the coefficients of the matching, reconstruction, and GAN terms are all set to 1.
+We run for 100 epochs, and report the result top-1 per-class accuracy using negative cosine similarity as the distance at test time.
+The mean and standard deviation of the Gaussian priors are set to be the mean and standard deviation of the attributes of the dataset.
+
+In the experiments of SAAE with implicit matching, the coefficient of the reconstruction term is 10 and that of the GAN is 1.
+We run for 100 epochs, and report the result top-1 per-class accuracy using negative cosine similarity as the distance at test time.
+
+In the experiments of our implementation of SAE, we find that better performance is given when the coefficient of the matching loss is 100 and that of the reconstruction loss is 1.
+This indicates that the performance of SAE is mostly driven by the direct matching between the encoded representation from the image and the attribute vector, and is only marginally driven by the autoencoder.
+
+%(wrong) the coefficients of the matching loss and the reconstruction loss are both set to 1.
+We run for 100 epochs, and report the result top-1 per-class accuracy using negative cosine similarity as the distance at test time.
+
+We find that on the CUB dataset, SAAE with explicit matching achieves the best accuracy in both standard and generalized ZSL tasks.
+On the AwA dataset, our SAE implementation gives the best accuracy on both standard and generalized ZSL tasks.
+
+% ----------------------------------------------
+
+\section{Discussion}
+
+% \subsection{SAE}
+
+% In the experiment of our implementation of SAE, we find that the best results are achieved when the coefficients of the matching loss and the reconstruction loss are both set to 1 (compared to having much larger coefficient of the matching loss)
+
+% One thing to notice is that the result of SAE is heavily affected by the $\lambda$ in the equation.
+If we set the $\lambda$ to be 1, the accuracy will stay around 5\% for AWA dataset.
+The result will only become close to the best result we have when the $\lambda$ is set to around 100000.
+After incorporating the adversarial part, the choice of $\lambda$ no longer matters: the accuracy will become close the the best result even we set the $\lambda$ to be 1.
+
+\subsection{SAAE-exp}
+Our extension with adding adversarial part for the autoencoder does not improve the accuracy for the strict ZSL scenario.
+We experiment with a lot of other settings, such as adding more layers for autoencoder, changing the hidden dimensions of generator and discriminator for adversarial part, and different sampling strategies, such as sampling from hidden state to produce negative samples, as described in \cite{makhzani2015adversarial} section 2.
+None of them give any performance boost.
+
+We suspect the reason could be two-folded.
+The first reason is that the semantic features plays the essential role to the model.
+We also try ablation study that does not include the semantic space as constraints.
+In this case the model is just slightly better than random guess.
+This is expected since ZSL task usually deals with fine-grained image classification, and without the additional semantic space input, the models trained only based on image features are likely to have a poor result.
+However, the only way we figure out to incorporate the semantic features into the adversarial autoencoder is to minimize the l2 loss between the hidden state of the encoder and the semantic representation, and this major constraint bound the accuracy of the model.
+
+The second possible reason is that the prior is hard to pick for the semantic distribution.
+The prior serves to regularize the encoded samples so that the hidden state of an encoder is similar to the prior distribution we choose.
+In normal cases, for example alignDraw\cite{mansimov2015generating}, gaussian prior works fine.
+However, in out scenario, the output from encoder has to be close to the semantic space, thus our chosen prior has to resemble the distribution of the semantic space.
+As discussed before, the semantic space is the probability that one attribute appears in this class.
+If we view the attributes in the space of all possible classes, this is similar to a multinomial distribution.
+However, changing gaussian prior to multinomial distribution also does not work well.
+
+The SAAE-exp model performs the best in generalized classification task.
+We think this is as expected due to the nature of our task.
+Adversarial autoencoder is proposed to regularize the class distribution with a shape.
+This regularized shape is even more important in fine-grained classification task we are dealing with, where the difference of classes is very subtle.
+The regularized shape can give a better split between different classes, and this will help improve the classification accuracy in generalized ZSL scenario.
+
+\subsection{SAAE-imp}
+
+We observe that the classification accuracy using SAAE with the attribute as the prior is very low in all experiments.
+The reason is that using attribute vectors as the prior only encourages the encoding to have the same distribution as that of the attributes, but not educating the encoder to learn how to generate the encoding such that each component of the encoding can best match its corresponding component of the attribute vector.
+Since each component of the attribute vector has very specific meaning, and at test time we predict the class label by matching each component of the given attribute vector with the corresponding component of the encoding generated from the test image, lacking the ability to correctly predict each component of the attribute vector leads to the poor performance of this approach.
+
+\subsection{SAE-GAN}
+
+By adding GAN on top of the SAE, we find that on the AwA dataset it improves the accuracy, but on the CUB dataset it does not.
+For the standard ZSL on the AwA dataset, in which GAN makes the most significant improvement, we conduct more detailed experiments to check how accuracy changes by using different coefficients for the GAN.
+The results are shown in Table \ref{tab:SAEGAN}.
+We observe that with suitable coefficient, GAN slightly improves the accuracy, but if the coefficient of GAN is too large, it harms the performance.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{lccccc}
+\toprule
+GAN coefficient & $10^{-1}$ & $10^{-2}$ & $10^{-3}$ & $10^{-4}$ & 0 \\
+Accuracy (\%) & 35.4 & 76.7 & 78.5 & 77.7 & 77.0 \\
+\bottomrule \\
+\end{tabular}
+\caption{The top-1 per-class accuray of the standard ZSL on the AwA dataset, using different coefficients for the GAN in SAE-GAN.}
+\label{tab:SAEGAN}
 \end{table}
@@
 
-%\section{Data}
+\section{Conclusion}
 
-%	We use two datasets: The Caltech-UCSD Birds 200 (2010) dataset \cite{Welinder2010}, and the Oxford VGG 102 category flower dataset \cite{Nilsback2008}.
-The Birds dataset has class number 200, feature dimension 500 $\times$ [300--500] $\times$ 3, and the size of the dataset is 6033.
-The bird images belonging to 200 species.
-Each class consists of between 20 and 40 images, with total of 6033 color images in jpeg format.
+In this paper, we proposed to use the adversarial antoencoder framework incorporating semantic features as a solution to ZSL problem.
+Our method named semantic adversarial autoencoder(SAAE) projects the image representation into the semantic feature space with a discriminator matching the projection to a given prior.
+It achieves comparable accuracies on AWA and CUB datasets, especially in the generalized ZSL scenario.
+We also demonstrate that this new SAAE model is more robust than existing SAE model through extensive experiments.
 
-%	The Oxford VGG 102 category flower dataset has class number 102, feature dimension [500--600] $\times$ 500 $\times$ 3, and the size of the dataset is 8189.
-The flower images belonging to 102 categories.
-Each class consists of between 40 and 258 images, with total of 8189 color images in jpeg format.
-
-% ----------------------------------------------------
-% ----------------------------------------------------
-
-%\section{Discussion}
-
-% 	The architecture proposed in this work can also be applied to image generation from text.
-By applying the inverse domain transfer function to a given text, $T^{-1}(\bb{t})$ can be taken as the code $\bb{h}$, which can then be fed into the decoder to obtain the image $\bb{x}$.
-
-% ----------------------------------------------------
-% ----------------------------------------------------
-
-%\subsubsection*{Acknowledgments}
-
-%Use unnumbered third level headings for the acknowledgments. All acknowledgments go at the end of the paper. Do not include acknowledgments in the anonymized submission, only in the final paper.
-
+\newpage
 % ----------------------------------------------------

### 2017-12-13 doc/paper.tex
Revising paper

@@
 
+\subsection{Semantic Autoencoder}
+
+For transfer learning tasks, the semantic autoencoder (SAE) \cite{kodirov2017semantic} is a tailor-made type of antoencoder-like structure that learns the transfer function between two domains.
+We consider the case in which one domain is the image feature $\bb{x}$, and the other domain is the attribute $\bb{t}$ (the ``semantic representation'') that describes the corresponding image.
+An autoencoder is trained to learn the transfer function $W$ through the optimization problem,
+	\begin{align}
+	\min_{W} || \bb{x} - W^{\top} W \bb{x} ||_2^2, \quad \text{s.t.} \;\; W \bb{x} = \bb{t}.
+	\end{align}
+	This model enforces the encoding of the image to be identical with the corresponding semantic representation.
+While this is a difficult constrained optimization problem, in the SAE architecture, the loss is relaxed to
+	\begin{align}
+	\label{eq:SAELoss} L_{\textrm{SAE}} = || \bb{x} - W^{\top} \bb{s}||_2^2 + \lambda || W \bb{x} - \bb{s} ||_2^2,
+	\end{align}
+	where a coefficient $\lambda$ is introduced to adjust the relative importance of the two terms.
+The SAE loss is a convex function, and in this form $W$ can be solved efficiently via the Bartels-Stewart algorithm \cite{lu1971solution}, which is adopted in \cite{kodirov2017semantic}.
+
 \subsection{Adversarial Autoencoder}
-Adversarial autoencoder\cite{makhzani2015adversarial} is an antoencoder with a generator and a discriminator.
-In addition, a prior is chosen to regularize the hidden representation of the input data.
-During training time, the generator can generate positive samples given the prior, and the discriminator aims to discriminate the positive samples from the generator and the negative samples from the hidden layer of the autoencoder.
-This model structure often contributes to a clear boundary of the learned representations by simultaneously minimizing the reconstruction loss from a plain autoencoder, the loss of misclassifying negative samples from the discriminator, and the loss of failing to generate positive samples from the generator.
 
-% ----------------------------------------------------
-% ----------------------------------------------------
-
-\subsection{Autoencoder models for ZSL}
-Our SAAE model is an extension of semantic autoencoder(SAE)\cite{kodirov2017semantic}.
-In SAE, the inputs are the image features X and the attribute representations S of the corresponding class.
-The original optimization problem of the SAE is
-    \begin{equation}
-    \min_{W} || \bb{x} - W^{\top} W \bb{x} ||_2^2, \quad \text{s.t.} \;\; W \bb{x} = \bb{s},
-    \end{equation}
-   where W is the parameter in the autoencoder.
-This model enforces the hidden representation of images in the autoencoder to mimic the corresponding semantic representation.
-The loss is further relaxed to
-   \begin{equation}
-   L_{\textrm{SAE}} = || \bb{x} - W^{\top} \bb{s}||_2^2 + \lambda || W \bb{x} - \bb{s} ||_2^2,
-    \end{equation}
-where a matching coefficient $\lambda$ is introduced here to control the importance of matching semantic space representation.
-(2) is a globally convex function, thus W can be solved via Bartels-Stewart algorithm\cite{lu1971solution}.
-
-    Based on SAE, We propose two architectures, explicit SAE and implicit SAE, which incorporate the idea of adversarial autoencoder.
-In one of them we draw positive samples from a Gaussian prior, and explicitly require the encoding $\bb{h}^c$ to approximate the semantic representation $ \bb{t}^c$.
-In this case, the prior serves as a regularizer, which is presented in Sec.~\ref{subsec:NoisePrior}.
-In the other, we directly use the text representation as positive samples drawn from some distribution that describes a class of data, and the code is trained by the adversarial net to match the text representation.
-In this case, the prior guides the generator (the encoder) to learn the code that is close to the semantic representation of text, which is presented in Sec.~\ref{subsec:TextPrior}.
+	In the adversarial autoencoder \cite{makhzani2015adversarial}, a generative adversarial net (GAN) \cite{Goodfellow2014} is incorporated into the autoencoder, and the prior in the GAN is chosen to regularize the hidden representation generated by the encoder.
+The positive samples $\bb{z}$ are drawn from the prior $r(\bb{z})$, while the generator $G$, which is simply the encoder in this architecture, generates negative samples $G(\bb{x})$ by encoding the input $\bb{x}$, which is drawn from the underlying data distribution $p_d(\bb{x})$.
+During training, the discriminator $D$ is trained to tell the positive samples from the negative samples, and the generator is trained to generate samples that has the aggregated distribution mimicking the prior distribution, so as to fool the discriminator.
+This procedure can be described as the optimization problem,
+	\begin{align}
+		\label{eq:AAE} \min_G \max_D \; E_{\bb{z} \sim r(\bb{z})}[ \log D(\bb{z}) ] + E_{\bb{x} \sim p_d(\bb{x})}[ \log( 1 - D(G(\bb{x})) ) + L_{\text{recon}} ],
+	\end{align}
+	where $L_{\text{recon}}$ is the reconstruction loss of the autoencoder.
+Through this procedure, the model learns to generate the encodings whose distribution is close to that of the prior by jointly minimizing the reconstruction loss from the autoencoder, the loss of misclassifying the positive and negative samples from the discriminator, and the loss of failing to generate positive samples from the generator.
 
@@
 
-\subsection{SAAE-exp}
-\label{subsec:NoisePrior}
+\subsection{Semantic Adversarial Autoencoder}
 
-	The explicit SAAE\ref{fig:Architecturea} has an autoencoder that learns the encoding $\bb{h}^c$ of the input images $\bb{x}^c$ belonging to a class $c$.
-The code $\bb{h}^c$ is explicitly required to match the text representation $\bb{t}^c$ of that class, as well as regularized by the prior in the adversarial net.
-The learning task can be expressed as the optimization problem,
-	\begin{align}
-   L_{semantic} + \min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) + || G(\bb{x}) - \bb{t} ||_2^2 \;\right].
-	\end{align}
-	The computational details are given in the Supplementary.
+	We propose the semantic adversarial autoencoder (SAAE) of which the generator learns to transfer the representation in one domain into that in another domain.
+The SAAE differs from the plain adversarial autoencoder in that it needs to encourage the input in one domain to be encoded into the representation in another domain (it learns a specific semantic).
+It also differs from SAE in that it uses the adversarial net to inject the global information of the distribution of the training data into the process of locally learning the encoding of each mini-batch of instances.
+
+	We perform experiments on two architectures: the SAAE with explicit matching (SAAE-exp) and the SAAE with implicit matching (SAAE-imp).
+Their architectures are shown in Figure \ref{fig:Architecture}.
+In SAAE-exp, we explicitly require the encoding to approximate the semantic representation, and the positive samples is drawn from the Gaussian prior.
+In this case, the prior serves as a regularizer.
+In SAAE-imp, we directly use the semantic representation as the positive samples drawn from some underlying distribution that describes the semantic representation, and the encoder is trained by the adversarial net to match the semantic representation.
+In this case, the prior guides the generator (the encoder) to learn the encoding that is close to the semantic representation.
 
@@
     \end{subfigure}
-    \caption{Adversarial autoencoders with (a) Gaussian prior and explicit matching to the text representation, and (b) text representations as positive samples drawn from some underlying prior of text distribution.}
+    \caption{Semantic adversarial autoencoders with (a) Gaussian prior and explicit matching to the text (or semantic/attribute) representation, and (b) text (semantic/attribute) representations as positive samples drawn from some underlying prior of the text (semantic/attribute) distribution.}
     \label{fig:Architecture}
@@
 
+\subsubsection{SAAE-exp}
+\label{subsubsec:NoisePrior}
+
+	SAAE-exp has an autoencoder that learns the encoding $\bb{h}^c$ of the input images $\bb{x}^c$ belonging to a class $c$.
+The encoding $\bb{h}^c$ is explicitly required to match the text (or, semantic/attribute)%
+	\footnote{We interchangeably use ``text'', ``semantic'', and ``attribute'' in this report.} %
+	representation $\bb{t}^c$ of that class, as well as regularized by the Gaussian prior in the adversarial net. The learning task can be expressed as the optimization problem,
+	\begin{align}
+	\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) + || G(\bb{x}) - \bb{t} ||_2^2 \;\right].
+	\end{align}
+
+	Given an input image representation $\bb{x} \in R^{d_x}$, the encoder encodes it into $\bb{h} \in R^{d_h}$ by
+	\begin{align}
+		\bb{h} = \tanh(W^e \bb{x}),
+	\end{align}
+	where $W^e \in R^{d_h \times d_x}$, and the hyperbolic tangent function is applied element-wisely.
+Note that the hidden representation space $R^{d_h}$ is also the space of the semantic representation; that is, $\bb{t} \in R^{d_h}$.
+The decoder computes
+	\begin{align}
+		\tilde{\bb{x}} = \tanh((W^e)^{\top} \bb{h}),
+	\end{align}
+	where $W^d \in R^{d_x \times d_h}$.
+
+	The generator of the adversarial net is the encoder of the autoencoder; that is,
+	\begin{align}
+		G(\bb{x}) = \tanh(W^e \bb{x}) = \bb{h}.
+	\end{align}
+	The positive samples are drawn from the Gaussian prior,
+	\begin{align}
+		\bb{z} \sim \mathcal{N}(\mu, \sigma^2),
+	\end{align}
+	where $\bb{z} \in R^{d_h}$, and $\mu$ and $\sigma$ are chosen to be the mean and standard deviation of the semantic representation.
+
+	We use a fully connected neural network with a single hidden layer as the discriminator. Given an input $\bb{z} \in R^{d_h}$, it computes
+	\begin{align}
+		\bb{z}^1 &= \textrm{sigmoid}( W^1 \bb{z} + \bb{b}^1 ), \\
+		%
+		z^2 &= \textrm{sigmoid}( (\bb{w}^2)^{\top} \bb{z}^1 + b^2 ),
+	\end{align}
+	where $\bb{z}^1 \in R^{d_1}$, $W^1 \in R^{d_1 \times d_h}$, $\bb{b}^1 \in R^{d_1}$, $\bb{w}^2 \in R^{d_1}$, and $b^2$ and $z^2$ are scalars. The discriminator returns
+	\begin{align}
+		D(\bb{z}) = z^2,
+	\end{align}
+	which is the estimation of the probability that $\bb{z}$ is drawn from the prior.
+
+	For the autoencoder and the generator of the adversarial net, the loss function for a mini-batch of instances, $S$, is the empirical risk,
+	\begin{align}
+		f_g = \frac{1}{|S|} \sum_{i \in S} \left\{ \log\left[ 1 - D( \bb{h}^{(i)} ) \right] + || \bb{x}^{(i)} - \tilde{\bb{x}}^{(i)} ||_2^2 + || \bb{h}^{(i)} - \bb{t}^{c_i} ||_2^2 \right\},
+	\end{align}
+	where the log function is applied element-wisely, and $c_i$ is the class of the instance $\bb{x}^{(i)}$. Here we assume that there is only one text $\bb{t}^c$ for each class $c$.
+
+	For the discriminator of the adversarial net, the loss function is
+	\begin{align}
+		f_d = -\frac{1}{|S|} \sum_{j = 1}^{|S|} \log D( \bb{z}^{(j)} ) - \frac{1}{|S|} \sum_{i \in S} \log\left[ 1 - D( \bb{h}^{(i)} ) \right],
+	\end{align}
+	where $\bb{z}^{(j)}$ are $|S|$ samples drawn from the prior distribution $\mathcal{N}(\mu, \sigma^2)$.
+
+	The optimization problem for the autoencoder and the generator is
+	\begin{align}
+		\min_{W^e} \; f_g,
+	\end{align}
+	while the parameters of the discriminator ($W^1, \bb{b}^1, \bb{w}^2, b^2$) are held constant. The optimization problem for the discriminator is
+	\begin{align}
+		\min_{W^1, \bb{b}^1, \bb{w}^2, b^2} \; f_d,
+	\end{align}
+	while the parameters of the generator ($W^e, \bb{b}^e, W^d, \bb{b}^d$) are held constant.
+
 % ----------------------------------------------------
 
-\subsection{SAAE-imp}
-\label{subsec:TextPrior}
+\subsubsection{SAAE-imp}
+\label{subsubsec:TextPrior}
 
-	The implicit SAAE \ref{fig:Architectureb} takes the text representation $\bb{t}^c$ as the positive sample drawn from some underlying prior dictating the distribution of the text representation of a class.
-In this architecture, the code is driven to match the text representation through the adversarial net itself.
-The optimization problem for this learning scheme is of the same form as the standard adversarial autoencoder,
+	SAAE-imp takes the text representation $\bb{t}^c$ as the positive sample drawn from some underlying prior dictating the distribution of the text representation of a class.
+In this architecture, the encoding is driven to match the text representation through the adversarial net itself.
+The encoder, decoder, generator, and discriminator are the same as described in section \ref{subsubsec:NoisePrior}.
+The difference is that we use the text representation, instead of Gaussian noise, as the prior in the adversarial net.
+For an input image $\bb{x}^{(i)}$ of class $c_i$ and the text representation $\bb{t}^{c_i}$ of this class, we use $\bb{t}^{c_i}$ as the sample drawn from some underlying prior for the representation distribution of this class,
 	\begin{align}
-   L_{semantic} + \min_{G} \max_D E_{\bb{t} \sim r(\bb{t})}\left[\; \log D(\bb{t}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) \;\right],
+		\bb{z}^{c_i} = \bb{t}^{c_i}.
 	\end{align}
-	except that the prior serves as a guide to match the text distribution rather than as a regularizer that drives the encoding to match a Gaussian noise.
+	In addition, we remove the term measuring the L2 distance between the text representation and the hidden representation of the image from the loss function.
+
+	The loss function for the autoencoder and the generator is now the standard one,
+	\begin{align}
+		f_g = \frac{1}{|S|} \sum_{i \in S} \left\{ \log\left[ 1 - D( \bb{h}^{(i)} ) \right] + || \bb{x}^{(i)} - \tilde{\bb{x}}^{(i)} ||_2^2 \right\}.
+	\end{align}
+	For the discriminator of the adversarial net, the loss function is
+	\begin{align}
+		f_d = -\frac{1}{|S|} \sum_{i \in S} \log D( \bb{t}^{c_i} ) - \frac{1}{|S|} \sum_{i \in S} \log\left[ 1 - D( \bb{h}^{(i)} ) \right].
+	\end{align}
+
+	The optimization and test procedures are the same as those described in section \ref{subsubsec:NoisePrior}.
 
@@
 The input test image $X$ is first projected using weight matrix $W$ to get the semantic representation $H$ and then the test class is decided by
-\begin{equation}
-	\min_i D(S_i, H),
-\end{equation}
-where $D$ is the distance function, which can be the negative cosine similarity or the Euclidean distance, We find that cosine similarity in general gives higher classification accuracy than the Euclidean distance does.
+\begin{align}
+	\hat{c} = \textrm{arg} \min_c \textrm{dist}(\bb{t}^c, \bb{h}),
+\end{align}
+where dist is the distance function, which can be the negative cosine similarity or the Euclidean distance, We find that cosine similarity in general gives higher classification accuracy than the Euclidean distance does.
 We use the former in our experiments.

### 2017-12-13 doc/paper.tex
Revised the paper.

@@
 
-\title{Adversarial Zero-Shot Learning}
+\title{Semantic Adversarial Autoencoder for Zero-Shot Learning}
 
@@
 \begin{abstract}
-In Zero-shot learning(ZSL), how to learn discriminative features for fine-grained classes is a main challenge.
-In this paper, we propose a novel model: semantic adversarial autoencoder(SAAE) to solve ZSL problem.
-This approach is based on a semantic autoencoder(SAE), which projects image representation onto the space of semantic features.
-We incorporate a discriminator for semantic representations to  strengthen the discriminative power of the model.
-The result of experiments on two standard datasets shows that our model is able to outperform other baseline models, especially in generalized ZSL scenario.
+
+In zero-shot learning tasks, how to classify the data in the unseen classes in one domain by leveraging the information from the semantic domain is a main challenge.
+We propose a novel model, the semantic adversarial autoencoder, to address this challenge.
+By injecting the global information of the distribution of the semantic representation, the model acquires better generalization ability.
+We perform experiments on the AwA and CUB datasets, and show that our model outperforms the semantic autoencoder in the generalized zero-shot learning tasks.
+
 \end{abstract}
@@
 
-Zero-shot learning has been an active research topic in the field of image classification.
+Zero-shot learning (ZSL) has been an active research topic in the field of image classification.
 It simulates how people learn things: when people see an unfamiliar object, they use existing knowledge and try to evaluate the new object.
@@
 This problem becomes even more severe when we target at the task of fine-grained classification because the annotation is more expensive and the number of fine-grained classes is huge.
-Realizing this limitation, researchers resort to additional information, for example, textual description, to solve this problem.
+Realizing this limitation, researchers resort to additional information, for example, textual or attributive description, to solve this problem.
 
-On the other hand, autoencoder has shown its great express power to present complicate distributions such human faces, natural sceneries and natural language.
+On the other hand, autoencoder has shown its great express power to present complicate distributions such human faces, natural sceneries, and natural language.
 It is able to convert complicated real world data distributions, e.g.
@@
 
- \par
-
 The fundamental problem of ZSL is to extract semantically meaningful feature embeddings that could bridge the gap between similar image/text features and fine-grained classes.
-Autoencoder becomes an ideal option for this task because it can automatically learn important features.
-In \cite{kodirov2017semantic}, they present a novel solution to zero-shot learning--Semantic AutoEncoder(SAE).
-Taking the encoder-decoder paradigm, an encoder aims to project a visual feature vector into the semantic space as in the existing zero-learning shot models and the decoder should be able to reconstruct the original visual feature.
+Autoencoder becomes an ideal option for this task because it can automatically learn representative features.
+In \cite{kodirov2017semantic}, the authors present a novel solution to zero-shot learning, the Semantic Autoencoder (SAE).
+Taking the encoder-decoder paradigm, an encoder aims to project a visual feature vector into the semantic space as in the existing zero-learning shot models, and the decoder should be able to reconstruct the original visual feature.
 Their results show that under this framework, the learned projection function from the seen classes is able to generalize better to the new unseen classes.
@@
 
-Inspired by these models, we propose an Semantic Adversarial AutoEncoder(SAAE).
-In our model, we have an encoder that projects a visual feature vector into the semantic space and a decoder that decodes and reconstructs the original visual features.
+Inspired by these models, we propose the model of Semantic adversarial autoencoder (SAAE).
+In this model, we have an encoder that projects a visual feature vector into the semantic space and a decoder that decodes and reconstructs the original visual features.
 Besides, we incorporates a discriminator as in \cite{makhzani2015adversarial} to ensure that generating from any part of prior space results in meaningful samples.
-
-Two types of discriminators will be discussed in this project, one is independent from semantic space and the other is dependent from semantic space.
+Two types of models that use different priors are investigated.
+In one type of the model, the prior is the Gaussian noise prior, and in the other type the semantic representation itself is used as the prior.
 
@@
 Considering that fine-grained categories might share some common knowledge, a common approach is to seek for an intermediate semantic representation that could connect seen and unseen classes.
-Human specified attributes are first explored to represent the discriminative properties shared among both seen and unseen categories in zero-shot learning\cite{torresani2010efficient, lampert2009learning}.
+Human specified attributes are first explored to represent the discriminative properties shared among both seen and unseen categories in zero-shot learning \cite{torresani2010efficient, lampert2009learning}.
 One limitation of this method is that the creation of attributes still relies on human labors, making it difficult to scale up to meet large scale needs.
@@
 \cite{Ba_2015_ICCV} proposed a model that changes both the ways of extracting features from images and text domains.
-More specifically, the image features are extracted from the activation layer of a convolutional neural network(CNN), and then go through a linear projection layer to reduce dimensions.
+More specifically, the image features are extracted from the activation layer of a convolutional neural network (CNN), and then go through a linear projection layer to reduce dimensions.
 The input text, e.g.
@@
 The SAE loss is a convex function, and in this form $W$ can be solved efficiently via the Bartels-Stewart algorithm \cite{lu1971solution}, which is adopted in \cite{kodirov2017semantic}.
+
+	Note that the SAE is more like a domain transfer machine, rather than a standard autoencoder: It is not minimizing the reconstruction loss; it is minimizing the two directions of transfers between the two domains.
+Later in our experiments we find that in practice the learning may be majorly driven by one of the two directions (see section \ref{subsec:SAE}).
 
@@
 
-	There are two scenarios for ZSL in image classification, namely standard ZSL and generalized ZSL.
-During training time, given training images $\bb{x}^c$ and their corresponding semantic representations $\bb{t}^c$ for $N_s$ seen classes $c$, the model learns to bridge the gap between $x^c$ and $t^c$.
+	There are two scenarios for ZSL, namely standard ZSL and generalized ZSL.
+For the standard ZSL, During training time, given training images $\bb{x}^c$ and their corresponding semantic representations $\bb{t}^c$ for $N_s$ seen classes $c$, the model learns to bridge the gap between $x^c$ and $t^c$.
+During testing time, we are given images $\bb{x}^{uc}$ from $N_{us}$ unseen classes and semantic representations $\bb{t}^{uc}$ for those unseen classes without knowing the correspondence between $\bb{x}^{uc}$ and $\bb{t}^{uc}$.
+The task is to determine which unseen class each image belongs to.
+For the generalized ZSL, the training procedure is the same, but the test images are not constrained to unseen classes: images from both seen and unseen classes can be used as test images and semantic representations for both classes are provided.
 
-	During testing time, for standard ZSL, we are given images $\bb{x}^{uc}$ from $N_{us}$ unseen classes and semantic representations $\bb{t}^{uc}$ for those unseen classes without knowing the correspondence between $\bb{x}^{uc}$ and $\bb{t}^{uc}$.
-The task is to determine which unseen class each image belongs to.
-For generalized ZSL, the test images are not constrained to unseen classes: images from both seen and unseen classes can be used as test images and semantic representations for both classes should be provided.
-
-During testing time, we follow the same classification method as in \cite{kodirov2017semantic}.
-The input test image $X$ is first projected using weight matrix $W$ to get the semantic representation $H$ and then the test class is decided by
+During the test time, we follow the same classification method as in \cite{kodirov2017semantic}.
+The input test image $\bb{x}$ is first projected to the semantic representation $\bb{h}$, and the class is predicted by
 \begin{align}
@@
 \end{align}
-where dist is the distance function, which can be the negative cosine similarity or the Euclidean distance, We find that cosine similarity in general gives higher classification accuracy than the Euclidean distance does.
+where dist is the distance function.
+The distance function can be the negative cosine similarity, $\frac{(\bb{t}^c)^{\top} \bb{h}}{||\bb{t}^c||_2 ||\bb{h}||_2}$, or the Euclidean distance, $||\bb{t}^c - \bb{h}||_2$.
+We find that cosine similarity in general gives higher classification accuracy than the Euclidean distance does.
 We use the former in our experiments.
@@
 \subsection{SAAE-exp}
-Our extension with adding adversarial part for the autoencoder does not improve the accuracy for the strict ZSL scenario.
-We experiment with a lot of other settings, such as adding more layers for autoencoder, changing the hidden dimensions of generator and discriminator for adversarial part, and different sampling strategies, such as sampling from hidden state to produce negative samples, as described in \cite{makhzani2015adversarial} section 2.
-None of them give any performance boost.
 
-We suspect the reason could be two-folded.
-The first reason is that the semantic features plays the essential role to the model.
+Our extension with adding adversarial part for the autoencoder does not yield higher accuracy than that achieved by the SAE in the standard ZSL scenario.
+We have experimented with a lot of other settings, such as adding more layers for the autoencoder, changing the hidden dimensions of the generator and the discriminator in the adversarial part, and different sampling strategies (such as sampling from the hidden state to produce negative samples, as described in \cite{makhzani2015adversarial}, section 2), but none of them gives any performance boost.
+
+We suspect the reason is that the semantic features plays the essential role in the standard ZSL tasks.
 We also try ablation study that does not include the semantic space as constraints.
@@
 This is expected since ZSL task usually deals with fine-grained image classification, and without the additional semantic space input, the models trained only based on image features are likely to have a poor result.
-However, the only way we figure out to incorporate the semantic features into the adversarial autoencoder is to minimize the l2 loss between the hidden state of the encoder and the semantic representation, and this major constraint bound the accuracy of the model.
+However, the only way we figure out to incorporate the semantic features into the adversarial autoencoder is to minimize the L2 loss between the hidden state of the encoder and the semantic representation, and this major constraint limits the accuracy that can be achieved by the model.
 
-The second possible reason is that the prior is hard to pick for the semantic distribution.
+% The second possible reason is that the prior is hard to pick for the semantic distribution.
 The prior serves to regularize the encoded samples so that the hidden state of an encoder is similar to the prior distribution we choose.
@@
 The SAAE-exp model performs the best in generalized classification task.
-We think this is as expected due to the nature of our task.
-Adversarial autoencoder is proposed to regularize the class distribution with a shape.
-This regularized shape is even more important in fine-grained classification task we are dealing with, where the difference of classes is very subtle.
-The regularized shape can give a better split between different classes, and this will help improve the classification accuracy in generalized ZSL scenario.
+We think this is as expected due to the nature of the task.
+Adversarial autoencoder is proposed to inject the global information of the distribution of the semantic representation of the training data.
+Through testing the model on both the seen and unseen classes, the model performs well because it has learned the distribution over all the seen classes.
 
@@
 Since each component of the attribute vector has very specific meaning, and at test time we predict the class label by matching each component of the given attribute vector with the corresponding component of the encoding generated from the test image, lacking the ability to correctly predict each component of the attribute vector leads to the poor performance of this approach.
+
+\subsection{SAE}
+\label{subsec:SAE}
+
+We note that SAE gives the best performance when the coefficient $\lambda$ in \eqref{eq:SAELoss} is much smaller than 1.
+This indicates that the learning is actually driven by learning how to generate (from attribute to reconstructed image), rather than how to infer (from image to attribute).
+We think this is an observation that has not be pointed out in the original SAE paper \cite{kodirov2017semantic}.
 
@@
 In this paper, we proposed to use the adversarial antoencoder framework incorporating semantic features as a solution to ZSL problem.
-Our method named semantic adversarial autoencoder(SAAE) projects the image representation into the semantic feature space with a discriminator matching the projection to a given prior.
-It achieves comparable accuracies on AWA and CUB datasets, especially in the generalized ZSL scenario.
-We also demonstrate that this new SAAE model is more robust than existing SAE model through extensive experiments.
+Our method, the semantic adversarial autoencoder, projects the image representation into the semantic feature space with a discriminator matching the projection to a given prior.
+It outperforms the semantic autoencoder in the generalized zero-shot learning tasks on the AwA and CUB datasets.
 

### 2017-12-13 doc/paper.tex
Revised paper.
Revise paper

@@
 \usepackage{subcaption}	% for \begin{subfigure}[t]{0.5\textwidth}
+
+\usepackage{courier}	% for \texttt{}
 
@@
 
-Inspired by these models, we propose the model of Semantic adversarial autoencoder (SAAE).
+Inspired by these models, we propose the model of semantic adversarial autoencoder (SAAE)%
+\footnote{The code is available on \texttt{https://github.com/yuhsianglin/10707DL\_proj}.}%
+.
 In this model, we have an encoder that projects a visual feature vector into the semantic space and a decoder that decodes and reconstructs the original visual features.
@@
 	\end{align}
-	while the parameters of the generator ($W^e, \bb{b}^e, W^d, \bb{b}^d$) are held constant.
+	while the parameters of the generator ($W^e$) are held constant.
 
@@
 	\begin{align}
-		\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G_{\textrm{SAE}}(\bb{x})) ) + L_{\textrm{SAE}} \;\right],
+		\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \lambda_{\textrm{GAN}} \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \lambda_{\textrm{GAN}} \log( 1 - D(G_{\textrm{SAE}}(\bb{x})) ) + \lambda_{\textrm{SAE}} L_{\textrm{SAE}} \;\right],
 	\end{align}
@@
 	\begin{align}
-		G_{\textrm{SAE}}(\bb{x}) = W \bb{x}.
+		G_{\textrm{SAE}}(\bb{x}) = W \bb{x},
 	\end{align}
+	and $\lambda_{\textrm{GAN}}$ and $\lambda_{\textrm{SAE}}$ are introduced to specify the relative importance of the GAN and SAE parts in the optimization objective.
 
@@
 By adding GAN on top of the SAE, we find that on the AwA dataset it improves the accuracy, but on the CUB dataset it does not.
-For the standard ZSL on the AwA dataset, in which GAN makes the most significant improvement, we conduct more detailed experiments to check how accuracy changes by using different coefficients for the GAN.
+For the standard ZSL on the AwA dataset, in which GAN makes the most significant improvement, we conduct more detailed experiments to check how accuracy changes by using different coefficients $\lambda_{\textrm{GAN}}$ for the GAN while keeping $\lambda_{\textrm{SAE}}$ fixed.
 The results are shown in Table \ref{tab:SAEGAN}.

### 2017-12-13 code/aaeexp.py
Reorganized

@@ -9,6 +9,8 @@ import tensorflow as tf
 import dataset
 
 
+# Take off biases, use tanh, both match/recon use mean square loss and reduce_mean to each matrix element
+
 class aaeexp(object):
 	def __init__(self,
 		input_dim, hid_dim, d1,
@@ -74,11 +76,11 @@ class aaeexp(object):
 			# Encoder
 			rng_ae = 1.0 / math.sqrt( float( self.input_dim + self.hid_dim ) )
 			W_e = tf.Variable( tf.random_uniform( [self.input_dim, self.hid_dim], minval = -rng_ae, maxval = rng_ae ), name = "W_e" )
-			b_e = tf.Variable(tf.zeros([self.hid_dim]), name = "b_e")
+			#b_e = tf.Variable(tf.zeros([self.hid_dim]), name = "b_e")
 			
 			# Decoder
 			# Weight is tied (W_d = W_e^T)
-			b_d = tf.Variable(tf.zeros([self.input_dim]), name = "b_d")
+			#b_d = tf.Variable(tf.zeros([self.input_dim]), name = "b_d")
 			
 			# Discriminator
 			# Layer 1
@@ -102,19 +104,23 @@ class aaeexp(object):
 
 			# --Build model--
 			# Autoencoder
-			H = tf.sigmoid( tf.matmul(X, W_e) + b_e )
+			#H = tf.sigmoid( tf.matmul(X, W_e) + b_e )
+			H = tf.tanh(tf.matmul(X, W_e))
 			
 			# Compute output as logit, to feed input of tf entropy function
-			X_tilde_logit = tf.matmul(H, tf.transpose(W_e)) + b_d
+			# X_tilde_logit = tf.matmul(H, tf.transpose(W_e)) + b_d
 			# Compute output after activation function (e.g. sigmoid) if using mean square loss
-			# X_tilde = tf.sigmoid( tf.matmul(H, tf.transpose(W_e)) + b_d )
+			#X_tilde = tf.sigmoid( tf.matmul(H, tf.transpose(W_e)) + b_d )
+			X_tilde = tf.tanh(tf.matmul(H, tf.transpose(W_e)))
 
 			# Note that this is an average over the total number of features (batch_size * input_dim)
-			ave_entropy = tf.reduce_mean( tf.nn.sigmoid_cross_entropy_with_logits(labels = X, logits = X_tilde_logit) )
[…]

### 2017-12-13 code/archive/aaeexp_1212.py

@@ -9,9 +9,7 @@ import tensorflow as tf
 import dataset
 
 
-# Take off biases, use tanh, both match/recon use mean square loss and reduce_mean to each matrix element
-
-class aaeexp3(object):
+class aaeexp(object):
 	def __init__(self,
 		input_dim, hid_dim, d1,
 		lrn_rate, train_batch_size, epoch_max, momentum = 0.0,
@@ -76,11 +74,11 @@ class aaeexp3(object):
 			# Encoder
 			rng_ae = 1.0 / math.sqrt( float( self.input_dim + self.hid_dim ) )
 			W_e = tf.Variable( tf.random_uniform( [self.input_dim, self.hid_dim], minval = -rng_ae, maxval = rng_ae ), name = "W_e" )
-			#b_e = tf.Variable(tf.zeros([self.hid_dim]), name = "b_e")
+			b_e = tf.Variable(tf.zeros([self.hid_dim]), name = "b_e")
 			
 			# Decoder
 			# Weight is tied (W_d = W_e^T)
-			#b_d = tf.Variable(tf.zeros([self.input_dim]), name = "b_d")
+			b_d = tf.Variable(tf.zeros([self.input_dim]), name = "b_d")
 			
 			# Discriminator
 			# Layer 1
@@ -104,23 +102,19 @@ class aaeexp3(object):
 
 			# --Build model--
 			# Autoencoder
-			#H = tf.sigmoid( tf.matmul(X, W_e) + b_e )
-			H = tf.tanh(tf.matmul(X, W_e))
+			H = tf.sigmoid( tf.matmul(X, W_e) + b_e )
 			
 			# Compute output as logit, to feed input of tf entropy function
-			# X_tilde_logit = tf.matmul(H, tf.transpose(W_e)) + b_d
+			X_tilde_logit = tf.matmul(H, tf.transpose(W_e)) + b_d
 			# Compute output after activation function (e.g. sigmoid) if using mean square loss
-			#X_tilde = tf.sigmoid( tf.matmul(H, tf.transpose(W_e)) + b_d )
-			X_tilde = tf.tanh(tf.matmul(H, tf.transpose(W_e)))
+			# X_tilde = tf.sigmoid( tf.matmul(H, tf.transpose(W_e)) + b_d )
 
 			# Note that this is an average over the total number of features (batch_size * input_dim)
[…]

### 2017-12-13 code/run_aaeexp_AwA_sZSL.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeexp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 1
+	coef_recon = 1
+	coef_gan = 0.01
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_106_exp3_AwA_sZSL_lrn_0p2_match_1_recon_1_gan_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeexp.aaeexp(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
[…]

### 2017-12-13 code/run_aaeimp_AwA_sZSL.py

@@ -1,0 +1,70 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import aaeimp
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	coef_recon = 1
+	coef_gan = 1
+
+	train_size = 24295
+	test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_67_imp_AwA_sZSL_lrn_0p2_recon_1_gen_1"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = aaeimp.aaeimp(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
+		generalizedZSL = generalizedZSL)
+
+	machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-13 code/run_sae_AwA_sZSL.py

@@ -1,0 +1,67 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import sae
+
+
+def main(_):
+	input_dim = 1024
+	attr_dim = 85
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	coef_match = 0.01
+
+	train_size = 24295
+	test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_84_sae3_AwA_sZSL_lrn_0p2_match_0p01"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = sae.sae(
+		input_dim, attr_dim,
+		lrn_rate, train_batch_size, epoch_max, #momentum = momentum,
+		coef_match = coef_match,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
+		generalizedZSL = generalizedZSL)
+
+	machine.train()
+
+
+if __name__ == "__main__":
+	tf.app.run(main = main, argv = None)

### 2017-12-13 code/run_saegan_AwA_sZSL.py

@@ -1,0 +1,75 @@
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+import tensorflow as tf
+import saegan
+
+
+def main(_):
+	input_dim = 1024
+	hid_dim = 85
+
+	d1 = 100
+
+	lrn_rate = 0.2
+	train_batch_size = 64
+	epoch_max = 100
+
+	#momentum = 0.9
+
+	gaus_mean = 0.21
+	gaus_stddev = 0.25
+
+	coef_match = 0.01
+	coef_recon = 1
+	coef_gan = 0.001
+
+	#train_size = 24295
+	#test_size = 6180
+	#reg_lambda = 1.0 / train_size
+
+	save_model_period = 1
+
+	generalizedZSL = False
+
+	unseen_class_file_name = "../AwA_standardZSL/unseen_class.npy"
+
+	train_file_name = "../AwA_standardZSL/xTrain_scaled.npy"
+	test_file_name = "../AwA_standardZSL/xTest_scaled.npy"
+
+	train_label_file_name = "../AwA_standardZSL/yTrain.npy"
+	test_label_file_name = "../AwA_standardZSL/yTest.npy"
+
+	test_attr_file_name = "../AwA_standardZSL/sTest_scaled.npy"
+
+	log_directory = "./log/log_104_exp4_AwA_sZSL_lrn_0p2_match_0p01_recon_1_gan_0p001"
+	log_file_name_head = log_directory + "/log"
+	if not os.path.exists(log_directory):
+		os.makedirs(log_directory)
+
+	#load_model_directory = "./log/log_27_lrn_0p02_data_AwA_match_1_adagrad_2"
+	load_model_directory = None
+
+	machine = saegan.saegan(
+		input_dim, hid_dim, d1,
+		lrn_rate, train_batch_size, epoch_max,
+		gaus_mean = gaus_mean, gaus_stddev = gaus_stddev,
+		coef_match = coef_match, coef_recon = coef_recon, coef_gan = coef_gan,
+		unseen_class_file_name = unseen_class_file_name,
+		train_file_name = train_file_name,
+		test_file_name = test_file_name,
+		train_label_file_name = train_label_file_name,
+		test_label_file_name = test_label_file_name,
+		test_attr_file_name = test_attr_file_name,
+		log_file_name_head = log_file_name_head,
+		save_model_period = save_model_period,
+		load_model_directory = load_model_directory,
[…]

### 2017-12-13 code/sae.py

@@ -11,7 +11,7 @@ import dataset
 
 # Use negative cosine similarity => good
 
-class sae3(object):
+class sae(object):
 	def __init__(self,
 		input_dim, attr_dim,
 		lrn_rate, train_batch_size, epoch_max, momentum = 0.0,

### 2017-12-13 code/saegan.py

@@ -11,7 +11,7 @@ import dataset
 
 # SAE structure + GAN
 
-class aaeexp4(object):
+class saegan(object):
 	def __init__(self,
 		input_dim, hid_dim, d1,
 		lrn_rate, train_batch_size, epoch_max, momentum = 0.0,

### 2017-12-13 code/archive/data_preprocessing/buildData.py
Reorganize

@@ -1,68 +1,0 @@
-import numpy as np
-import os
-
-image_id_file = '../data/CUB_200_2011/images.txt'
-image_class_file = '../data/CUB_200_2011/image_class_labels.txt'
-train_test_file = '../data/CUB_200_2011/train_test_split.txt'
-image_features_dir = '../data/preprocessed/'
-training_data_file = '../data/preprocessed/training.txt'
-testing_data_file = '../data/preprocessed/testing.txt'
-
-def readImage2IdFile(filepath):
-    image2Id = {}
-    with open(filepath, 'r') as f:
-        for line in f:
-            _id, filename = line.split()
-            image2Id[filename] = _id
-    
-    return image2Id
-
-def readImage2ClassFile(filepath):
-    image2Class = {}
-    with open(filepath, 'r') as f:
-        for line in f:
-            imageId, classId = line.split()
-            image2Class[imageId] = int(classId) - 1
-    
-    return image2Class
-
-def readTrainTestSplitFile(filepath):
-    trainTestSplit = {}
-    with open(filepath, 'r') as f:
-        for line in f:
-            imageId, isTrain = line.split()
-            trainTestSplit[imageId] = bool(int(isTrain))
-    
-    return trainTestSplit
-
-def readAndPreprocessImageFeatures(fileDir, image2Id, image2Class, trainTestSplit):
-    trainingData, testingData = [], []
-    for folder in os.listdir(fileDir):
-        if not os.path.isdir(os.path.join(fileDir, folder)):
-            continue
-        
-        print(folder)
-        for filename in os.listdir(os.path.join(fileDir, folder)):
-            features = np.load(os.path.join(fileDir, folder, filename)).squeeze().tolist()
-            name = folder + '/' + filename.rstrip('.npy')
-            imgId = image2Id[name]
-            _class = image2Class[imgId]
-            features.append(_class)
-            if trainTestSplit[imgId]:
-                trainingData.append(features)
-            else:
-                testingData.append(features)
-    
-    print(len(trainingData), len(testingData))
-    np.savetxt(training_data_file, np.array(trainingData))
-    np.savetxt(testing_data_file, np.array(testingData))
-    
-    return
-
-if __name__ == "__main__":
-    image2Id = readImage2IdFile(image_id_file)
-    image2Class = readImage2ClassFile(image_class_file)
-    trainTestSplit = readTrainTestSplitFile(train_test_file)
-    readAndPreprocessImageFeatures(image_features_dir, image2Id, image2Class, trainTestSplit)
-
-    

### 2017-12-13 code/archive/data_preprocessing/buildSemanticSpace.py

@@ -1,64 +1,0 @@
-from collections import defaultdict
-import os
-
-import numpy as np
-from gensim.models import Doc2Vec
-from gensim.models.doc2vec import TaggedDocument
-import pickle
-
-annotationFile = "../data/CUB_200_2011/attributes/image_attribute_labels.txt"
-classFile = "../data/CUB_200_2011/image_class_labels.txt"
-outputFile = "../data/preprocessed/attribute_embeddings"
-birdTextDir = "../data/BirdsText"
-birdTextOutput = "../data/preprocessed/birdsText.txt"
-
-def buildAttributeSemanticSpace():
-    img2Class = {}
-    classCount = defaultdict(int)
-    with open(classFile, 'r') as f:
-        for line in f:
-            imgId, classId = line.split()
-            img2Class[imgId] = int(classId) - 1
-            classCount[int(classId) - 1] += 1
-
-    result = np.zeros((200, 312))
-    with open(annotationFile, 'r') as f:
-        for line in f:
-            if len(line.split()) != 5:
-                continue
-            imgId, featureId, exist, _1, _2 = line.split()
-            result[img2Class[imgId]][int(featureId) - 1] += int(exist)
-    
-    for i in range(200):
-        result[i] = result[i] / classCount[i]
-    
-    np.save(outputFile, result)
-    return result
-
-def bird2Text():
-    documents = []
-    for filename in os.listdir(birdTextDir):
-        className = int(filename.split('.')[0]) - 1
-        fileContent = open(os.path.join(birdTextDir, filename), 'r', encoding='utf-8', errors='ignore').read()
-        tokenList = fileContent.split()
-        doc = TaggedDocument(tokenList, [className])
-        documents.append(doc)
-    model = Doc2Vec(size = 300, min_count = 5, window = 8)
-
-    model.build_vocab(documents)
-    for epoch in range(20):
-        model.train(documents)
-        model.alpha -= 0.002
-        model.min_alpha = model.alpha
-
-    model.delete_temporary_training_data(keep_doctags_vectors=True, keep_inference=True)
-    result = []
-    for i in range(200):
-        vector = model.docvecs[i]
-        result.append(vector)
-    
-    np.savetxt(birdTextOutput, np.array(result))
-
-if __name__ == "__main__":
-    # buildAttributeSemanticSpace()
-    bird2Text()

### 2017-12-13 code/archive/data_preprocessing/extractFeatures.py

@@ -1,55 +1,0 @@
-import numpy as np
-import os
-import tensorflow as tf
-from PIL import Image
-
-try:
-    import urllib2 as urllib
-except ImportError:
-    import urllib.request as urllib
-
-from datasets import imagenet, dataset_utils
-from nets import inception
-from preprocessing import inception_preprocessing
-
-from tensorflow.contrib import slim
-
-img_dir = '../data/CUB_200_2011/images/'
-preprocessed_dir = '../data/preprocessed'
-checkpoints_dir = 'checkpoints/'
-image_size = inception.inception_v1.default_image_size
-
-# url = "http://download.tensorflow.org/models/inception_v1_2016_08_28.tar.gz"
-
-# if not tf.gfile.Exists(checkpoints_dir):
-#     tf.gfile.MakeDirs(checkpoints_dir)
-
-# dataset_utils.download_and_uncompress_tarball(url, checkpoints_dir)
-
-for foldername in os.listdir(img_dir):
-    print(foldername)
-    
-    if not tf.gfile.Exists(os.path.join(preprocessed_dir, foldername)):
-        tf.gfile.MakeDirs(os.path.join(preprocessed_dir, foldername))
-
-    for filename in os.listdir(os.path.join(img_dir, foldername)):
-        with tf.Graph().as_default():
-            image_file = tf.read_file(os.path.join(img_dir, foldername, filename))
-            image = tf.image.decode_jpeg(image_file, channels=3)
-            processed_image = inception_preprocessing.preprocess_image(image, image_size, image_size, is_training=False)
-            processed_images = tf.expand_dims(processed_image, 0)
-            
-            with slim.arg_scope(inception.inception_v1_arg_scope()):
-                logits, end_points = inception.inception_v1(processed_images, num_classes=1001, is_training=False)
-            probabilities = tf.nn.softmax(logits)                
-
-            init_fn = slim.assign_from_checkpoint_fn(
-                os.path.join(checkpoints_dir, 'inception_v1.ckpt'), 
-                slim.get_model_variables('InceptionV1'))
-
-            with tf.Session() as sess:
-                init_fn(sess)
-                
-                np_image, probabilities = sess.run([image, probabilities])
-                array = end_points['AvgPool_0a_7x7'].eval()
-                np.save(os.path.join(preprocessed_dir, foldername, filename), array)

### 2017-12-13 code/archive/data_preprocessing/preprocessing/preprocess_AwA_generalizedZSL.py

@@ -1,28 +1,0 @@
-from __future__ import absolute_import
-from __future__ import division
-from __future__ import print_function
-
-import numpy as np
-
-
-xTrain = np.load("../AwA_generalizedZSL/xtrain_new.npy")
-xTrain = (xTrain - xTrain.min()) / (xTrain.max() - xTrain.min())
-np.save("../AwA_generalizedZSL/xTrain_scaled.npy", xTrain.astype(np.float32))
-
-xTest = np.load("../AwA_generalizedZSL/xtest_new.npy")
-xTest = (xTest - xTest.min()) / (xTest.max() - xTest.min())
-np.save("../AwA_generalizedZSL/xTest_scaled.npy", xTest.astype(np.float32))
-
-yTrain = np.load("../AwA_generalizedZSL/ytrain_new.npy")
-np.save("yTrain.npy", yTrain.astype(np.int32))
-
-yTest = np.load("../AwA_generalizedZSL/ytest_new.npy")
-np.save("yTest.npy", yTest.astype(np.int32))
-
-unseen_class = np.load("../AwA_generalizedZSL/unseen.npy")
-unseen_class = unseen_class - 1
-np.save("../AwA_generalizedZSL/unseen_class.npy", unseen_class.astype(np.int32))
-
-sTest = np.load("../AwA_generalizedZSL/semantic.npy")
-sTest = (sTest - sTest.min()) / (sTest.max() - sTest.min())
-np.save("../AwA_generalizedZSL/sTest_scaled.npy", sTest.astype(np.float32))

### 2017-12-13 code/archive/data_preprocessing/preprocessing/preprocess_AwA_standardZSL.py

@@ -1,72 +1,0 @@
-from __future__ import absolute_import
-from __future__ import division
-from __future__ import print_function
-
-import numpy as np
-
-
-xTrain = np.load("../AwA_standardZSL/xTrain.npy")
-xTrain = (xTrain - xTrain.min()) / (xTrain.max() - xTrain.min())
-np.save("../AwA_standardZSL/xTrain_scaled.npy", xTrain.astype(np.float32))
-
-yTrain_file = open("../AwA_standardZSL/labelTrain.txt", "r")
-yTrain = []
-for line in yTrain_file:
-	yTrain.append(int(line) - 1)
-yTrain_file.close()
-yTrain = np.array(yTrain)
-np.save("../AwA_standardZSL/yTrain.npy", yTrain.astype(np.int32))
-
-xTest = np.load("../AwA_standardZSL/xTest.npy")
-xTest = (xTest - xTest.min()) / (xTest.max() - xTest.min())
-np.save("../AwA_standardZSL/xTest_scaled.npy", xTest.astype(np.float32))
-
-yTest_file = open("../AwA_standardZSL/labelTest.txt", "r")
-yTest = []
-unseen_class = []
-for line in yTest_file:
-	label = int(line) - 1
-	yTest.append(label)
-	if label not in unseen_class:
-		unseen_class.append(label)
-yTest_file.close()
-yTest = np.array(yTest)
-unseen_class = np.array(unseen_class)
-np.save("../AwA_standardZSL/yTest.npy", yTest.astype(np.int32))
-np.save("../AwA_standardZSL/unseen_class.npy", unseen_class.astype(np.int32))
-
-
-label_attr_dict = {}
-
-sTrain = np.load("../AwA_standardZSL/sTrain.npy")
-sTrain = (sTrain - sTrain.min()) / (sTrain.max() - sTrain.min())
-
-for instance_idx, label in enumerate(yTrain):
-	if label not in label_attr_dict:
-		label_attr_dict[label] = sTrain[instance_idx]
-	else:
-		if (label_attr_dict[label] - sTrain[instance_idx]).any():
-			print("Warn: Not all class member has same attribute")
-
-sTest = np.load("../AwA_standardZSL/sTest.npy")
-sTest = (sTest - sTest.min()) / (sTest.max() - sTest.min())
-
-s_idx = 0
-current_label = yTest[0]
-if current_label not in label_attr_dict:
-	label_attr_dict[current_label] = sTest[s_idx]
[…]

### 2017-12-13 code/archive/data_preprocessing/preprocessing/preprocess_AwA_standardZSL_2.py

@@ -1,72 +1,0 @@
-from __future__ import absolute_import
-from __future__ import division
-from __future__ import print_function
-
-import numpy as np
-
-
-xTrain = np.load("../AwA_standardZSL/xTrain.npy")
-xTrain = (xTrain - xTrain.min()) / (xTrain.max() - xTrain.min())
-#np.save("../AwA_standardZSL/xTrain_scaled.npy", xTrain.astype(np.float32))
-
-yTrain_file = open("../AwA_standardZSL/labelTrain.txt", "r")
-yTrain = []
-for line in yTrain_file:
-	yTrain.append(int(line) - 1)
-yTrain_file.close()
-yTrain = np.array(yTrain)
-#np.save("../AwA_standardZSL/yTrain.npy", yTrain.astype(np.int32))
-
-xTest = np.load("../AwA_standardZSL/xTest.npy")
-xTest = (xTest - xTest.min()) / (xTest.max() - xTest.min())
-#np.save("../AwA_standardZSL/xTest_scaled.npy", xTest.astype(np.float32))
-
-yTest_file = open("../AwA_standardZSL/labelTest.txt", "r")
-yTest = []
-unseen_class = []
-for line in yTest_file:
-	label = int(line) - 1
-	yTest.append(label)
-	if label not in unseen_class:
-		unseen_class.append(label)
-yTest_file.close()
-yTest = np.array(yTest)
-unseen_class = np.array(unseen_class)
-#np.save("../AwA_standardZSL/yTest.npy", yTest.astype(np.int32))
-#np.save("../AwA_standardZSL/unseen_class.npy", unseen_class.astype(np.int32))
-
-
-label_attr_dict = {}
-
-sTrain = np.load("../AwA_standardZSL/sTrain.npy")
-#sTrain = (sTrain - sTrain.min()) / (sTrain.max() - sTrain.min())
-
-for instance_idx, label in enumerate(yTrain):
-	if label not in label_attr_dict:
-		label_attr_dict[label] = sTrain[instance_idx]
-	else:
-		if (label_attr_dict[label] - sTrain[instance_idx]).any():
-			print("Warn: Not all class member has same attribute")
-
-sTest = np.load("../AwA_standardZSL/sTest.npy")
-#sTest = (sTest - sTest.min()) / (sTest.max() - sTest.min())
-
-s_idx = 0
-current_label = yTest[0]
-if current_label not in label_attr_dict:
[…]

### 2017-12-13 code/archive/data_preprocessing/preprocessing/preprocess_CUB_generalizedZSL.py

@@ -1,26 +1,0 @@
-from __future__ import absolute_import
-from __future__ import division
-from __future__ import print_function
-
-import numpy as np
-import re
-
-
-xTrain = np.load("../CUB_200_2011_generalizedZSL/training_data_general.npy")
-xTrain = (xTrain - xTrain.min()) / (xTrain.max() - xTrain.min())
-np.save("../CUB_200_2011_generalizedZSL/xTrain_scaled.npy", xTrain.astype(np.float32))
-
-yTrain = np.load("../CUB_200_2011_generalizedZSL/training_label_general.npy")
-np.save("../CUB_200_2011_generalizedZSL/yTrain.npy", yTrain.astype(np.int32))
-
-xTest = np.load("../CUB_200_2011_generalizedZSL/testing_data_general.npy")
-xTest = (xTest - xTest.min()) / (xTest.max() - xTest.min())
-np.save("../CUB_200_2011_generalizedZSL/xTest_scaled.npy", xTest.astype(np.float32))
-
-yTest = np.load("../CUB_200_2011_generalizedZSL/testing_label_general.npy")
-np.save("../CUB_200_2011_generalizedZSL/yTest.npy", yTest.astype(np.int32))
-
-unseen_class = np.array(range(150, 200))
-np.save("../CUB_200_2011_generalizedZSL/unseen_class.npy", unseen_class.astype(np.int32))
-
-# use the same sTest_scaled.npy from standard ZSL

### 2017-12-13 code/archive/data_preprocessing/preprocessing/preprocess_CUB_standardZSL.py

@@ -1,80 +1,0 @@
-from __future__ import absolute_import
-from __future__ import division
-from __future__ import print_function
-
-import numpy as np
-import re
-
-
-file = open("../CUB_200_2011_1202_standardZSL/training.txt", "r")
-X = []
-Y = []
-for line in file:
-	xtmp = re.split(" ", line)
-	digittmp = int(float(xtmp[-1]))
-	del xtmp[-1]
-	xtmp = list(np.array(xtmp).astype(float))
-	X.append(xtmp)
-	Y.append(digittmp)
-file.close()
-
-file = open("../CUB_200_2011_1202_standardZSL/validation.txt", "r")
-for line in file:
-	xtmp = re.split(" ", line)
-	digittmp = int(float(xtmp[-1]))
-	del xtmp[-1]
-	xtmp = np.array(xtmp).astype(np.float32)
-	X.append(xtmp)
-	Y.append(digittmp)
-file.close()
-
-X = np.array(X).astype(np.float32)
-Y = np.array(Y).astype(np.int32)
-
-X = (X - X.min()) / (X.max() - X.min())
-np.save("../CUB_200_2011_1202_standardZSL/xTrain_scaled.npy", X)
-np.save("../CUB_200_2011_1202_standardZSL/yTrain.npy", Y)
-
-
-
-file = open("../CUB_200_2011_1202_standardZSL/testing.txt", "r")
-X = []
-Y = []
-for line in file:
-	xtmp = re.split(" ", line)
-	digittmp = int(float(xtmp[-1]))
-	del xtmp[-1]
-	xtmp = np.array(xtmp).astype(np.float32)
-	X.append(xtmp)
-	Y.append(digittmp)
-file.close()
-
-X = np.array(X).astype(np.float32)
-Y = np.array(Y).astype(np.int32)
-
-X = (X - X.min()) / (X.max() - X.min())
-np.save("../CUB_200_2011_1202_standardZSL/xTest_scaled.npy", X)
-np.save("../CUB_200_2011_1202_standardZSL/yTest.npy", Y)
-
-
-
-file = open("../CUB_200_2011_1202_standardZSL/class_attribute_labels_continuous.txt", "r")
-S = []
-for line in file:
-	stmp = re.split(" ", line)
-	stmp = np.array(stmp).astype(np.float32)
-	S.append(stmp)
-file.close()
-
-S = np.array(S).astype(np.float32)
-
[…]
